### 2022-11-03 3rd_try.qmd
Create 3rd_try.qmd

---
title: "quato_file_2"
format: html
---

## revised Quarto file

This is a new try of generating a Quarto file in RStudio. The engine is revised as Knitr. Below is a try-out description of the corpus.

BROWN CORPUS

A Standard Corpus of Present-Day Edited American

English, for use with Digital Computers.

by W. N. Francis and H. Kucera (1964)

Department of Linguistics, Brown University

Providence, Rhode Island, USA

Revised 1971, Revised and Amplified 1979

http://www.hit.uib.no/icame/brown/bcm.html

Distributed with the permission of the copyright holder,

redistribution permitted.

### 2023-06-12 freqlist_location.R
freqlist of location related text

@@ -1,0 +1,20 @@
+install.packages('tidyverse')
+install.packages('mclm')
+install.packages('here')
+install.packages('kableExtra')
+install.packages('readr')
+install.packages("stringr")
+library('tidyverse')
+library('mclm')
+library('here')
+library('kableExtra')
+library(readr)
+library(stringr)
+file_path <- here("merged_allchapters.csv")
+# Read the CSV file
+data <- read_csv(file_path)
+
+# Preprocess the "Plain_text" column
+data$Plain_text <- tolower(data$Plain_text)
+flist <- freqlist(data$Plain_text, as_text = TRUE)
+print(flist, n = 20)

### 2023-06-12 paper_quarto.qmd
quarto commit

---
title: "Keyword and Collocation analysis on India-related text of Natural History"
format: html
---

## 1. Research Question

Natural History by Pliny the Elder is considered the very first encyclopedia in modern history. It not only showcased the actual merchant exchange of the Roman Empire, but also manifested the spatial imagination of Pliny the Elder and the referenced scholarships of that time. As it is a text containing rich research potentials,

## 2. Corpus Description

Quarto enables you to weave together content and executable code into a finished document. To learn more about Quarto see <https://quarto.org>.

## 3. Keyword Analysis on India-related texts

## 4. Collocation Analysis on "India" in the whole corpus

Quarto enables you to weave together content and executable code into a finished document. To learn more about Quarto see <https://quarto.org>.

## 5. Conclusion

Quarto enables you to weave together content and executable code into a finished document. To learn more about Quarto see <https://quarto.org>.

## Running Code

When you click the **Render** button a document will be generated that includes both content and the output of embedded code. You can embed code like this:

```{r}
1 + 1
```

You can add options to executable code like this

```{r}
#| echo: false
2 * 2
```

The `echo: false` option disables the printing of code (only output is displayed).

### 2023-06-12 freqlist_location.R
corpus run

@@ -10,11 +10,36 @@ library('here')
 library('kableExtra')
 library(readr)
 library(stringr)
-file_path <- here("merged_allchapters.csv")
+fpath_target <- here("geotext_indianregion.csv")
+fpath_ref <- here("wholebooktext.csv")
 # Read the CSV file
-data <- read_csv(file_path)
+data_target <- read_csv(fpath_target)
+data_ref <- read_csv(fpath_ref)
+
 
 # Preprocess the "Plain_text" column
-data$Plain_text <- tolower(data$Plain_text)
-flist <- freqlist(data$Plain_text, as_text = TRUE)
-print(flist, n = 20)
+data_target$Text <- tolower(data_target$Text)
+data_ref$Text <- tolower(data_ref$Text)
+flist_target <- freqlist(data_target$Text, as_text = TRUE) %>% print()
+flist_ref <- freqlist(data_ref$Text, as_text = TRUE) %>% print()
+
+# calculate scores
+scores_kw <- assoc_scores(flist_target, flist_ref)
+
+# print scores, sorted by PMI
+print(scores_kw, sort_order = "PMI")
+print(scores_kw, sort_order = "G_signed")
+
+top_scores_kw <- scores_kw %>% 
+  filter(PMI >= 2 & G_signed >= 2)
+
+# print top_scores_kw, sorted by PMI
+top_scores_kw %>%
+  print(sort_order = "PMI")
+
+# print top_scores_kw, sorted by G_signed
+top_scores_kw %>%
+  print(sort_order = "G_signed")
+
+coocs <- data_ref %>% 
+  surf_cooc("(?xi)  ^ india $")

### 2023-06-13 freqlist_location.R
collocation try

@@ -41,5 +41,16 @@ top_scores_kw %>%
 top_scores_kw %>%
   print(sort_order = "G_signed")
 
-coocs <- data_ref %>% 
-  surf_cooc("(?xi)  ^ india $")
+
+corpus_folder <- here("geotext_whole.csv")
+fnames_geo <- get_fnames(corpus_folder) %>% 
+  keep_re("[.]csv")
+coocs <- surf_cooc(data_ref$Text, "(?xi)  ^ india $")
+coocs$target_freqlist
+coocs$ref_freqlist
+
+# calculate scores
+scores_colloc <- assoc_scores(coocs)
+
+# print scores, sorted by PMI
+print(scores_colloc, sort_order = "PMI")

### 2023-06-14 freqlist_location.R
r script importing corpus in txt

@@ -12,6 +12,7 @@ library(readr)
 library(stringr)
 fpath_target <- here("geotext_indianregion.csv")
 fpath_ref <- here("wholebooktext.csv")
+fname
 # Read the CSV file
 data_target <- read_csv(fpath_target)
 data_ref <- read_csv(fpath_ref)
@@ -20,8 +21,12 @@ data_ref <- read_csv(fpath_ref)
 # Preprocess the "Plain_text" column
 data_target$Text <- tolower(data_target$Text)
 data_ref$Text <- tolower(data_ref$Text)
-flist_target <- freqlist(data_target$Text, as_text = TRUE) %>% print()
-flist_ref <- freqlist(data_ref$Text, as_text = TRUE) %>% print()
+
+corpus_target <- unique(data_target$Text)
+corpus_ref <- unique(data_ref$Text)
+
+flist_target <- freqlist(corpus_target, as_text = TRUE) %>% print()
+flist_ref <- freqlist(corpus_ref, as_text = TRUE) %>% print()
 
 # calculate scores
 scores_kw <- assoc_scores(flist_target, flist_ref)
@@ -42,10 +47,17 @@ top_scores_kw %>%
   print(sort_order = "G_signed")
 
 
-corpus_folder <- here("geotext_whole.csv")
-fnames_geo <- get_fnames(corpus_folder) %>% 
-  keep_re("[.]csv")
-coocs <- surf_cooc(data_ref$Text, "(?xi)  ^ india $")
+
+
+
+corpus_folder <- here("geotext_whole")
+fnames_geotext <- get_fnames(corpus_folder) %>% 
+  keep_re("[.]txt")
+
+print(fnames_BASE, 10, hide_path = corpus_folder)
+
+coocs <- fnames_BASE %>% 
+  surf_cooc("(?xi)  ^ india $")
 coocs$target_freqlist
 coocs$ref_freqlist
 
@@ -54,3 +66,6 @@ scores_colloc <- assoc_scores(coocs)
 
 # print scores, sorted by PMI
 print(scores_colloc, sort_order = "PMI")
+
+# print scores, sorted by G_signed
+print(scores_colloc, sort_order = "G_signed")

### 2023-06-14 paper_quarto.qmd
punctuation remove

@@
 
-## 1. Research Question
+# 1. Research Question
 
@@
 It not only showcased the actual merchant exchange of the Roman Empire, but also manifested the spatial imagination of Pliny the Elder and the referenced scholarships of that time.
-As it is a text containing rich research potentials,
 
-## 2. Corpus Description
+# 2. Corpus Description
+
+As there is a digitized and name entities annotated full text available on [ToposText project](https://topostext.org/work/148 "Check Natural History on ToposText"), I scraped the full text and exported them in .txt as a corpus, and also exported those with geographical location annotations, which considered as geographically related texts as a sub corpus.
+
+(statistics)
+
+# 3. Data Preparation
+
+```{r}
+#| label: chunk
+#| output: false
+#| warning: false
+library('tidyverse')
+library('mclm')
+library('here')
+library('kableExtra')
+
+corpus_folder <- here("NH_wholetext")
+fnames_wholetext <- get_fnames(corpus_folder) %>% 
+  keep_re("[.]txt")
+
+print(fnames_wholetext, 10, hide_path = corpus_folder)
+
+corpus_folder <-  here("NH_geotext_india")
+fnames_indiatext <- get_fnames(corpus_folder) %>% 
+  keep_re("[.]txt")
+
+print(fnames_indiatext, 10, hide_path = corpus_folder)
+```
+
+# 4. Keyword Analysis on India-related texts
+
+```{r}
+# build frequency list for target corpus
+flist_target <- fnames_indiatext %>%
+  freqlist(re_token_splitter = r"--[(?xi)    \s+   ]--", # whitespace as token splitter
+           file_encoding     = "windows-1252") %>%
+  print()
+# build frequency list for reference corpus
+flist_ref <- fnames_wholetext %>%
+  freqlist(re_token_splitter = r"--[(?xi)  \s+   ]--",
+           file_encoding     = "windows-1252") %>%
+  print()
+```
+
+```{r}
+flist_target %>% 
+  as_tibble() %>% 
+  kbl(col.names = c("Rank", "Type", "Absolute", "Relative")) %>% 
+  kable_minimal(full_width = FALSE) %>% 
+  add_header_above(c(" " = 2, "Frequency" = 2)) %>% 
+  scroll_box(height = "400px")
+```
+
+# 5. Collocation Analysis on "India" in the whole corpus
 
@@
 
-## 3. Keyword Analysis on India-related texts
-
-## 4. Collocation Analysis on "India" in the whole corpus
+# 6. Conclusion
 
 Quarto enables you to weave together content and executable code into a finished document. To learn more about Quarto see <https://quarto.org>.
-
-## 5. Conclusion
-
-Quarto enables you to weave together content and executable code into a finished document. To learn more about Quarto see <https://quarto.org>.
-
-## Running Code
-
-When you click the **Render** button a document will be generated that includes both content and the output of embedded code. You can embed code like this:
-
-```{r}
-1 + 1
-```
-
-You can add options to executable code like this
-
-```{r}
-#| echo: false
-2 * 2
-```
-
-The `echo: false` option disables the printing of code (only output is displayed).

### 2023-06-14 freqlist_location.R

@@ -2,14 +2,14 @@ install.packages('tidyverse')
 install.packages('mclm')
 install.packages('here')
 install.packages('kableExtra')
-install.packages('readr')
-install.packages("stringr")
+
+
 library('tidyverse')
 library('mclm')
 library('here')
 library('kableExtra')
-library(readr)
-library(stringr)
+
+
 fpath_target <- here("geotext_indianregion.csv")
 fpath_ref <- here("wholebooktext.csv")
 fname
@@ -50,13 +50,41 @@ top_scores_kw %>%
 
 
 
-corpus_folder <- here("geotext_whole")
-fnames_geotext <- get_fnames(corpus_folder) %>% 
+corpus_folder <- here("NH_wholetext")
+fnames_wholetext <- get_fnames(corpus_folder) %>% 
   keep_re("[.]txt")
 
-print(fnames_BASE, 10, hide_path = corpus_folder)
+print(fnames_wholetext, 10, hide_path = corpus_folder)
 
-coocs <- fnames_BASE %>% 
+corpus_folder <- here("NH_geotext_india")
+fnames_indiatext <- get_fnames(corpus_folder) %>% 
+  keep_re("[.]txt")
+
+print(fnames_indiatext, 10, hide_path = corpus_folder)
+
+# build frequency list for target corpus
+flist_target <- fnames_indiatext %>%
+  freqlist(
+    re_token_splitter = r"--[(?xi)    \s+   ]--", # whitespace as token splitter
+    re_token_transf_in = "[[:punct:]]", # Match punctuation marks
+    token_transf_out = "" # Replace punctuation marks with an empty string
+  ) %>%
+  print()
+
+# build frequency list for reference corpus
+flist_ref <- fnames_wholetext %>%
+  freqlist(re_token_splitter = r"--[(?xi)    \s+   ]--", # whitespace as token splitter
+           re_token_transf_in = "[[:punct:]]", # Match punctuation marks
+           token_transf_out = "") %>%
+  print()
+
+# calculate scores
+scores_kw <- assoc_scores(flist_target, flist_ref)
+
+# print scores, sorted by PMI
+print(scores_kw, sort_order = "PMI")
+
+coocs <- fnames_wholetext %>% 
   surf_cooc("(?xi)  ^ india $")
 coocs$target_freqlist
 coocs$ref_freqlist
@@ -69,3 +97,6 @@ print(scores_colloc, sort_order = "PMI")
 
[…]

### 2023-06-14 paper_quarto.qmd
0614 update

@@
 It not only showcased the actual merchant exchange of the Roman Empire, but also manifested the spatial imagination of Pliny the Elder and the referenced scholarships of that time.
+
+```{r}
+library(ggplot2)
+library(dplyr)
+
+data <- read.csv("geotext_whole.csv")
+
+summary_data <- data %>%
+  group_by(ToposText_ID, Place_Name) %>%
+  summarise(Count = n()) %>%
+  arrange(desc(Count)) %>%
+  top_n(30, Count) %>% print()
+
+```
+
+```{r}
+ggplot(summary_data, aes(x = Count, y = reorder(Place_Name, Count))) +
+  geom_bar(stat = "identity", fill = "steelblue") +
+  labs(x = "Count", y = "Place_Name") +
+  ggtitle("Top 30 Most Referred Location Names") +
+  facet_wrap(~ Place_Name, ncol = 1, scales = "free_y") +
+  theme(axis.text.y = element_text(size = 8, hjust = 0.5))
+```
 
@@
 flist_target <- fnames_indiatext %>%
-  freqlist(re_token_splitter = r"--[(?xi)    \s+   ]--", # whitespace as token splitter
-           file_encoding     = "windows-1252") %>%
+  freqlist(
+    re_token_splitter = r"--[(?xi)    \s+   ]--", # whitespace as token splitter
+    re_token_transf_in = "[[:punct:]]", # Match punctuation marks
+    token_transf_out = "" # Replace punctuation marks with an empty string
+  ) %>%
   print()
+
 # build frequency list for reference corpus
 flist_ref <- fnames_wholetext %>%
-  freqlist(re_token_splitter = r"--[(?xi)  \s+   ]--",
-           file_encoding     = "windows-1252") %>%
+  freqlist(re_token_splitter = r"--[(?xi)    \s+   ]--", # whitespace as token splitter
+           re_token_transf_in = "[[:punct:]]", # Match punctuation marks
+           token_transf_out = "") %>%
   print()
+
+# calculate scores
+scores_kw <- assoc_scores(flist_target, flist_ref)
+
+top_scores_kw <- scores_kw %>% 
+  filter(PMI >= 2 & G_signed >= 2)
+
+# print top_scores_kw, sorted by PMI
+top_scores_kw %>%
+  print(sort_order = "PMI")
+
+# print top_scores_kw, sorted by G_signed
+top_scores_kw %>%
+  print(sort_order = "G_signed")
 ```
@@
 ```{r}
-flist_target %>% 
+top_scores_kw %>% # also valid for top_scores_colloc
   as_tibble() %>%
-  kbl(col.names = c("Rank", "Type", "Absolute", "Relative")) %>% 
-  kable_minimal(full_width = FALSE) %>% 
-  add_header_above(c(" " = 2, "Frequency" = 2)) %>% 
+  select(type, a, PMI, G_signed) %>% # select 4 columns
+  arrange(desc(PMI)) %>%             # sort by PMI (descending) 
+  head(30) %>%                       # select top 30 rows
+  kbl(col.names = c("Type", "Frequency", "PMI", r"(Signed $G^2$)")) %>% 
+  kable_minimal() %>% 
   scroll_box(height = "400px")
@@
 
-Quarto enables you to weave together content and executable code into a finished document. To learn more about Quarto see <https://quarto.org>.
+```{r}
+coocs <- fnames_wholetext %>% 
+  surf_cooc("(?xi)  ^ india $", 
+            re_token_splitter = r"--[(?xi)    \s+   ]--", # whitespace as token splitter
+            re_token_transf_in = "[[:punct:]]", # Match punctuation marks
+            token_transf_out = "")
+coocs$target_freqlist
+coocs$ref_freqlist
+
+# calculate scores
+scores_colloc <- assoc_scores(coocs)
+
+top_scores_colloc <- scores_colloc %>% 
+  filter(PMI >= 2 & G_signed >= 2)
+
+# print top_scores_colloc, sorted by PMI
+top_scores_colloc %>%
+  print(sort_order = "PMI")
+
+# print top_scores_colloc, sorted by G_signed
+top_scores_colloc %>%
+  print(sort_order = "G_signed")
+```
+
+```{r}
+top_scores_colloc %>% # also valid for top_scores_kw
+  as_tibble() %>%
+  select(type, a, PMI, G_signed) %>% # select 4 columns
+  arrange(desc(G_signed)) %>%        # sort by G_signed (descending)  
+  head(30) %>%                       # select top 30 rows
+  kbl(col.names = c("Type", "Frequency", "PMI", r"(Signed $G^2$)")) %>% 
+  kable_minimal() %>% 
+  scroll_box(height = "400px")
+```
 

### 2023-06-14 freqlist_location.R

@@ -8,6 +8,23 @@ library('tidyverse')
 library('mclm')
 library('here')
 library('kableExtra')
+library(ggplot2)
+library(dplyr)
+
+data <- read.csv("geotext_whole.csv")
+
+summary_data <- data %>%
+  group_by(ToposText_ID, Place_Name) %>%
+  summarise(Count = n()) %>%
+  arrange(desc(Count)) %>%
+  top_n(10, Count) %>% print()
+
+ggplot(summary_data, aes(x = Count, y = reorder(Place_Name, Count))) +
+  geom_bar(stat = "identity", fill = "steelblue") +
+  labs(x = "Count", y = "Place_Name") +
+  ggtitle("Top 30 Most Referred Location Names") +
+  facet_wrap(~ Place_Name, ncol = 1, scales = "free_y") +
+  theme(axis.text.y = element_text(size = 8, hjust = 0.5))
 
 
 fpath_target <- here("geotext_indianregion.csv")
@@ -84,8 +101,25 @@ scores_kw <- assoc_scores(flist_target, flist_ref)
 # print scores, sorted by PMI
 print(scores_kw, sort_order = "PMI")
 
+# print scores, sorted by G_signed
+print(scores_kw, sort_order = "G_signed")
+
+top_scores_kw <- scores_kw %>% 
+  filter(PMI >= 2 & G_signed >= 2)
+
+# print top_scores_kw, sorted by PMI
+top_scores_kw %>%
+  print(sort_order = "PMI")
+
+# print top_scores_kw, sorted by G_signed
+top_scores_kw %>%
+  print(sort_order = "G_signed")
+
 coocs <- fnames_wholetext %>% 
-  surf_cooc("(?xi)  ^ india $")
+  surf_cooc("(?xi)  ^ india $", 
+            re_token_splitter = r"--[(?xi)    \s+   ]--", # whitespace as token splitter
+            re_token_transf_in = "[[:punct:]]", # Match punctuation marks
+            token_transf_out = "")
 coocs$target_freqlist
 coocs$ref_freqlist
 
@@ -98,5 +132,32 @@ print(scores_colloc, sort_order = "PMI")
 # print scores, sorted by G_signed
 print(scores_colloc, sort_order = "G_signed")
 
+top_scores_colloc <- scores_colloc %>% 
+  filter(PMI >= 2 & G_signed >= 2)
 
+# print top_scores_colloc, sorted by PMI
+top_scores_colloc %>%
+  print(sort_order = "PMI")
+
[…]

### 2023-06-16 paper_quarto.qmd
map and bar chart added

--- 2023-06-14 paper_quarto.qmd
@@
 
+```{r setup, include=FALSE}
+library('tidyverse')
+library('mclm')
+library('here')
+library('kableExtra')
+library('dplyr')
+library('ggplot2')
+library('leaflet')
+```
+
 # 1. Research Question
@@
 It not only showcased the actual merchant exchange of the Roman Empire, but also manifested the spatial imagination of Pliny the Elder and the referenced scholarships of that time.
+
+```{r}
+#| label: table
+#| warning: false
+data <- read.csv("geotext_whole.csv")
+
+summary_data <- data %>%
+  group_by(ToposText_ID, Place_Name, Lat, Long) %>%
+  summarise(Count = n()) %>%
+  arrange(desc(Count)) %>%
+  ungroup()
+
+top_20_summary_data <- summary_data %>%
+  top_n(20, Count) %>%
+  ungroup() %>% print()
+
+```
+
+```{r}
+#| label: barchart
+#| warning: false
+ggplot(top_20_summary_data, aes(x = reorder(Place_Name, -Count), y = Count)) +
+  geom_bar(stat = "identity") +
+  labs(x = "Place Name", y = "Count") +
+  ggtitle("Top 20 Place Names Mentioned") +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1))
+```
+
+```{r}
+#| label: map
+#| warning: false
+m <- leaflet() %>%
+  addTiles() %>%
+  addCircleMarkers(
+    data = top_20_summary_data,
+    lat = ~Lat,
+    lng = ~Long,
+    radius = sqrt(top_20_summary_data$Count) * 0.8,  # Adjust the scaling factor as needed
+    color = "blue",
+    fill = TRUE,
+    fillOpacity = 0.6,
+    popup = paste("Place Name:", top_20_summary_data$Place_Name, "<br>",
+                  "Count:", top_20_summary_data$Count)
+  ) %>% print()
+
+```
 
@@
 ```{r}
-#| label: chunk
-#| output: false
+#| label: corpus
 #| warning: false
-library('tidyverse')
-library('mclm')
-library('here')
-library('kableExtra')
 
@@
 ```{r}
+#| label: keyword
+#| warning: false
+
 # build frequency list for target corpus
 flist_target <- fnames_indiatext %>%
-  freqlist(re_token_splitter = r"--[(?xi)    \s+   ]--", # whitespace as token splitter
-           file_encoding     = "windows-1252") %>%
-  print()
+  freqlist(
+    re_token_splitter = r"--[(?xi)    \s+   ]--", # whitespace as token splitter
+    re_token_transf_in = "[[:punct:]]", # Match punctuation marks
+    token_transf_out = "" # Replace punctuation marks with an empty string
+  )
+
 # build frequency list for reference corpus
 flist_ref <- fnames_wholetext %>%
-  freqlist(re_token_splitter = r"--[(?xi)  \s+   ]--",
-           file_encoding     = "windows-1252") %>%
-  print()
+  freqlist(re_token_splitter = r"--[(?xi)    \s+   ]--", # whitespace as token splitter
+           re_token_transf_in = "[[:punct:]]", # Match punctuation marks
+           token_transf_out = "")
+
+# calculate scores
+scores_kw <- assoc_scores(flist_target, flist_ref)
+
+top_scores_kw <- scores_kw %>% 
+  filter(PMI >= 2 & G_signed >= 2)
+
+# print top_scores_kw, sorted by PMI
+top_scores_kw %>%
+  print(sort_order = "PMI")
+
+# print top_scores_kw, sorted by G_signed
+top_scores_kw %>%
+  print(sort_order = "G_signed")
 ```
@@
 ```{r}
-flist_target %>% 
+#| label: top30keyword
+#| warning: false
+
+top_scores_kw %>% # also valid for top_scores_colloc
   as_tibble() %>%
-  kbl(col.names = c("Rank", "Type", "Absolute", "Relative")) %>% 
-  kable_minimal(full_width = FALSE) %>% 
-  add_header_above(c(" " = 2, "Frequency" = 2)) %>% 
+  select(type, a, PMI, G_signed) %>% # select 4 columns
+  arrange(desc(PMI)) %>%             # sort by PMI (descending) 
+  head(30) %>%                       # select top 30 rows
+  kbl(col.names = c("Type", "Frequency", "PMI", r"(Signed $G^2$)")) %>% 
+  kable_minimal() %>% 
   scroll_box(height = "400px")
@@
 
-Quarto enables you to weave together content and executable code into a finished document. To learn more about Quarto see <https://quarto.org>.
+```{r}
+#| label: collocation
+#| warning: false
+
+coocs <- fnames_wholetext %>% 
+  surf_cooc("(?xi)  ^ india $", 
+            re_token_splitter = r"--[(?xi)    \s+   ]--", # whitespace as token splitter
+            re_token_transf_in = "[[:punct:]]", # Match punctuation marks
+            token_transf_out = "")
+coocs$target_freqlist
+coocs$ref_freqlist
+
+# calculate scores
+scores_colloc <- assoc_scores(coocs)
+
+top_scores_colloc <- scores_colloc %>% 
+  filter(PMI >= 2 & G_signed >= 2)
+
+# print top_scores_colloc, sorted by PMI
+top_scores_colloc %>%
+  print(sort_order = "PMI")
+
+# print top_scores_colloc, sorted by G_signed
+top_scores_colloc %>%
+  print(sort_order = "G_signed")
+```
+
+```{r}
+#| label: top30collocatioin
+#| warning: false
+top_scores_colloc %>% # also valid for top_scores_kw
+  as_tibble() %>%
+  select(type, a, PMI, G_signed) %>% # select 4 columns
+  arrange(desc(G_signed)) %>%        # sort by G_signed (descending)  
+  head(30) %>%                       # select top 30 rows
+  kbl(col.names = c("Type", "Frequency", "PMI", r"(Signed $G^2$)")) %>% 
+  kable_minimal() %>% 
+  scroll_box(height = "400px")
+```
 

### 2023-06-16 freqlist_location.R

@@ -2,29 +2,54 @@ install.packages('tidyverse')
 install.packages('mclm')
 install.packages('here')
 install.packages('kableExtra')
+install.packages("leaflet")
 
 
 library('tidyverse')
 library('mclm')
 library('here')
 library('kableExtra')
-library(ggplot2)
-library(dplyr)
+library('ggplot2')
+library('dplyr')
+library('leaflet')
 
 data <- read.csv("geotext_whole.csv")
 
 summary_data <- data %>%
-  group_by(ToposText_ID, Place_Name) %>%
+  group_by(ToposText_ID, Place_Name, Lat, Long) %>%
   summarise(Count = n()) %>%
   arrange(desc(Count)) %>%
-  top_n(10, Count) %>% print()
+  ungroup() %>% print(n=20)
 
-ggplot(summary_data, aes(x = Count, y = reorder(Place_Name, Count))) +
-  geom_bar(stat = "identity", fill = "steelblue") +
-  labs(x = "Count", y = "Place_Name") +
-  ggtitle("Top 30 Most Referred Location Names") +
-  facet_wrap(~ Place_Name, ncol = 1, scales = "free_y") +
-  theme(axis.text.y = element_text(size = 8, hjust = 0.5))
+top_20_summary_data <- summary_data %>%
+  top_n(20, Count) %>%
+  ungroup() %>% print()
+
+# Create a bar chart using ggplot2
+ggplot(top_20_summary_data, aes(x = reorder(Place_Name, -Count), y = Count)) +
+  geom_bar(stat = "identity") +
+  labs(x = "Place Name", y = "Count") +
+  ggtitle("Top 20 Place Names Mentioned") +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1))
+
+
+
+# Create a leaflet map
+m <- leaflet() %>%
+  addTiles() %>%
+  addCircleMarkers(
+    data = top_20_summary_data,
+    lat = ~Lat,
+    lng = ~Long,
+    radius = sqrt(top_20_summary_data$Count) * 0.8,  # Adjust the scaling factor as needed
+    color = "blue",
+    fill = TRUE,
+    fillOpacity = 0.6,
+    popup = paste("Place Name:", top_20_summary_data$Place_Name, "<br>",
+                  "Count:", top_20_summary_data$Count)
+  )
+# Display the map
+m
 
 
 fpath_target <- here("geotext_indianregion.csv")
[…]

### 2023-06-19 paper_quarto.qmd
innitial format

--- 2023-06-14 paper_quarto.qmd
@@
 ---
+engine: knitr
 title: "Keyword and Collocation analysis on India-related text of Natural History"
-format: html
+author: "Lizao Zhuang (Dawn) r0914937"
+format: 
+  html:
+    theme: journal
+    toc: true
+    code-link: true
+    abstract-title: "Abstract"
+number-sections: true
+code-fold: true
+abstract: 'The paper applies the methodology of keyword analysis and collocation analysis in corpus linguistics to explore the possible topics of the text related to "India" in Natural History of Pliny the Elder.'
 ---
 
-# 1. Research Question
+```{r setup, include=FALSE}
+library('tidyverse')
+library('mclm')
+library('here')
+library('kableExtra')
+library('dplyr')
+library('ggplot2')
+library('leaflet')
+library('widgetframe')
+options(digits = 3)
+```
+
+# Research Question
 
@@
 
-# 2. Corpus Description
+The text of the whole book has been digitized and annotated with people's name and places' name and coordinates by [TOPOSText](https://topostext.org/the-project) project since 2012.
+By scraping the text as well as the geographical related annotations, the distribution of place names in the encyclopedia can be investigated, which will contribute to a comprehensive understanding of the spatial imagination of Pliny the Elder and the scholarships in his reference network.
 
-As there is a digitized and name entities annotated full text available on [ToposText project](https://topostext.org/work/148 "Check Natural History on ToposText"), I scraped the full text and exported them in .txt as a corpus, and also exported those with geographical location annotations, which considered as geographically related texts as a sub corpus.
-
-(statistics)
-
-# 3. Data Preparation
+@fig-geoname shows the Top 20 distinct geographical names mentioned in Natural History.
 
 ```{r}
-#| label: chunk
-#| output: false
+#| label: fig-geoname
+#| fig-cap: Bar Chart for Top 20 Distinct Place Names Mentioned in Natural History
 #| warning: false
-library('tidyverse')
-library('mclm')
-library('here')
-library('kableExtra')
+#| echo: false
 
-corpus_folder <- here("NH_wholetext")
-fnames_wholetext <- get_fnames(corpus_folder) %>% 
+data <- read.csv("geotext_whole.csv")
+
+summary_data <- data %>%
+  group_by(ToposText_ID, Place_Name, Lat, Long) %>%
+  summarise(Count = n()) %>%
+  arrange(desc(Count)) %>%
+  ungroup()
+
+top_20_summary_data <- summary_data %>%
+  top_n(20, Count) %>%
+  ungroup()
+
+ggplot(top_20_summary_data, aes(x = reorder(Place_Name, -Count), y = Count)) +
+  geom_bar(stat = "identity") +
+  labs(x = "Place Name", y = "Count") +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1))
+
+```
+
+When mapping the places with the annotated coordinates, as shown in @fig-map, India is the only one place that not in mediterranean region while having a rather high counts in the mentioned times.
+
+```{r}
+#| label: fig-map
+#| fig-cap: Mapping of geographical names mentioned in Natural History
+#| warning: false
+#| echo: false
+
+m <- leaflet() %>%
+  addTiles() %>%
+  addCircleMarkers(
+    data = top_20_summary_data,
+    lat = ~Lat,
+    lng = ~Long,
+    radius = sqrt(top_20_summary_data$Count) * 0.8,  
+    color = "blue",
+    fill = TRUE,
+    fillOpacity = 0.6,
+    popup = paste("Place Name:", top_20_summary_data$Place_Name, "<br>",
+                  "Count:", top_20_summary_data$Count)
+  )
+
+widgetframe::frameWidget(m, width = "100%")
+
+```
+
+In this regards, this paper tries to further explore what themes are referred around the text about India region with application of keyword analysis and collocation analysis methods in corpus linguistics.
+
+# Corpus Description
+
+As mentioned, the digitized text with geographical annotation is available through [TOPOSText](https://topostext.org/work/148 "Check Natural History on ToposText") project, I further scraped the full text and exported them in .txt as a \[reference corpus\](#\| label: ref-corpus), and also exported those with annotation of coordinates in a range of indian subcontinent as geographically related texts to India as a \[target corpus\](#tar-corpus).
+The scraping code can be accessed in the link.
+
+```{r}
+#| label: prepare-corpus
+#| warning: false
+
+refcorpus_folder <- here("NH_wholetext")
+fnames_wholetext <- get_fnames(refcorpus_folder) %>% 
   keep_re("[.]txt")
 
-print(fnames_wholetext, 10, hide_path = corpus_folder)
-
-corpus_folder <-  here("NH_geotext_india")
-fnames_indiatext <- get_fnames(corpus_folder) %>% 
+tarcorpus_folder <-  here("NH_geotext_india")
+fnames_indiatext <- get_fnames(tarcorpus_folder) %>% 
   keep_re("[.]txt")
 
-print(fnames_indiatext, 10, hide_path = corpus_folder)
+ref_flist <- freqlist(fnames_wholetext, re_token_splitter = re("\\s+"))
+tar_flist <- freqlist(fnames_indiatext, re_token_splitter = re("\\s+"))
 ```
 
-# 4. Keyword Analysis on India-related texts
+The @ref-corpus consists of all texts in the encyclopedia, divided by paragraphs, has `r prettyNum(n_tokens(ref_flist))` tokens and `r n_types(ref_flist)` types, with the type-token ratio of `r round(n_types(ref_flist)/n_tokens(ref_flist), 2)`.
+
+And the @tar-corpus consists of all text related to Indian subcontinent (with coordinates in range of 8°4'N-37°6'N and 68°7'E to 97°25'E) , has `r prettyNum(n_tokens(tar_flist))` tokens and `r n_types(tar_flist)` types, with the type-token ratio of `r round(n_types(tar_flist)/n_tokens(tar_flist), 2)`.
+
+The tokens are separated by white space and in the analysis of this paper, all the punctuation marks are removed.
+
+# Keyword Analysis on India-related texts
 
 ```{r}
+#| label: keyword
+#| warning: false
+
 # build frequency list for target corpus
 flist_target <- fnames_indiatext %>%
-  freqlist(re_token_splitter = r"--[(?xi)    \s+   ]--", # whitespace as token splitter
-           file_encoding     = "windows-1252") %>%
-  print()
+  freqlist(
+    re_token_splitter = r"--[(?xi)    \s+   ]--", # whitespace as token splitter
+    re_token_transf_in = "[[:punct:]]", # Match punctuation marks
+    token_transf_out = "" # Replace punctuation marks with an empty string
+  )
+
 # build frequency list for reference corpus
 flist_ref <- fnames_wholetext %>%
-  freqlist(re_token_splitter = r"--[(?xi)  \s+   ]--",
-           file_encoding     = "windows-1252") %>%
-  print()
+  freqlist(re_token_splitter = r"--[(?xi)    \s+   ]--", # whitespace as token splitter
+           re_token_transf_in = "[[:punct:]]", # Match punctuation marks
+           token_transf_out = "")
+
+# calculate scores
+scores_kw <- assoc_scores(flist_target, flist_ref)
+
+top_scores_kw <- scores_kw %>% 
+  filter(PMI >= 2 & G_signed >= 2)
+
 ```
 
+@tbl-kwtables shows the top 30 keywords in Indian related texts comparing to other context, respectively sorted by PMI and G_signed.
+
 ```{r}
-flist_target %>% 
+#| label: tbl-kwtables
+#| tbl-cap: Top 30 Keywords of Indian related texts in Natural History
+#| tbl-subcap: 
+#|  - "Sorted by PMI"
+#|  - "Sorted by G_signed"
+#| layout-ncol: 2
+#| warning: false
+#| echo: false
+
+top_scores_kw %>% # also valid for top_scores_colloc
   as_tibble() %>%
-  kbl(col.names = c("Rank", "Type", "Absolute", "Relative")) %>% 
-  kable_minimal(full_width = FALSE) %>% 
-  add_header_above(c(" " = 2, "Frequency" = 2)) %>% 
-  scroll_box(height = "400px")
+  select(type, a, PMI, G_signed) %>% # select 4 columns
+  arrange(desc(PMI)) %>%             # sort by PMI (descending) 
+  head(30) %>%                       # select top 30 rows
+  kbl(col.names = c("Type", "Frequency", "PMI", "(Signed $G^{2}$)"))
+
+top_scores_kw %>% # also valid for top_scores_colloc
+  as_tibble() %>%
+  select(type, a, PMI, G_signed) %>% # select 4 columns
+  arrange(desc(G_signed)) %>%             # sort by PMI (descending) 
+  head(30) %>%                       # select top 30 rows
+  kbl(col.names = c("Type", "Frequency", "PMI", "(Signed $G^{2}$)"))
+
 ```
 
-# 5. Collocation Analysis on "India" in the whole corpus
+# Collocation Analysis on "India" in the whole corpus
+
+```{r}
+#| label: collocation
+#| warning: false
+
+coocs <- fnames_wholetext %>% 
+  surf_cooc("(?xi)  ^ india $", 
+            re_token_splitter = r"--[(?xi)    \s+   ]--", # whitespace as token splitter
+            re_token_transf_in = "[[:punct:]]", # Match punctuation marks
+            token_transf_out = "")
+
+# calculate scores
+scores_colloc <- assoc_scores(coocs)
+
+top_scores_colloc <- scores_colloc %>% 
+  filter(PMI >= 2 & G_signed >= 2)
+```
+
+@tbl-coltables shows the top 30 keywords in Indian related texts comparing to other context, respectively sorted by PMI and G_signed.
+
+```{r}
+#| label: tbl-coltables
+#| tbl-cap: Top 30 Collocates of word "India" in Natural History
+#| tbl-subcap: 
+#|  - "Sorted by PMI"
+#|  - "Sorted by G_signed"
+#| layout-ncol: 2
+#| warning: false
+
+top_scores_colloc %>% 
+  as_tibble() %>%
+  select(type, a, PMI, G_signed) %>% # select 4 columns
+  arrange(desc(PMI)) %>%        # sort by G_signed (descending)  
+  head(30) %>%                       # select top 30 rows
+  kbl(col.names = c("Type", "Frequency", "PMI", "(Signed $G^{2}$)"))
+
+top_scores_colloc %>% 
+  as_tibble() %>%
+  select(type, a, PMI, G_signed) %>% # select 4 columns
+  arrange(desc(G_signed)) %>%        # sort by G_signed (descending)  
+  head(30) %>%                       # select top 30 rows
+  kbl(col.names = c("Type", "Frequency", "PMI", "(Signed $G^{2}$)"))
+
+```
+
+# Conclusion
 
 Quarto enables you to weave together content and executable code into a finished document. To learn more about Quarto see <https://quarto.org>.
-
-# 6. Conclusion
-
-Quarto enables you to weave together content and executable code into a finished document. To learn more about Quarto see <https://quarto.org>.

### 2023-06-19 freqlist_location.R
innitial formatting

@@ -3,7 +3,7 @@ install.packages('mclm')
 install.packages('here')
 install.packages('kableExtra')
 install.packages("leaflet")
-
+install.packages("quarto")
 
 library('tidyverse')
 library('mclm')
@@ -21,11 +21,20 @@ summary_data <- data %>%
   arrange(desc(Count)) %>%
   ungroup() %>% print(n=20)
 
-top_20_summary_data <- summary_data %>%
-  top_n(20, Count) %>%
-  ungroup() %>% print()
+summary_data %>% # also valid for top_scores_colloc
+  as_tibble() %>%
+  select(Place_Name, Count) %>% # select 4 columns
+  arrange(desc(Count)) %>%             # sort by PMI (descending) 
+  head(20) %>%                       # select top 30 rows
+  kbl(col.names = c("Place_Name", "Count")) %>% 
+  kable_minimal() %>% 
+  scroll_box(height = "400px")
 
 # Create a bar chart using ggplot2
+top_20_summary_data <- summary_data %>%
+  top_n(20, Count) %>%
+  ungroup()
+
 ggplot(top_20_summary_data, aes(x = reorder(Place_Name, -Count), y = Count)) +
   geom_bar(stat = "identity") +
   labs(x = "Place Name", y = "Count") +
@@ -51,47 +60,6 @@ m <- leaflet() %>%
 # Display the map
 m
 
-
-fpath_target <- here("geotext_indianregion.csv")
-fpath_ref <- here("wholebooktext.csv")
-fname
-# Read the CSV file
-data_target <- read_csv(fpath_target)
-data_ref <- read_csv(fpath_ref)
-
-
-# Preprocess the "Plain_text" column
-data_target$Text <- tolower(data_target$Text)
-data_ref$Text <- tolower(data_ref$Text)
-
-corpus_target <- unique(data_target$Text)
-corpus_ref <- unique(data_ref$Text)
-
-flist_target <- freqlist(corpus_target, as_text = TRUE) %>% print()
-flist_ref <- freqlist(corpus_ref, as_text = TRUE) %>% print()
-
-# calculate scores
-scores_kw <- assoc_scores(flist_target, flist_ref)
-
-# print scores, sorted by PMI
-print(scores_kw, sort_order = "PMI")
-print(scores_kw, sort_order = "G_signed")
-
-top_scores_kw <- scores_kw %>% 
[…]

### 2023-06-19 paper_quarto.qmd
19/6 update

@@
 library('leaflet')
-library('widgetframe')
 options(digits = 3)
@@
 
-widgetframe::frameWidget(m, width = "100%")
+m
 
@@
 
-As mentioned, the digitized text with geographical annotation is available through [TOPOSText](https://topostext.org/work/148 "Check Natural History on ToposText") project, I further scraped the full text and exported them in .txt as a \[reference corpus\](#\| label: ref-corpus), and also exported those with annotation of coordinates in a range of indian subcontinent as geographically related texts to India as a \[target corpus\](#tar-corpus).
+As mentioned, the digitized text with geographical annotation is available through [TOPOSText](https://topostext.org/work/148 "Check Natural History on ToposText") project, I further scraped the full text and exported them in .txt as a \![reference corpus\]{#ref-corpus}, and also exported those with annotation of coordinates in a range of Indian subcontinent as geographically related texts to India as a \![target corpus\]{#tar-corpus}.
 The scraping code can be accessed in the link.
@@
 
-The @ref-corpus consists of all texts in the encyclopedia, divided by paragraphs, has `r prettyNum(n_tokens(ref_flist))` tokens and `r n_types(ref_flist)` types, with the type-token ratio of `r round(n_types(ref_flist)/n_tokens(ref_flist), 2)`.
-
-And the @tar-corpus consists of all text related to Indian subcontinent (with coordinates in range of 8°4'N-37°6'N and 68°7'E to 97°25'E) , has `r prettyNum(n_tokens(tar_flist))` tokens and `r n_types(tar_flist)` types, with the type-token ratio of `r round(n_types(tar_flist)/n_tokens(tar_flist), 2)`.
-
-The tokens are separated by white space and in the analysis of this paper, all the punctuation marks are removed.
+> The @ref-corpus consists of all texts in the encyclopedia, divided by paragraphs, has `r prettyNum(n_tokens(ref_flist))` tokens and `r n_types(ref_flist)` types, with the type-token ratio of `r round(n_types(ref_flist)/n_tokens(ref_flist), 2)`.
+>
+> And the @tar-corpus consists of all text related to Indian subcontinent (with coordinates in range of 8°4'N-37°6'N and 68°7'E to 97°25'E) , has `r prettyNum(n_tokens(tar_flist))` tokens and `r n_types(tar_flist)` types, with the type-token ratio of `r round(n_types(tar_flist)/n_tokens(tar_flist), 2)`.
+>
+> The tokens are separated by white space and in the analysis of this paper, all the punctuation marks are removed.
 
@@
 
+::: {#tbl-kwtables .panel-tabset}
+## Sorted by PMI
+
 ```{r}
-#| label: tbl-kwtables
-#| tbl-cap: Top 30 Keywords of Indian related texts in Natural History
-#| tbl-subcap: 
-#|  - "Sorted by PMI"
-#|  - "Sorted by G_signed"
-#| layout-ncol: 2
 #| warning: false
@@
   head(30) %>%                       # select top 30 rows
-  kbl(col.names = c("Type", "Frequency", "PMI", "(Signed $G^{2}$)"))
+  kbl(col.names = c("Type", "Frequency", "PMI", r"(Signed $G^2$)"))%>% 
+  kable_minimal() %>% 
+  scroll_box(height = "400px")
+```
+
+## Sorted by G_signed
+
+```{r}
+#| warning: false
+#| echo: false
 
@@
   head(30) %>%                       # select top 30 rows
-  kbl(col.names = c("Type", "Frequency", "PMI", "(Signed $G^{2}$)"))
+  kbl(col.names = c("Type", "Frequency", "PMI", r"(Signed $G^2$)")) %>% 
+  kable_minimal() %>% 
+  scroll_box(height = "400px")
+```
+:::
+
+```{r}
+#| label: tbl-kwtables1
+#| tbl-cap: Top 30 Keywords of Indian related texts in Natural History
+#| tbl-subcap: 
+#|  - "Sorted by PMI"
+#|  - "Sorted by G_signed"
+#| layout-ncol: 2
+#| warning: false
+#| echo: false
+#| output: false
+
+top_scores_kw %>% # also valid for top_scores_colloc
+  as_tibble() %>%
+  select(type, a, PMI, G_signed) %>% # select 4 columns
+  arrange(desc(PMI)) %>%             # sort by PMI (descending) 
+  head(30) %>%                       # select top 30 rows
+  kbl(col.names = c("Type", "Frequency", "PMI", "r (Signed $G^{2}$)"))
+
+top_scores_kw %>% # also valid for top_scores_colloc
+  as_tibble() %>%
+  select(type, a, PMI, G_signed) %>% # select 4 columns
+  arrange(desc(G_signed)) %>%             # sort by PMI (descending) 
+  head(30) %>%                       # select top 30 rows
+  kbl(col.names = c("Type", "Frequency", "PMI", "r (Signed $G^{2}$)"))
 
@@
 
-@tbl-coltables shows the top 30 keywords in Indian related texts comparing to other context, respectively sorted by PMI and G_signed.
+@tbl-coltable_PMI and @tbl-coltable_Gsigned shows the top 30 keywords in Indian related texts comparing to other context, respectively sorted by PMI and G_signed.
+
+::: panel-tabset
+## Sorted by PMI
 
 ```{r}
-#| label: tbl-coltables
+#| label: tbl-coltable_PMI
+#| tbl-cap-location: top
+#| tbl-cap: Top 30 Keywords on Indian Related Text in Natural History (sorted by PMI)
+#| warning: false
+#| echo: false
+top_scores_colloc %>% 
+  as_tibble() %>%
+  select(type, a, PMI, G_signed) %>% # select 4 columns
+  arrange(desc(PMI)) %>%        # sort by G_signed (descending)  
+  head(30) %>%                       # select top 30 rows
+  kbl(col.names = c("Type", "Frequency", "PMI", "Signed G^2"))%>%
+  kable_minimal() %>% 
+  scroll_box(height = "400px")
+
+```
+
+## Sorted by G_signed
+
+```{r}
+#| label: tbl-coltable_Gsigned
+#| tbl-cap-location: top
+#| tbl-cap: Top 30 Keywords on Indian Related Text in Natural History (sorted by G_signed)
+#| warning: false
+#| echo: false
+
+top_scores_colloc %>% 
+  as_tibble() %>%
+  select(type, a, PMI, G_signed) %>% # select 4 columns
+  arrange(desc(G_signed)) %>%        # sort by G_signed (descending)  
+  head(30) %>%                       # select top 30 rows
+  kbl(col.names = c("Type", "Frequency", "PMI", "`r (Signed G^2^)`"))%>% 
+  kable_minimal() %>% 
+  scroll_box(height = "400px")
+
+```
+:::
+
+```{r}
+#| label: tbl-coltables1
 #| tbl-cap: Top 30 Collocates of word "India" in Natural History
@@
 #| warning: false
+#| echo: false
+#| output: false
 

### 2023-06-19 paper_quarto.qmd
tibble update

@@
 
-As mentioned, the digitized text with geographical annotation is available through [TOPOSText](https://topostext.org/work/148 "Check Natural History on ToposText") project, I further scraped the full text and exported them in .txt as a \![reference corpus\]{#ref-corpus}, and also exported those with annotation of coordinates in a range of Indian subcontinent as geographically related texts to India as a \![target corpus\]{#tar-corpus}.
+As mentioned, the digitized text with geographical annotation is available through [TOPOSText](https://topostext.org/work/148 "Check Natural History on ToposText") project, I further scraped the full text and exported them in .txt as a **reference corpus**, and also exported those with annotation of coordinates in a range of Indian subcontinent as geographically related texts to India as a **target corpus**.
 The scraping code can be accessed in the link.
@@
 
-> The @ref-corpus consists of all texts in the encyclopedia, divided by paragraphs, has `r prettyNum(n_tokens(ref_flist))` tokens and `r n_types(ref_flist)` types, with the type-token ratio of `r round(n_types(ref_flist)/n_tokens(ref_flist), 2)`.
->
-> And the @tar-corpus consists of all text related to Indian subcontinent (with coordinates in range of 8°4'N-37°6'N and 68°7'E to 97°25'E) , has `r prettyNum(n_tokens(tar_flist))` tokens and `r n_types(tar_flist)` types, with the type-token ratio of `r round(n_types(tar_flist)/n_tokens(tar_flist), 2)`.
->
-> The tokens are separated by white space and in the analysis of this paper, all the punctuation marks are removed.
+The **reference corpus** consists of all texts in the encyclopedia, divided by paragraphs, has `r prettyNum(n_tokens(ref_flist))` tokens and `r n_types(ref_flist)` types, with the type-token ratio of `r round(n_types(ref_flist)/n_tokens(ref_flist), 2)`.
+
+And the **target corpus** consists of all text related to Indian subcontinent (with coordinates in range of *8°4'N-37°6'N and 68°7'E to 97°25'E*) , has `r prettyNum(n_tokens(tar_flist))` tokens and `r n_types(tar_flist)` types, with the type-token ratio of `r round(n_types(tar_flist)/n_tokens(tar_flist), 2)`.
+
+The tokens are separated by white space and in the analysis of this paper, all the punctuation marks are removed.
 
@@
 
-@tbl-kwtables shows the top 30 keywords in Indian related texts comparing to other context, respectively sorted by PMI and G_signed.
+@tbl-kwtable_PMI and @tbl-kwtable_Gsigned shows the top 30 keywords in Indian related texts comparing to other context, respectively sorted by PMI and G_signed.
 
-::: {#tbl-kwtables .panel-tabset}
+::: panel-tabset
 ## Sorted by PMI
@@
 #| echo: false
+#| label: tbl-kwtable_PMI
+#| tbl-cap-location: top
+#| tbl-cap: Top 30 Keywords on Indian Related Text in Natural History (sorted by PMI)
 
@@
 #| echo: false
+#| label: tbl-kwtable_Gsigned
+#| tbl-cap-location: top
+#| tbl-cap: Top 30 Keywords on Indian Related Text in Natural History (sorted by G_Signed)
 
@@
 
-@tbl-coltable_PMI and @tbl-coltable_Gsigned shows the top 30 keywords in Indian related texts comparing to other context, respectively sorted by PMI and G_signed.
+@tbl-coltable_PMI and @tbl-coltable_Gsigned shows the top 30 collocates to the word "india" in the whole text, respectively sorted by PMI and G_signed.
 
@@
   head(30) %>%                       # select top 30 rows
-  kbl(col.names = c("Type", "Frequency", "PMI", "Signed G^2"))%>%
+  kbl(col.names = c("Type", "Frequency", "PMI", "Signed G^2^"))%>%
   kable_minimal() %>% 

### 2023-06-19 paper_quarto.qmd
20/6 update

@@
 
-top_scores_kw %>% # also valid for top_scores_colloc
+top_scores_kw %>% 
   as_tibble() %>%
@@
   head(30) %>%                       # select top 30 rows
-  kbl(col.names = c("Type", "Frequency", "PMI", r"(Signed $G^2$)"))%>% 
+  kbl(col.names = c("Type", "Frequency", "PMI", r"(Signed $G^2$)")) %>% 
   kable_minimal() %>% 

### 2023-06-19 freqlist_location.R
test table

@@ -148,7 +148,7 @@ top_scores_colloc %>% # also valid for top_scores_kw
   head(30) %>%                       # select top 30 rows
   kbl(col.names = c("Type", "Frequency", "PMI", r"(Signed $G^2$)")) %>% 
   kable_minimal() %>% 
-  scroll_box(height = "400px")
+  scroll_box(height = "400px") %>% print()
 
 top_scores_kw %>% # also valid for top_scores_colloc
   as_tibble() %>%
@@ -160,3 +160,17 @@ top_scores_kw %>% # also valid for top_scores_colloc
   scroll_box(height = "400px")
 
 quarto::render("paper_quarto.md", to = "html", verbose = TRUE)
+
+
+test_table <- data.frame(
+  Column1 = rnorm(1),
+  Column2 = rnorm(1),
+  Column3 = rnorm(1),
+  Column4 = rnorm(1)
+) %>% print()
+
+test_table %>% # also valid for top_scores_colloc
+  as_tibble() %>%                     # select top 30 rows
+  kbl(col.names = c("Type", "Frequency", "PMI", r"(Signed $G^2$)")) %>% 
+  kable_minimal() %>% 
+  scroll_box(height = "400px") %>% print()

### 2023-06-20 paper_quarto.qmd
test table
bibliography add

@@
 code-fold: true
+bibliography:
+  - bibliography.bib
+  - packages.bib
+csl: unified-style-sheet-for-linguistics.csl
 abstract: 'The paper applies the methodology of keyword analysis and collocation analysis in corpus linguistics to explore the possible topics of the text related to "India" in Natural History of Pliny the Elder.'
@@
 options(digits = 3)
+
+knitr::write_bib(
+  c("base", "mclm", "ggplot2", "tidyverse", "leaflet"),
+  here("packages.bib")
+)
 ```
@@
 
-When mapping the places with the annotated coordinates, as shown in @fig-map, India is the only one place that not in mediterranean region while having a rather high counts in the mentioned times.
+When mapping the places with the annotated coordinates, as shown in @fig-map, India is the only one place that not in Mediterranean region while having a rather high counts in the mentioned times.
 
@@
 
+`{tidyverse}`, `{mclm}` are the main packages used in this paper.
+
 # Keyword Analysis on India-related texts
@@
 
-@tbl-kwtable_PMI and @tbl-kwtable_Gsigned shows the top 30 keywords in Indian related texts comparing to other context, respectively sorted by PMI and G_signed.
+@tbl-kwtables below shows the top 30 keywords in Indian related texts comparing to other context, respectively sorted by PMI and G_signed.
 
-::: panel-tabset
+::: {#tbl-kwtables .panel-tabset}
 ## Sorted by PMI
@@
 #| tbl-cap-location: top
-#| tbl-cap: Top 30 Keywords on Indian Related Text in Natural History (sorted by PMI)
+#| tbl-cap: Top 30 collocates to the word "india" in Natural History (sorted by PMI)
 #| warning: false
@@
 #| tbl-cap-location: top
-#| tbl-cap: Top 30 Keywords on Indian Related Text in Natural History (sorted by G_signed)
+#| tbl-cap: Top 30 collocates to the word "india" in Natural History (sorted by G_signed)
 #| warning: false
@@
 Quarto enables you to weave together content and executable code into a finished document. To learn more about Quarto see <https://quarto.org>.
+
+```{quarto-cite}
+```

### 2023-06-20 paper_quarto.qmd
reference added

@@
 bibliography:
-  - bibliography.bib
+  - references.bib
   - packages.bib  
@@
 
-`{tidyverse}`, `{mclm}` are the main packages used in this paper.
+[@R-tidyverse] and [@R-mclm] [@R-base] [@R-ggplot2] [@R-leaflet] are the main packages used in this paper. [@dodd2021] [@nappo2017]
 
@@
   head(30) %>%                       # select top 30 rows
-  kbl(col.names = c("Type", "Frequency", "PMI", r"(Signed $G^2$)")) %>% 
+  kbl(col.names = c("Type", "Frequency", "PMI", r"(Signed $G^2$)"), escape = FALSE) %>% 
   kable_minimal() %>% 
@@
   head(30) %>%                       # select top 30 rows
-  kbl(col.names = c("Type", "Frequency", "PMI", "Signed G^2^"))%>%
+  kbl(col.names = c("Type", "Frequency", "PMI", r"(Signed $G^2$)"), escape = FALSE) %>%
   kable_minimal() %>% 
@@
   head(30) %>%                       # select top 30 rows
-  kbl(col.names = c("Type", "Frequency", "PMI", "`r (Signed G^2^)`"))%>% 
+  kbl(col.names = c("Type", "Frequency", "PMI", r"(Signed $G^2$)"), escape = FALSE) %>% 
   kable_minimal() %>% 
@@
 
-Quarto enables you to weave together content and executable code into a finished document. To learn more about Quarto see <https://quarto.org>.
-
-```{quarto-cite}
-```
+Trade related words (including important transportation milestones, trading goods and the description of the goods (colors, precious, etc.)) are more prone to be occur in the text related to India.
+It reflects the trading connection of the two empires, and also how the recognition of the other empire for the scholars of that period.

### 2023-06-20 freqlist_location.R

@@ -161,16 +161,3 @@ top_scores_kw %>% # also valid for top_scores_colloc
 
 quarto::render("paper_quarto.md", to = "html", verbose = TRUE)
 
-
-test_table <- data.frame(
-  Column1 = rnorm(1),
-  Column2 = rnorm(1),
-  Column3 = rnorm(1),
-  Column4 = rnorm(1)
-) %>% print()
-
-test_table %>% # also valid for top_scores_colloc
-  as_tibble() %>%                     # select top 30 rows
-  kbl(col.names = c("Type", "Frequency", "PMI", r"(Signed $G^2$)")) %>% 
-  kable_minimal() %>% 
-  scroll_box(height = "400px") %>% print()

### 2023-06-21 paper_quarto.qmd
keyword wordlist update

@@
 
-Natural History by Pliny the Elder is considered the very first encyclopedia in modern history.
-It not only showcased the actual merchant exchange of the Roman Empire, but also manifested the spatial imagination of Pliny the Elder and the referenced scholarships of that time.
+Pliny the Elder's "Natural History" stands as a seminal work in the history of encyclopedias, serving as a gateway to understanding the knowledge and worldview of ancient Rome.
+Beyond its role as a compendium of diverse subjects, the text provides a captivating glimpse into the actual merchant exchanges [@dodd2021] of the Roman Empire while shedding a light on the spatial imagination of Pliny and the scholarly references of his time [@nappo2017].
 
-The text of the whole book has been digitized and annotated with people's name and places' name and coordinates by [TOPOSText](https://topostext.org/the-project) project since 2012.
-By scraping the text as well as the geographical related annotations, the distribution of place names in the encyclopedia can be investigated, which will contribute to a comprehensive understanding of the spatial imagination of Pliny the Elder and the scholarships in his reference network.
+The text of the whole book has been digitized and annotated with people's name, places' name and coordinates by [TOPOSText](https://topostext.org/the-project) project since 2012.
+This invaluable resource allows for the creation of a dataset that includes both the textual contents and geographical annotations, which can be utilized to investigate the distribution of place names in the entire text and examine the frequencies and patterns of geographically-related content.
 
-@fig-geoname shows the Top 20 distinct geographical names mentioned in Natural History.
+As a starting point, @fig-geoname reveals the Top 20 distinct geographical names mentioned within the text.
 
@@
 #| fig-cap: Bar Chart for Top 20 Distinct Place Names Mentioned in Natural History
+#| fig-cap-location: top
 #| warning: false
@@
 
-When mapping the places with the annotated coordinates, as shown in @fig-map, India is the only one place that not in Mediterranean region while having a rather high counts in the mentioned times.
+An intriguing observation from this analysis, as depicted in @fig-map, is the prominence of India---a region outside the Mediterranean---despite its high frequency of mentions.
 
@@
 #| fig-cap: Mapping of geographical names mentioned in Natural History
+#| fig-cap-location: top
 #| warning: false
@@
 
-In this regards, this paper tries to further explore what themes are referred around the text about India region with application of keyword analysis and collocation analysis methods in corpus linguistics.
+Building upon this observation, this paper aims to delve deeper into the themes associated with the India region by employing keyword analysis and collocation analysis methods within the framework of corpus linguistics.
+
+The analysis is conducted in R environment [@R-base], and the main corpus linguistics anlysing methods are applied through functions from [mclm](https://masterclm.github.io/mclm/) [@R-mclm] package.
+In addition, [tidyverse](https://www.tidyverse.org/) [@R-tidyverse] and [leaflet](https://rstudio.github.io/leaflet/) [@R-leaflet] are used for data manipulation and visualisation.
 
@@
 
-As mentioned, the digitized text with geographical annotation is available through [TOPOSText](https://topostext.org/work/148 "Check Natural History on ToposText") project, I further scraped the full text and exported them in .txt as a **reference corpus**, and also exported those with annotation of coordinates in a range of Indian subcontinent as geographically related texts to India as a **target corpus**.
-The scraping code can be accessed in the link.
+As mentioned earlier, the digitized text of "Natural History" with geographical annotations is readily accessible through the [TOPOSText](https://topostext.org/work/148 "Check Natural History on ToposText") project.
+In order to facilitate the analysis, I conducted additional scraping of the full text, exporting it as a **reference corpus** in .txt format.
+Furthermore, I extracted the texts specifically associated with the Indian subcontinent, utilizing the annotated coordinates, creating a **target corpus** of geographically related texts focused on India.
+The scraping code can be found in the link: .
 
@@
 
-The tokens are separated by white space and in the analysis of this paper, all the punctuation marks are removed.
-
-[@R-tidyverse] and [@R-mclm] [@R-base] [@R-ggplot2] [@R-leaflet] are the main packages used in this paper. [@dodd2021] [@nappo2017]
+The punctuation marks are removed in the tokenization process.
 
 # Keyword Analysis on India-related texts
+
+The frequency list of the **target corpus** (Indian subcontinent related texts) and **reference corpus** (whole text) are generated respectively.
+And the association scores are calculated and filtered for those returning both PMI and $G^2$ gaining 2 or higher, in order to get the statisticly most significant keyword in India-related texts comparing to the reference corpus.
+
+When calculating the word frequency in the **target corpus**, the word "india" itself is removed from the token in order to get more descriptive words in the corpus, which will be more efficient in implying the possible thematic keyword in the **target corpus**.
 
@@
   freqlist(
-    re_token_splitter = r"--[(?xi)    \s+   ]--", # whitespace as token splitter
     re_token_transf_in = "[[:punct:]]", # Match punctuation marks
-    token_transf_out = "" # Replace punctuation marks with an empty string
+    token_transf_out = "", # Replace punctuation marks with an empty string
+    re_drop_token = "india"
   )
@@
 flist_ref <- fnames_wholetext %>%
-  freqlist(re_token_splitter = r"--[(?xi)    \s+   ]--", # whitespace as token splitter
+  freqlist(
     re_token_transf_in = "[[:punct:]]", # Match punctuation marks
-           token_transf_out = "")
+    token_transf_out = ""
+  )
 
@@
 
-@tbl-kwtables below shows the top 30 keywords in Indian related texts comparing to other context, respectively sorted by PMI and G_signed.
+Tables below shows the top 20 keywords in Indian related texts comparing to other context, respectively sorted by PMI (@tbl-kwtable_PMI) and G_signed (@tbl-kwtable_Gsigned).
 
-::: {#tbl-kwtables .panel-tabset}
+::: panel-tabset
 ## Sorted by PMI
@@
 #| tbl-cap-location: top
-#| tbl-cap: Top 30 Keywords on Indian Related Text in Natural History (sorted by PMI)
+#| tbl-cap: Top 20 Keywords on Indian Related Text in Natural History (sorted by PMI)
 
@@
   as_tibble() %>%
-  select(type, a, PMI, G_signed) %>% # select 4 columns
-  arrange(desc(PMI)) %>%             # sort by PMI (descending) 
-  head(30) %>%                       # select top 30 rows
+  select(type, a, PMI, G_signed) %>% 
+  arrange(desc(PMI)) %>%             
+  head(20) %>%                       
   kbl(col.names = c("Type", "Frequency", "PMI", r"(Signed $G^2$)")) %>% 
@@
 #| tbl-cap-location: top
-#| tbl-cap: Top 30 Keywords on Indian Related Text in Natural History (sorted by G_Signed)
+#| tbl-cap: Top 20 Keywords on Indian Related Text in Natural History (sorted by G_Signed)
 
@@
   arrange(desc(G_signed)) %>%             # sort by PMI (descending) 
-  head(30) %>%                       # select top 30 rows
-  kbl(col.names = c("Type", "Frequency", "PMI", r"(Signed $G^2$)"), escape = FALSE) %>% 
+  head(20) %>%                       # select top 30 rows
+  kbl(col.names = c("Type", "Frequency", "PMI", r"(Signed $G^2$)")) %>% 
   kable_minimal() %>% 
@@
 
+@tbl-kwPMI below shows the explanation of the top 20 keywords in Indian related text.
+
 ```{r}
-#| label: tbl-kwtables1
-#| tbl-cap: Top 30 Keywords of Indian related texts in Natural History
-#| tbl-subcap: 
-#|  - "Sorted by PMI"
-#|  - "Sorted by G_signed"
-#| layout-ncol: 2
 #| warning: false
-#| echo: false
-#| output: false
+#| label: tbl-kwPMI
 
-top_scores_kw %>% # also valid for top_scores_colloc
-  as_tibble() %>%
-  select(type, a, PMI, G_signed) %>% # select 4 columns
-  arrange(desc(PMI)) %>%             # sort by PMI (descending) 
-  head(30) %>%                       # select top 30 rows
-  kbl(col.names = c("Type", "Frequency", "PMI", "r (Signed $G^{2}$)"))
-
-top_scores_kw %>% # also valid for top_scores_colloc
-  as_tibble() %>%
-  select(type, a, PMI, G_signed) %>% # select 4 columns
-  arrange(desc(G_signed)) %>%             # sort by PMI (descending) 
-  head(30) %>%                       # select top 30 rows
-  kbl(col.names = c("Type", "Frequency", "PMI", "r (Signed $G^{2}$)"))
+keyword_PMI_tibble <- tibble(
+  Word = c("ganges", "beryls", "ichthyophagi", "megasthenes", "obsidian", "bdellium", "agates", "callaina", "condensation", "gerra", "jomanes", "nonius", "prasii", "alia", "carnelian", "cophes", "hypasis", "merchandize", "peppertree", "sacae"),
+  Type = c("Proper Noun", "Noun", "Plural Noun", "Proper Noun", "Noun", "Noun", "Noun", "Noun/Proper Noun", "Noun", "Noun/Proper Noun", "Noun/Proper Noun", "Noun/Proper Noun", "Noun/Proper Noun", "Adverb", "Noun", "Noun/Proper Noun", "Noun/Proper Noun", "Noun", "Noun", "Noun/Proper Noun"),
+  Exp = c("a major river in India", "a type of gemstone", "a group of people who primarily subsist on fish", "a Greek historian and diplomat", "a type of volcanic glass", "a fragrant resin obtained from certain trees", "a type of semiprecious gemstone", "pale green precious stone (lat)", "the process of vapor turning into a liquid state", "war (lat)", "a Roman nomen gentile, gens or 'family name'", "a Roman nomen gentile, gens or 'family name'", "prase, green coloured gem", "by another / different way / route", "a reddish-brown variety of chalcedony", "a river that rises in the ancient Paropamise range, eventually falling into the Indus river near its confluence with the Cophes river", "a river in north India", "goods or commodities", "a tree that produces peppercorns", "the easternmost nation of Elibe, situated to the south of Ilia and the north of Bern")
+) %>% print()
 

### 2023-06-21 freqlist_location.R

@@ -4,6 +4,11 @@ install.packages('here')
 install.packages('kableExtra')
 install.packages("leaflet")
 install.packages("quarto")
+install.packages("topicmodels")
+install.packages("tm")
+
+library(topicmodels)
+library(tm)
 
 library('tidyverse')
 library('mclm')
@@ -57,8 +62,7 @@ m <- leaflet() %>%
     popup = paste("Place Name:", top_20_summary_data$Place_Name, "<br>",
                   "Count:", top_20_summary_data$Count)
   )
-# Display the map
-m
+
 
 corpus_folder <- here("NH_wholetext")
 fnames_wholetext <- get_fnames(corpus_folder) %>% 
@@ -79,17 +83,15 @@ n_types(tar_flist)
 
 # build frequency list for target corpus
 flist_target <- fnames_indiatext %>%
-  freqlist(
-    re_token_splitter = r"--[(?xi)    \s+   ]--", # whitespace as token splitter
-    re_token_transf_in = "[[:punct:]]", # Match punctuation marks
-    token_transf_out = "" # Replace punctuation marks with an empty string
-  ) %>%
+  freqlist(re_token_transf_in = "[[:punct:]]", # Match punctuation marks
+           token_transf_out = "",# Replace punctuation marks with an empty string
+           re_drop_token = "india"
+    ) %>%
   print()
 
 # build frequency list for reference corpus
 flist_ref <- fnames_wholetext %>%
-  freqlist(re_token_splitter = r"--[(?xi)    \s+   ]--", # whitespace as token splitter
-           re_token_transf_in = "[[:punct:]]", # Match punctuation marks
+  freqlist(re_token_transf_in = "[[:punct:]]", # Match punctuation marks
            token_transf_out = "") %>%
   print()
 
@@ -101,6 +103,27 @@ print(scores_kw, sort_order = "PMI")
 
 # print scores, sorted by G_signed
 print(scores_kw, sort_order = "G_signed")
+
+
+keyword_PMI_tibble <- tibble(
+  Word = c("ganges", "beryls", "ichthyophagi", "megasthenes", "obsidian", "bdellium", "agates", "callaina", "condensation", "gerra", "jomanes", "nonius", "prasii", "alia", "carnelian", "cophes", "hypasis", "merchandize", "peppertree", "sacae"),
[…]

### 2023-06-21 paper_quarto.qmd
concordence table added

@@
 Pliny the Elder's "Natural History" stands as a seminal work in the history of encyclopedias, serving as a gateway to understanding the knowledge and worldview of ancient Rome.
-Beyond its role as a compendium of diverse subjects, the text provides a captivating glimpse into the actual merchant exchanges [@dodd2021] of the Roman Empire while shedding a light on the spatial imagination of Pliny and the scholarly references of his time [@nappo2017].
+Beyond its role as a compendium of diverse subjects, the text provides a captivating glimpse into the actual merchant exchanges [@dodd2021] of the Roman Empire while shedding a light on the spatial imagination of Pliny and the scholarly references of his time [@plinyth2011].
 
@@
 The frequency list of the **target corpus** (Indian subcontinent related texts) and **reference corpus** (whole text) are generated respectively.
-And the association scores are calculated and filtered for those returning both PMI and $G^2$ gaining 2 or higher, in order to get the statisticly most significant keyword in India-related texts comparing to the reference corpus.
+And the association scores are calculated and filtered for those returning both PMI and $G^2$ gaining 2 or higher (in which criteria indicating the words having an at least four times higher probability than that in all the data taken together, as well as having a confirming evidence statistically [@methods]), in order to get the statistically most significant keyword in India-related texts comparing to the reference corpus.
 
@@
 
-Tables below shows the top 20 keywords in Indian related texts comparing to other context, respectively sorted by PMI (@tbl-kwtable_PMI) and G_signed (@tbl-kwtable_Gsigned).
+Tables below shows the top 20 keywords in Indian related texts comparing to the entire texts in the encyclopedia, respectively sorted by PMI (@tbl-kwtable_PMI) and G_signed (@tbl-kwtable_Gsigned).
 
@@
   select(type, a, PMI, G_signed) %>% 
-  arrange(desc(PMI)) %>%             
-  head(20) %>%                       
+  slice_max(order_by = PMI, n = 20, with_ties = TRUE) %>%                       
   kbl(col.names = c("Type", "Frequency", "PMI", r"(Signed $G^2$)")) %>% 
@@
   as_tibble() %>%
-  select(type, a, PMI, G_signed) %>% # select 4 columns
-  arrange(desc(G_signed)) %>%             # sort by PMI (descending) 
-  head(20) %>%                       # select top 30 rows
+  select(type, a, PMI, G_signed) %>%         # sort by PMI (descending) 
+  slice_max(order_by = G_signed, n = 20, with_ties = TRUE) %>%   # select top 30 rows
   kbl(col.names = c("Type", "Frequency", "PMI", r"(Signed $G^2$)")) %>% 
@@
 
-@tbl-kwPMI below shows the explanation of the top 20 keywords in Indian related text.
+As **PMI Score** is seen as the indicator for keyword analysis, the top 20 keywords sorted by PMI were further checked of the meaning and tagged of its type manually.
+@tbl-kwlist below shows the explanation of the top 20 keywords in Indian related text.
 
@@
 #| warning: false
-#| label: tbl-kwPMI
+#| echo: false
+#| label: tbl-kwlist
+#| tbl-cap: Top 20 keywords with meaning sorted by PMI
+#| tbl-cap-location: top
 
-keyword_PMI_tibble <- tibble(
-  Word = c("ganges", "beryls", "ichthyophagi", "megasthenes", "obsidian", "bdellium", "agates", "callaina", "condensation", "gerra", "jomanes", "nonius", "prasii", "alia", "carnelian", "cophes", "hypasis", "merchandize", "peppertree", "sacae"),
-  Type = c("Proper Noun", "Noun", "Plural Noun", "Proper Noun", "Noun", "Noun", "Noun", "Noun/Proper Noun", "Noun", "Noun/Proper Noun", "Noun/Proper Noun", "Noun/Proper Noun", "Noun/Proper Noun", "Adverb", "Noun", "Noun/Proper Noun", "Noun/Proper Noun", "Noun", "Noun", "Noun/Proper Noun"),
-  Exp = c("a major river in India", "a type of gemstone", "a group of people who primarily subsist on fish", "a Greek historian and diplomat", "a type of volcanic glass", "a fragrant resin obtained from certain trees", "a type of semiprecious gemstone", "pale green precious stone (lat)", "the process of vapor turning into a liquid state", "war (lat)", "a Roman nomen gentile, gens or 'family name'", "a Roman nomen gentile, gens or 'family name'", "prase, green coloured gem", "by another / different way / route", "a reddish-brown variety of chalcedony", "a river that rises in the ancient Paropamise range, eventually falling into the Indus river near its confluence with the Cophes river", "a river in north India", "goods or commodities", "a tree that produces peppercorns", "the easternmost nation of Elibe, situated to the south of Ilia and the north of Bern")
-) %>% print()
+keyword_PMI_list <- data.frame(
+  Word = c("ganges", "beryls", "ichthyophagi", "megasthenes", "obsidian", "bdellium", "agates", "callaina", "condensation", "gerra", "jomanes", "nonius", "prasii", "alia", "carnelian", "cophes", "hypasis", "merchandize", "peppertree", "sacae", "sandastros", "thornbush"),
+  Exp = c("a major river in India", "a type of gemstone", "a group of people who primarily subsist on fish", "a Greek historian and diplomat", "a type of volcanic glass", "a fragrant resin obtained from certain trees", "a type of semiprecious gemstone", "pale green precious stone (lat)", "the process of vapor turning into a liquid state", "war (lat)", "a Roman nomen gentile, gens or \"family name\"", "a Roman nomen gentile, gens or \"family name\"", "prase, green coloured gem", "by another / different way / route (lat)", "a reddish-brown variety of chalcedony", "a river that rises in the ancient Paropamise range, eventually falling into the Indus river near its confluence with the Cophes river", "a river in north India", "goods or commodities", "a tree that produces peppercorns", "the easternmost nation of Elibe, situated to the south of Ilia and the north of Bern", "a precious stone found in India and Arabia", "any of many thorny or spiny shrubs and bushes"),
+  Tag = c("river", "goods", "people", "people", "goods", "goods", "goods", "goods", "activity", "activity", "people", "people", "goods", "route", "goods", "river", "river", "goods", "tree", "river", "goods", "tree"),
+  Sub_tag = c("N/A", "stone", "group of people", "famous people", "others", "others", "stone", "stone", "producing activity", "N/A", "human name", "human name", "stone", "N/A", "stone", "N/A", "N/A", "general", "origin of goods", "N/A", "stone", "N/A")
+)
 
+keyword_PMI_list %>% 
+  as_tibble() %>%
+  select(Word, Exp, Tag, Sub_tag) %>%                        
+  kbl(col.names = c("Word", "Exp", "Tag", "Sub_tag")) %>% 
+  kable_minimal()
+```
+
+As the distribution plot of categories @fig-kwtype manifested, most keywords about Indian related texts in Natural History have a potential topic of goods (especially precious stones), and also people (both tribes and famous diplomats) and rivers in India (carrying the important role of origin of goods or transportation routes), which incorporates the investigation in [@nappo2017].
+
+```{r}
+#| warning: false
+#| echo: false
+#| label: fig-kwtype
+#| fig-cap: Top 20 keywords type distribution
+#| fig-cap-location: top
+
+tag_counts <- keyword_PMI_list %>%
+  count(Tag) %>%
+  arrange(desc(n))
+
+# Plot the tag distribution
+ggplot(tag_counts, aes(x = n, y = reorder(Tag, -n), fill = Tag)) +
+  geom_bar(stat = "identity") +
+  labs(x = "Count", y = "Tag", fill = "Tag") +
+  theme_minimal() +
+  coord_flip()
 ```
@@
 # Collocation Analysis on "India" in the whole corpus
+
+In addition to the investigation on the keywords in the "Indian" related texts, it is also worthwhile having a look at what words collocated when Pliny the Elder referred to the word "India".
+
+By indicating "india" as the target item for the analysis through the function of [surf_cooc](https://masterclm.github.io/mclm/reference/create_cooc.html) in [@R-mclm] and removing the punctuation marks, similarly to the Keyword Analysis criteria chosen above, collocation scores for co-text of both right and left side of "india" are calculated and filtered with those with both PMI and G_signed scores as 2 or above to get the prominent collocates of "india", in order to get an concrete overview of the discourse and recognization of Pliny the Elder to "India".
 
@@
   surf_cooc("(?xi)  ^ india $", 
-            re_token_splitter = r"--[(?xi)    \s+   ]--", # whitespace as token splitter
             re_token_transf_in = "[[:punct:]]", # Match punctuation marks
@@
 
-@tbl-coltable_PMI and @tbl-coltable_Gsigned shows the top 30 collocates to the word "india" in the whole text, respectively sorted by PMI and G_signed.
+@tbl-coltable_Gsigned and @tbl-coltable_PMI shows the top 20 collocates to the word "india" in the whole text, respectively sorted by PMI and G_signed.
 
 ::: panel-tabset
-## Sorted by PMI
+## Sorted by G_singed
 
 ```{r}
-#| label: tbl-coltable_PMI
+#| label: tbl-coltable_Gsigned
 #| tbl-cap-location: top
-#| tbl-cap: Top 30 collocates to the word "india" in Natural History (sorted by PMI)
+#| tbl-cap: Top 20 collocates to the word "india" in Natural History (sorted by PMI)
 #| warning: false
@@
   as_tibble() %>%
-  select(type, a, PMI, G_signed) %>% # select 4 columns
-  arrange(desc(PMI)) %>%        # sort by G_signed (descending)  
-  head(30) %>%                       # select top 30 rows
+  select(type, a, PMI, G_signed) %>% 
+  slice_max(order_by = G_signed, n = 20, with_ties = TRUE) %>%
   kbl(col.names = c("Type", "Frequency", "PMI", r"(Signed $G^2$)"), escape = FALSE) %>%
@@
 
-## Sorted by G_signed
+## Sorted by PMI
 
 ```{r}
-#| label: tbl-coltable_Gsigned
+#| label: tbl-coltable_PMI
 #| tbl-cap-location: top
-#| tbl-cap: Top 30 collocates to the word "india" in Natural History (sorted by G_signed)
+#| tbl-cap: Top 20 collocates to the word "india" in Natural History (sorted by PMI)
 #| warning: false
@@
   as_tibble() %>%
-  select(type, a, PMI, G_signed) %>% # select 4 columns
-  arrange(desc(G_signed)) %>%        # sort by G_signed (descending)  
-  head(30) %>%                       # select top 30 rows
+  select(type, a, PMI, G_signed) %>%
+  slice_max(order_by = PMI, n = 20, with_ties = TRUE) %>% 
   kbl(col.names = c("Type", "Frequency", "PMI", r"(Signed $G^2$)"), escape = FALSE) %>% 
@@
 
+As the returned $G^2$ indicates the strongness of evidence of the independency of the two words,
+
+In addition, as shown in @tbl-concordance, with the concordance table of word "india" providing more details about the context of \"India\".
+
 ```{r}
-#| label: tbl-coltables1
-#| tbl-cap: Top 30 Collocates of word "India" in Natural History
-#| tbl-subcap: 
-#|  - "Sorted by PMI"
-#|  - "Sorted by G_signed"
-#| layout-ncol: 2
+#| label: tbl-concordance
+#| tbl-cap-location: top
+#| tbl-cap: Concordance table of word "india" in Natural History
 #| warning: false
 #| echo: false
-#| output: false
 
-top_scores_colloc %>% 
+conc_data <- conc(fnames_wholetext, '\\bindia\\b')
+
+conc_data %>%
   as_tibble() %>%
-  select(type, a, PMI, G_signed) %>% # select 4 columns
-  arrange(desc(PMI)) %>%        # sort by G_signed (descending)  
-  head(30) %>%                       # select top 30 rows
-  kbl(col.names = c("Type", "Frequency", "PMI", "(Signed $G^{2}$)"))
-
-top_scores_colloc %>% 
-  as_tibble() %>%
-  select(type, a, PMI, G_signed) %>% # select 4 columns
-  arrange(desc(G_signed)) %>%        # sort by G_signed (descending)  
-  head(30) %>%                       # select top 30 rows
-  kbl(col.names = c("Type", "Frequency", "PMI", "(Signed $G^{2}$)"))
-
+  select(source, left, match, right) %>%
+  mutate(
+    source = short_names(source),
+    book = as.integer(gsub("^(\\d+).*", "\\1", source)),
+    chapter = as.numeric(gsub("^\\d+\\.(\\d+)\\.\\d+_text$", "\\1", source)),
+    paragraph = as.numeric(gsub("^\\d+\\.\\d+\\.(\\d+)_text$", "\\1", source))
+  ) %>%
+  arrange(book, chapter, paragraph) %>%
+  select(book, chapter, paragraph, left, match, right) %>%
+  kbl(align = c("r", "r", "r", "c", "l", "l", "l")) %>%
+  kable_paper(font_size = 15) %>%
+  scroll_box(height = "400px")
 ```

### 2023-06-21 freqlist_location.R

@@ -4,11 +4,7 @@ install.packages('here')
 install.packages('kableExtra')
 install.packages("leaflet")
 install.packages("quarto")
-install.packages("topicmodels")
-install.packages("tm")
 
-library(topicmodels)
-library(tm)
 
 library('tidyverse')
 library('mclm')
@@ -24,16 +20,8 @@ summary_data <- data %>%
   group_by(ToposText_ID, Place_Name, Lat, Long) %>%
   summarise(Count = n()) %>%
   arrange(desc(Count)) %>%
-  ungroup() %>% print(n=20)
+  ungroup() 
 
-summary_data %>% # also valid for top_scores_colloc
-  as_tibble() %>%
-  select(Place_Name, Count) %>% # select 4 columns
-  arrange(desc(Count)) %>%             # sort by PMI (descending) 
-  head(20) %>%                       # select top 30 rows
-  kbl(col.names = c("Place_Name", "Count")) %>% 
-  kable_minimal() %>% 
-  scroll_box(height = "400px")
 
 # Create a bar chart using ggplot2
 top_20_summary_data <- summary_data %>%
@@ -64,36 +52,32 @@ m <- leaflet() %>%
   )
 
 
-corpus_folder <- here("NH_wholetext")
-fnames_wholetext <- get_fnames(corpus_folder) %>% 
+corpus_folder_whole <- here("NH_wholetext")
+fnames_wholetext <- get_fnames(corpus_folder_whole) %>% 
   keep_re("[.]txt")
 
-print(fnames_wholetext, 10, hide_path = corpus_folder)
+print(fnames_wholetext, 10, hide_path = corpus_folder_whole)
 
-corpus_folder <- here("NH_geotext_india")
-fnames_indiatext <- get_fnames(corpus_folder) %>% 
+corpus_folder_in <- here("NH_geotext_india")
+fnames_indiatext <- get_fnames(corpus_folder_in) %>% 
   keep_re("[.]txt")
 
-print(fnames_indiatext, 10, hide_path = corpus_folder)
+print(fnames_indiatext, 10, hide_path = corpus_folder_in)
 
-prettyNum(n_tokens(ref_flist))
-n_types(ref_flist)
-prettyNum(n_tokens(tar_flist))
-n_types(tar_flist)
+ref_flist <- freqlist(fnames_wholetext, re_token_splitter = re("\\s+"))
+tar_flist <- freqlist(fnames_indiatext, re_token_splitter = re("\\s+"))
 
[…]

### 2023-06-22 paper_quarto.qmd
footnote added

@@
 Furthermore, I extracted the texts specifically associated with the Indian subcontinent, utilizing the annotated coordinates, creating a **target corpus** of geographically related texts focused on India.
-The scraping code can be found in the link: .
+The scraping was conducted with [beautifulsoup](https://www.crummy.com/software/BeautifulSoup/bs4/doc/) library in python, the [code](https://github.com/lizaodawn/zhuang/blob/papertry/Natural%20History_corpus%20scrape.ipynb) can be referred by click.[^1]
+
+[^1]: Since the paper is a pilot exploration of my master thesis, I used the scraped corpus already scraped with python.
 
@@
 
-In addition, as shown in @tbl-concordance, with the concordance table of word "india" providing more details about the context of \"India\".
+In addition, as shown in @tbl-concordance, with the concordance table of word "india" providing more details about the context of "India".
 

### 2023-06-22 paper_quarto.qmd
first completed draft

--- 2023-06-21 paper_quarto.qmd
@@
 title: "Keyword and Collocation analysis on India-related text of Natural History"
-author: "Lizao Zhuang (Dawn) r0914937"
+author: "Dawn, Lizao Zhuang (r0914937)"
 format: 
@@
 csl: unified-style-sheet-for-linguistics.csl
-abstract: 'The paper applies the methodology of keyword analysis and collocation analysis in corpus linguistics to explore the possible topics of the text related to "India" in Natural History of Pliny the Elder.'
+abstract: 'This paper presents a comprehensive analysis of keywords and collocates related to India in a corpus of Natural History by Pliny the Elder.
+The study focuses on uncovering prominent themes and topics associated with India in the context of the book.
+The research employs keyword analysis and collocate examination techniques to reveal significant insights into the perception and imagination of India, as a competent counterpart to the Roman Empire, by Pliny the Elder and the scholars of his time.'
 ---
@@
 
-Pliny the Elder's "Natural History" stands as a seminal work in the history of encyclopedias, serving as a gateway to understanding the knowledge and worldview of ancient Rome.
+Pliny the Elder's *Natural History* stands as a seminal work in the history of encyclopedias, serving as a gateway to understanding the knowledge and worldview of ancient Rome.
 Beyond its role as a compendium of diverse subjects, the text provides a captivating glimpse into the actual merchant exchanges [@dodd2021] of the Roman Empire while shedding a light on the spatial imagination of Pliny and the scholarly references of his time [@plinyth2011].
@@
 
-Building upon this observation, this paper aims to delve deeper into the themes associated with the India region by employing keyword analysis and collocation analysis methods within the framework of corpus linguistics.
+Building upon this observation, this paper aims to delve deeper into the themes associated with the India region referred in the text by employing keyword analysis and collocation analysis methods within the framework of corpus linguistics.
 
-The analysis is conducted in R environment [@R-base], and the main corpus linguistics anlysing methods are applied through functions from [mclm](https://masterclm.github.io/mclm/) [@R-mclm] package.
+The analysis is conducted in R environment [@R-base], and the main anlysing methods are applied through functions from [mclm](https://masterclm.github.io/mclm/) [@R-mclm] package.
 In addition, [tidyverse](https://www.tidyverse.org/) [@R-tidyverse] and [leaflet](https://rstudio.github.io/leaflet/) [@R-leaflet] are used for data manipulation and visualisation.
@@
 
-As mentioned earlier, the digitized text of "Natural History" with geographical annotations is readily accessible through the [TOPOSText](https://topostext.org/work/148 "Check Natural History on ToposText") project.
-In order to facilitate the analysis, I conducted additional scraping of the full text, exporting it as a **reference corpus** in .txt format.
+As mentioned earlier, the digitized text of *Natural History* with geographical annotations is readily accessible through the [TOPOSText](https://topostext.org/work/148 "Check Natural History on ToposText") project.
+In order to facilitate the analysis, I conducted a scraping of the full text, exporting it as a **reference corpus** in .txt format.
 Furthermore, I extracted the texts specifically associated with the Indian subcontinent, utilizing the annotated coordinates, creating a **target corpus** of geographically related texts focused on India.
-The scraping code can be found in the link: .
+The scraping was conducted with [Beautiful Soup](https://www.crummy.com/software/BeautifulSoup/bs4/doc/) library in Python, and the [code](https://github.com/lizaodawn/zhuang/blob/papertry/Natural%20History_corpus%20scrape.ipynb) is uploaded to the same repository of the project.[^1]
+
+[^1]: As this paper represents a preliminary investigation for my master's thesis, I utilized the corpus that had already been scraped using Python.
 
@@
 
-The **reference corpus** consists of all texts in the encyclopedia, divided by paragraphs, has `r prettyNum(n_tokens(ref_flist))` tokens and `r n_types(ref_flist)` types, with the type-token ratio of `r round(n_types(ref_flist)/n_tokens(ref_flist), 2)`.
+The **target corpus** consists of all text related to Indian subcontinent (with coordinates in range of *8°4'N-37°6'N and 68°7'E to 97°25'E*), segregated by paragraphs, containing `r prettyNum(n_tokens(tar_flist))` tokens and `r n_types(tar_flist)` types, with the type-token ratio of `r round(n_types(tar_flist)/n_tokens(tar_flist), 2)`.
 
-And the **target corpus** consists of all text related to Indian subcontinent (with coordinates in range of *8°4'N-37°6'N and 68°7'E to 97°25'E*) , has `r prettyNum(n_tokens(tar_flist))` tokens and `r n_types(tar_flist)` types, with the type-token ratio of `r round(n_types(tar_flist)/n_tokens(tar_flist), 2)`.
+And the **reference corpus** consists of all texts in *Natural History*, segregated by paragraphs, consisting of `r prettyNum(n_tokens(ref_flist))` tokens and `r n_types(ref_flist)` types, with the type-token ratio of `r round(n_types(ref_flist)/n_tokens(ref_flist), 2)`.
 
@@
 
-# Keyword Analysis on India-related texts
+# Keyword analysis on India-related texts
 
-The frequency list of the **target corpus** (Indian subcontinent related texts) and **reference corpus** (whole text) are generated respectively.
-And the association scores are calculated and filtered for those returning both PMI and $G^2$ gaining 2 or higher (in which criteria indicating the words having an at least four times higher probability than that in all the data taken together, as well as having a confirming evidence statistically [@methods]), in order to get the statistically most significant keyword in India-related texts comparing to the reference corpus.
+As mentioned, the method of keyword analysis could help with a further discuss about the prominent theme and topic in the India-related texts.
 
-When calculating the word frequency in the **target corpus**, the word "india" itself is removed from the token in order to get more descriptive words in the corpus, which will be more efficient in implying the possible thematic keyword in the **target corpus**.
+The frequency lists for the **target corpus** (Indian subcontinent related texts) and **reference corpus** (whole text) are generated respectively, and the association scores are calculated through the [assoc_scores](https://masterclm.github.io/mclm/reference/assoc_scores.html) function.
+The association score is filtered based on the criteira of both PMI and $G^2$ scores, requiring a minimum score of 2.
+This criterion ensures that the selected words have a probability at least four times higher than the overall data, along with statistically significant supporting evidence [@methods], allowing to identify the most statistically significant keywords in India-related texts when compared to the reference corpus.
+
+During the calculation of word frequencies in the **target corpus**, the specific word "India" itself was excluded from the analysis.
+This exclusion was intentional, aiming to focus on more descriptive words within the corpus and efficiently identify potential thematic keywords in the **target corpus**.
 
@@
 
-Tables below shows the top 20 keywords in Indian related texts comparing to the entire texts in the encyclopedia, respectively sorted by PMI (@tbl-kwtable_PMI) and G_signed (@tbl-kwtable_Gsigned).
+The following tables present the top 20 keywords in India-related texts as compared to the entire texts in *Natural History*.
+They are sorted based on their PMI (@tbl-kwtable_PMI) and G_signed scores (@tbl-kwtable_Gsigned), respectively.
+The initial sorting was carried out based on the PMI scores (@tbl-kwtable_PMI), since the it serves as a crucial indicator for measuring the keyness of words.
 
@@
 
-As **PMI Score** is seen as the indicator for keyword analysis, the top 20 keywords sorted by PMI were further checked of the meaning and tagged of its type manually.
-@tbl-kwlist below shows the explanation of the top 20 keywords in Indian related text.
+From these keywords, a manual examination was performed to determine their meaning and assign appropriate tags as based on their category.
+The resulting explanations for the top 20 keywords, sorted by PMI, can be found in @tbl-kwlist below.
 
@@
   select(Word, Exp, Tag, Sub_tag) %>%                        
-  kbl(col.names = c("Word", "Exp", "Tag", "Sub_tag")) %>% 
+  kbl(col.names = c("Word", "Exp", "Category", "Sub_category")) %>% 
   kable_minimal()
@@
 
-As the distribution plot of categories @fig-kwtype manifested, most keywords about Indian related texts in Natural History have a potential topic of goods (especially precious stones), and also people (both tribes and famous diplomats) and rivers in India (carrying the important role of origin of goods or transportation routes), which incorporates the investigation in [@nappo2017].
+The distribution plot of categories, as demonstrated in @fig-kwtype, reveals the pattern regarding keywords of India-related texts in Natural History.
 
@@
 
-# Collocation Analysis on "India" in the whole corpus
+Significantly, a substantial number of the keywords in the India-related text revolve around goods, particularly precious stones, suggesting a prominent thematic focus.
+The presence of keywords such as "beryls", "obsidian", "bdellium", "agates", "callaina", "prasii", "carnelian" and "sandastros" indicates the involvement of various gemstones and goods associated with India.
+These findings are complemented by the presence of keywords like "condensation", "merchandize" and "peppertree" which suggest the production and trade of goods between the Roman Empire and the Indian subcontinent during that era.
 
-In addition to the investigation on the keywords in the "Indian" related texts, it is also worthwhile having a look at what words collocated when Pliny the Elder referred to the word "India".
+Furthermore, the keywords related to rivers in India, such as "ganges", "cophes", "hypasis," and "sacae" indicate their significance as sources of goods or as integral parts of trading routes.
+Since Pliny the Elder's contextual framework includes critical descriptions of the geographical surroundings like rivers, as evident in his references to the Po River and the Nile River [@pollard2009; @murphy2003], a deeper investigation into the portrayal and role of Indian rivers within this context would provide valuable insights.
 
-By indicating "india" as the target item for the analysis through the function of [surf_cooc](https://masterclm.github.io/mclm/reference/create_cooc.html) in [@R-mclm] and removing the punctuation marks, similarly to the Keyword Analysis criteria chosen above, collocation scores for co-text of both right and left side of "india" are calculated and filtered with those with both PMI and G_signed scores as 2 or above to get the prominent collocates of "india", in order to get an concrete overview of the discourse and recognization of Pliny the Elder to "India".
+Additionally, a notable proportion of the keywords pertain to people, encompassing names, descriptions, and specific historical figures like "megasthenes".
+This suggests the historical significance of individuals who played a role in trade with India or in documenting and understanding the region.
+
+In conclusion, the keywords extracted from the India-related text in the *Natural History* shed light on India's role in trade, the production of valuable goods, and its association with notable historical figures and geographical features within the perspective of Pliny the Elder during the 1st century BC in the context of the Roman Empire.
+These findings could also contribute to a better understanding of India's historical interactions with the broader ancient world.
+
+# Collocation analysis on "India" in the whole corpus
+
+In addition to examining the keywords in the India-related texts, it is also valuable to explore the collocates that appear alongside the word "India" when mentioned in the book.
+
+To analyse the co-text surrounding the term "India," the [surf_cooc](https://masterclm.github.io/mclm/reference/create_cooc.html) function was employed, with "india" designated as the target item for the analysis.
+And following the same criteria as the previous keyword analysis, the collocation scores were filtered of having both PMI and G_signed scores of 2 or higher.
+By employing this approach, the prominent collocates of "india" were identified, providing a tangible understanding of the prevailing discourse and potentially reflecting Pliny the Elder's perspective on the region.
 
@@
 
-@tbl-coltable_Gsigned and @tbl-coltable_PMI shows the top 20 collocates to the word "india" in the whole text, respectively sorted by PMI and G_signed.
+@tbl-coltable_Gsigned and @tbl-coltable_PMI display the top 20 collocates associated with the word "india" in the entire text., respectively sorted by G_signed and PMI scores.
+As the returned $G^2$ score helps gauge the strength of evidence regarding the independence between the two words [@methods], thereby facilitating the initial sorting.
 
@@
 
-As the returned $G^2$ indicates the strongness of evidence of the independency of the two words,
+The top 20 collocates associated with the word "India," sorted by their $G^2$ scores, reveal three key dimensions:
 
-In addition, as shown in @tbl-concordance, with the concordance table of word "india" providing more details about the context of \"India\".
+1.
+**Geographical Connections**: The collocates such as "arabia", "ethiopia", "east," "south," "opposite," and "beyond" indicate the geographical relationships and proximity between India and these regions.
+
+2.
+**Trading and Imports**: The presence of collocates like "imported," "produces," "produce," and "nations" suggests that India had a significant role in trade and the importation of goods.
+It also implies that India was known for producing various commodities that were sought after by other nations.
+
+3.
+**Boundaries and Borders**: The collocates "boundary," "set," and "part" indicate the existence of defined boundaries or borders related to India.
+This suggests that there were recognized territorial demarcations associated with India during the referenced period.
+
+Within the context of Pliny the Elder's *Natural History* is a book with an encyclopedia scope written in Roman Empire, these collocates suggest the interconnecting role India played in the network of interactions, trade, or cultural exchanges between India and the Mediterranean regions during 1st century BC.
+They highlight India's significance as a trading partner, its geographical positioning, and the recognition of its territorial boundaries.
+
+Furthermore, the concordance table of the word "india," as displayed in @tbl-concordance, presents a comprehensive overview of the instances where "india" appears throughout the text, showcasing the specific contexts as well as providing additional information regarding the references to "India." It serves as a valuable resource for understanding the various perspectives, descriptions, and associations attributed to India within the context of *Natural History*.
 
@@
 
-Trade related words (including important transportation milestones, trading goods and the description of the goods (colors, precious, etc.)) are more prone to be occur in the text related to India.
-It reflects the trading connection of the two empires, and also how the recognition of the other empire for the scholars of that period.
+In conclusion, this paper located the research question on potential theme and topics in texts about India in Pliny the Elder's *Natural History* based on the prominent distribution of "India" in the entire text comparing to other place names.
+The analysis was conducted with the keyword analysis and collocation analysis in a framework of corpus linguistics.
+
+The analysis of keywords in the India-related text revealed significant themes such as the rivers, gemstones, goods, and historical figures like Megasthenes.
+These findings emphasize the cultural, geographical, and historical importance of India in the scope of scholars in Roman Empire during 1st century BC.
+
+Moreover, the exploration of collocates uncovered the geographical connections, trading networks, and territorial boundaries linked to India.
+The collocates highlighted the close relationships with neighboring regions such as Arabia and Ethiopia, along with references to trade, imports, and commodity production.
+
+Additionally, the study provided information on the specific contexts and usage of the word "India" within Pliny the Elder's *Natural History*, as a resource for further analysis about the discourse and recognition of India during that era.
+
+While this research represents an initial exploration, it paves the way for future investigations.
+Subsequent studies can expand the analysis to encompass a wider range of texts, explore different domains within Indian subcontinent-related literature, and utilize advanced natural language processing techniques to gain deeper semantic insights.

### 2023-06-22 paper_quarto.qmd
first completed draft minor fix

@@
 The frequency lists for the **target corpus** (Indian subcontinent related texts) and **reference corpus** (whole text) are generated respectively, and the association scores are calculated through the [assoc_scores](https://masterclm.github.io/mclm/reference/assoc_scores.html) function.
-The association score is filtered based on the criteira of both PMI and $G^2$ scores, requiring a minimum score of 2.
+The association score is filtered based on the criteria of both PMI and $G^2$ scores, requiring a minimum score of 2.
 This criterion ensures that the selected words have a probability at least four times higher than the overall data, along with statistically significant supporting evidence [@methods], allowing to identify the most statistically significant keywords in India-related texts when compared to the reference corpus.
@@
 
-The distribution plot of categories, as demonstrated in @fig-kwtype, reveals the pattern regarding keywords of India-related texts in Natural History.
+The distribution plot of categories, as demonstrated in @fig-kwtype, reveals the pattern regarding keywords of India-related texts in *Natural History*.
 
@@
 
-@tbl-coltable_Gsigned and @tbl-coltable_PMI display the top 20 collocates associated with the word "india" in the entire text., respectively sorted by G_signed and PMI scores.
+@tbl-coltable_Gsigned and @tbl-coltable_PMI display the top 20 collocates associated with the word "india" in the entire text, respectively sorted by G_signed and PMI scores.
 As the returned $G^2$ score helps gauge the strength of evidence regarding the independence between the two words [@methods], thereby facilitating the initial sorting.
@@
 #| tbl-cap-location: top
-#| tbl-cap: Top 20 collocates to the word "india" in Natural History (sorted by PMI)
+#| tbl-cap: Top 20 collocates to the word "india" in Natural History (sorted by G_signed)
 #| warning: false
@@
 2.
-**Trading and Imports**: The presence of collocates like "imported," "produces," "produce," and "nations" suggests that India had a significant role in trade and the importation of goods.
+**Trading and Imports**: The presence of collocates like "imported", "produces", "produce" and "nations" suggests that India had a significant role in trade and the importation of goods.
 It also implies that India was known for producing various commodities that were sought after by other nations.
@@
 3.
-**Boundaries and Borders**: The collocates "boundary," "set," and "part" indicate the existence of defined boundaries or borders related to India.
+**Boundaries and Borders**: The collocates "boundary," "set" and "part" indicate the existence of defined boundaries or borders related to India.
 This suggests that there were recognized territorial demarcations associated with India during the referenced period.
@@
 
-Furthermore, the concordance table of the word "india," as displayed in @tbl-concordance, presents a comprehensive overview of the instances where "india" appears throughout the text, showcasing the specific contexts as well as providing additional information regarding the references to "India." It serves as a valuable resource for understanding the various perspectives, descriptions, and associations attributed to India within the context of *Natural History*.
+Furthermore, the concordance table of the word "india" as displayed in @tbl-concordance, presents a comprehensive overview of the instances where "india" appears throughout the text, showcasing the specific contexts as well as providing additional information regarding the references to "India." It serves as a valuable resource for understanding the various perspectives, descriptions, and associations attributed to India within the context of *Natural History*.
 

### 2023-06-23 paper_quarto.qmd
first draft update

@@
 In order to facilitate the analysis, I conducted a scraping of the full text, exporting it as a **reference corpus** in .txt format.
-Furthermore, I extracted the texts specifically associated with the Indian subcontinent, utilizing the annotated coordinates, creating a **target corpus** of geographically related texts focused on India.
-The scraping was conducted with [Beautiful Soup](https://www.crummy.com/software/BeautifulSoup/bs4/doc/) library in Python, and the [code](https://github.com/lizaodawn/zhuang/blob/papertry/Natural%20History_corpus%20scrape.ipynb) is uploaded to the same repository of the project.[^1]
+Furthermore, I extracted the texts specifically associated with the India, utilizing the annotated coordinates, creating a **target corpus** of geographically related texts focused on India.
+The scraping was conducted with [Beautiful Soup](https://www.crummy.com/software/BeautifulSoup/bs4/doc/) library in Python, and the [code](https://github.com/lizaodawn/zhuang/blob/papertry/Natural%20History_corpus%20.ipynb) is uploaded to the same repository of the project.[^1]
 
@@
 
-ref_flist <- freqlist(fnames_wholetext, re_token_splitter = re("\\s+"))
-tar_flist <- freqlist(fnames_indiatext, re_token_splitter = re("\\s+"))
+# build frequency list for reference corpus
+flist_ref <- fnames_wholetext %>%
+  freqlist(re_token_transf_in = "[[:punct:]]", # Match punctuation marks
+           token_transf_out = "")
+
+# build frequency list for target corpus
+flist_target_all <- fnames_indiatext %>%
+  freqlist(re_token_transf_in = "[[:punct:]]", # Match punctuation marks
+           token_transf_out = ""
+    ) 
 ```
 
-The **target corpus** consists of all text related to Indian subcontinent (with coordinates in range of *8°4'N-37°6'N and 68°7'E to 97°25'E*), segregated by paragraphs, containing `r prettyNum(n_tokens(tar_flist))` tokens and `r n_types(tar_flist)` types, with the type-token ratio of `r round(n_types(tar_flist)/n_tokens(tar_flist), 2)`.
+The **target corpus** consists of all text related to India (with coordinates in range of *8°4'N-37°6'N and 68°7'E-97°25'E*), segregated by paragraphs, containing `r prettyNum(n_tokens(flist_target_all))` tokens and `r n_types(flist_target_all)` types, with the type-token ratio of `r round(n_types(flist_target_all)/n_tokens(flist_target_all), 2)`.
+[^2]
 
-And the **reference corpus** consists of all texts in *Natural History*, segregated by paragraphs, consisting of `r prettyNum(n_tokens(ref_flist))` tokens and `r n_types(ref_flist)` types, with the type-token ratio of `r round(n_types(ref_flist)/n_tokens(ref_flist), 2)`.
+[^2]: Given the challenges in precisely determining the coordinate range during the 1st century BC, the coordinate range of modern India is applied as a rough approximation.
+
+And the **reference corpus** consists of all texts in *Natural History*, segregated by paragraphs, consisting of `r prettyNum(n_tokens(flist_ref))` tokens and `r n_types(flist_ref)` types, with the type-token ratio of `r round(n_types(flist_ref)/n_tokens(flist_ref), 2)`.
 
@@
 
-The frequency lists for the **target corpus** (Indian subcontinent related texts) and **reference corpus** (whole text) are generated respectively, and the association scores are calculated through the [assoc_scores](https://masterclm.github.io/mclm/reference/assoc_scores.html) function.
+The frequency lists for the **target corpus** (India-related texts) and **reference corpus** (whole text) are generated respectively, and the association scores are calculated through the [assoc_scores](https://masterclm.github.io/mclm/reference/assoc_scores.html) function.
 The association score is filtered based on the criteria of both PMI and $G^2$ scores, requiring a minimum score of 2.
@@
 The presence of keywords such as "beryls", "obsidian", "bdellium", "agates", "callaina", "prasii", "carnelian" and "sandastros" indicates the involvement of various gemstones and goods associated with India.
-These findings are complemented by the presence of keywords like "condensation", "merchandize" and "peppertree" which suggest the production and trade of goods between the Roman Empire and the Indian subcontinent during that era.
+These findings are complemented by the presence of keywords like "condensation", "merchandize" and "peppertree" which suggest the production and trade of goods between the Roman Empire and the Indian regions during that era.
 

### 2023-06-23 freqlist_location.R

@@ -37,7 +37,7 @@ ggplot(top_20_summary_data, aes(x = reorder(Place_Name, -Count), y = Count)) +
 
 
 # Create a leaflet map
-m <- leaflet() %>%
+mapping <- leaflet() %>%
   addTiles() %>%
   addCircleMarkers(
     data = top_20_summary_data,
@@ -64,41 +64,29 @@ fnames_indiatext <- get_fnames(corpus_folder_in) %>%
 
 print(fnames_indiatext, 10, hide_path = corpus_folder_in)
 
-ref_flist <- freqlist(fnames_wholetext, re_token_splitter = re("\\s+"))
-tar_flist <- freqlist(fnames_indiatext, re_token_splitter = re("\\s+"))
-
-# build frequency list for target corpus
-flist_target <- fnames_indiatext %>%
-  freqlist(re_token_transf_in = "[[:punct:]]", # Match punctuation marks
-           token_transf_out = "",# Replace punctuation marks with an empty string
-           re_drop_token = "india"
-    ) 
 
 # build frequency list for reference corpus
 flist_ref <- fnames_wholetext %>%
   freqlist(re_token_transf_in = "[[:punct:]]", # Match punctuation marks
            token_transf_out = "")
 
+# build frequency list for target corpus
+flist_target_all <- fnames_indiatext %>%
+  freqlist(re_token_transf_in = "[[:punct:]]", # Match punctuation marks
+           token_transf_out = ""
+    ) 
+
+flist_target <- fnames_indiatext %>%
+  freqlist(re_token_transf_in = "[[:punct:]]", # Match punctuation marks
+           token_transf_out = "",
+           re_drop_token = "india"
+  )
+
 # calculate scores
 scores_kw <- assoc_scores(flist_target, flist_ref)
 
-# print scores, sorted by PMI
-print(scores_kw, sort_order = "PMI")
-
-# print scores, sorted by G_signed
-print(scores_kw, sort_order = "G_signed")
-
-
 top_scores_kw <- scores_kw %>% 
   filter(PMI >= 2 & G_signed >= 2)
-
-# print top_scores_kw, sorted by PMI
-top_scores_kw %>%
-  print(sort_order = "PMI")
-
-# print top_scores_kw, sorted by G_signed
-top_scores_kw %>%
-  print(sort_order = "G_signed")
 
 top_scores_kw %>% 
   as_tibble() %>%
[…]

### 2023-06-23 paper_quarto.qmd
minor fix

@@
 Furthermore, I extracted the texts specifically associated with the India, utilizing the annotated coordinates, creating a **target corpus** of geographically related texts focused on India.
-The scraping was conducted with [Beautiful Soup](https://www.crummy.com/software/BeautifulSoup/bs4/doc/) library in Python, and the [code](https://github.com/lizaodawn/zhuang/blob/papertry/Natural%20History_corpus%20.ipynb) is uploaded to the same repository of the project.[^1]
+The scraping was conducted with [Beautiful Soup](https://www.crummy.com/software/BeautifulSoup/bs4/doc/) library in Python, and the [code](https://github.com/lizaodawn/zhuang/blob/papertry/Natural%20History_corpus.ipynb) is uploaded to the same repository of the project.[^1]
 

### 2023-06-28 paper_quarto.qmd

@@
 
-[^2]: Given the challenges in precisely determining the coordinate range during the 1st century BC, the coordinate range of modern India is applied as a rough approximation.
+[^2]: Given the challenges in precisely determining the coordinate range during the 1st century AD, the coordinate range of modern India is applied as a rough approximation.
 
@@
 
-In conclusion, the keywords extracted from the India-related text in the *Natural History* shed light on India's role in trade, the production of valuable goods, and its association with notable historical figures and geographical features within the perspective of Pliny the Elder during the 1st century BC in the context of the Roman Empire.
+In conclusion, the keywords extracted from the India-related text in the *Natural History* shed light on India's role in trade, the production of valuable goods, and its association with notable historical figures and geographical features within the perspective of Pliny the Elder during the 1st century AD in the context of the Roman Empire.
 These findings could also contribute to a better understanding of India's historical interactions with the broader ancient world.
@@
 
-Within the context of Pliny the Elder's *Natural History* is a book with an encyclopedia scope written in Roman Empire, these collocates suggest the interconnecting role India played in the network of interactions, trade, or cultural exchanges between India and the Mediterranean regions during 1st century BC.
+Within the context of Pliny the Elder's *Natural History* is a book with an encyclopedia scope written in Roman Empire, these collocates suggest the interconnecting role India played in the network of interactions, trade, or cultural exchanges between India and the Mediterranean regions during 1st century AD.
 They highlight India's significance as a trading partner, its geographical positioning, and the recognition of its territorial boundaries.
@@
 The analysis of keywords in the India-related text revealed significant themes such as the rivers, gemstones, goods, and historical figures like Megasthenes.
-These findings emphasize the cultural, geographical, and historical importance of India in the scope of scholars in Roman Empire during 1st century BC.
+These findings emphasize the cultural, geographical, and historical importance of India in the scope of scholars in Roman Empire during 1st century AD.
 

### 2023-07-18 practice with ggplot.qmd
updated paper version

---
title: "ggplot_tryout"
format: html
code-fold: true
---

```{r}
library(tidyverse)
set.seed(2022)
rows <- 20
cake_eaten <- tibble(
  hunger_level = sample(1:100, rows, replace = TRUE),
  cake_eaten = sample(1:100, rows, replace = TRUE)/100, 
  cake_flavor = sample(rep_len(c("vanilla", "chocolate"), rows))
)
```

##Step1: setting up a plot

```{r}
#| label: fig-ggplot
#| fig-cap: "Output of the basic `ggplot()` call."
g <- ggplot(cake_eaten, aes(x = cake_eaten, y = hunger_level))
g
```

##Step2: adding fig points

```{r}
#| label: fig-point
#| fig-cap: Output after adding the points geometry.
#| code-fold: true
g <- g + geom_point(aes(color = cake_flavor), size = 3)
g
```

##Step 3: adding fig-theme-light

```{r}
#| label: fig-theme-light
#| fig-cap: Output after adding a "light" theme.
g <- g + theme_light(base_size = 20)
g
```

### 2023-08-18 paper_quarto.qmd
0818 modification

@@
 number-sections: true
-code-fold: true
+echo: false
+code-link: true
 bibliography:
@@
 library('kableExtra')
-library('dplyr')
-library('ggplot2')
 library('leaflet')
@@
 #| label: fig-geoname
-#| fig-cap: Bar Chart for Top 20 Distinct Place Names Mentioned in Natural History
+#| fig-cap: Bar chart for top 20 distinct place names mentioned in *Natural History*
 #| fig-cap-location: top
@@
 
+# Create a bar chart using ggplot2
 top_20_summary_data <- summary_data %>%
@@
 ggplot(top_20_summary_data, aes(x = reorder(Place_Name, -Count), y = Count)) +
-  geom_bar(stat = "identity") +
-  labs(x = "Place Name", y = "Count") +
+  geom_col() +
+  labs(x = "Place name", y = "Number of occurrences") +
   theme(axis.text.x = element_text(angle = 45, hjust = 1))
-
 ```
@@
   addCircleMarkers(
-    data = top_20_summary_data,
+    data = summary_data,
     lat = ~Lat,
     lng = ~Long,
-    radius = sqrt(top_20_summary_data$Count) * 0.8,  
+    radius = sqrt(summary_data$Count) * 0.8,  # Adjust the scaling factor as needed
     color = "blue",
@@
     fillOpacity = 0.6,
-    popup = paste("Place Name:", top_20_summary_data$Place_Name, "<br>",
-                  "Count:", top_20_summary_data$Count)
+    popup = paste("Place name:", summary_data$Place_Name, "<br>",
+                  "Number of occurences:", summary_data$Count)
   )
@@
 
-The frequency lists for the **target corpus** (India-related texts) and **reference corpus** (whole text) are generated respectively, and the association scores are calculated through the [assoc_scores](https://masterclm.github.io/mclm/reference/assoc_scores.html) function.
+The frequency lists for the **target corpus** (India-related texts) and **reference corpus** (whole text) are generated respectively, and the association scores are calculated through the `mclm::assoc_scores()` function.
 The association score is filtered based on the criteria of both PMI and $G^2$ scores, requiring a minimum score of 2.
@@
 Significantly, a substantial number of the keywords in the India-related text revolve around goods, particularly precious stones, suggesting a prominent thematic focus.
-The presence of keywords such as "beryls", "obsidian", "bdellium", "agates", "callaina", "prasii", "carnelian" and "sandastros" indicates the involvement of various gemstones and goods associated with India.
-These findings are complemented by the presence of keywords like "condensation", "merchandize" and "peppertree" which suggest the production and trade of goods between the Roman Empire and the Indian regions during that era.
+The presence of keywords such as *beryls*, *obsidian*, *bdellium*, *agates*, *callaina*, *prasii*, *carnelian* and *sandastros* indicates the involvement of various gemstones and goods associated with India.
+These findings are complemented by the presence of keywords like *condensation*, *merchandize* and *peppertree* which suggest the production and trade of goods between the Roman Empire and the Indian regions during that era.
 
-Furthermore, the keywords related to rivers in India, such as "ganges", "cophes", "hypasis," and "sacae" indicate their significance as sources of goods or as integral parts of trading routes.
+Furthermore, the keywords related to rivers in India, such as *ganges*, *cophes*, *hypasis*, and *sacae* indicate their significance as sources of goods or as integral parts of trading routes.
 Since Pliny the Elder's contextual framework includes critical descriptions of the geographical surroundings like rivers, as evident in his references to the Po River and the Nile River [@pollard2009; @murphy2003], a deeper investigation into the portrayal and role of Indian rivers within this context would provide valuable insights.
 
-Additionally, a notable proportion of the keywords pertain to people, encompassing names, descriptions, and specific historical figures like "megasthenes".
+Additionally, a notable proportion of the keywords pertain to people, encompassing names, descriptions, and specific historical figures like *megasthenes*.
 This suggests the historical significance of individuals who played a role in trade with India or in documenting and understanding the region.
@@
 
-To analyse the co-text surrounding the term "India," the [surf_cooc](https://masterclm.github.io/mclm/reference/create_cooc.html) function was employed, with "india" designated as the target item for the analysis.
+To analyse the co-text surrounding the term "India," the `mclm::surf_cooc()` function was employed, with "india" designated as the target item for the analysis.
 And following the same criteria as the previous keyword analysis, the collocation scores were filtered of having both PMI and G_signed scores of 2 or higher.
@@
 1.
-**Geographical Connections**: The collocates such as "arabia", "ethiopia", "east," "south," "opposite," and "beyond" indicate the geographical relationships and proximity between India and these regions.
+**Geographical Connections**: The collocates such as *arabia*, *ethiopia*, *east*, *south*, *opposite*, and *beyond* indicate the geographical relationships and proximity between India and these regions.
 
 2.
-**Trading and Imports**: The presence of collocates like "imported", "produces", "produce" and "nations" suggests that India had a significant role in trade and the importation of goods.
+**Trading and Imports**: The presence of collocates like *imported*, *produces*, *produce* and *nations* suggests that India had a significant role in trade and the importation of goods.
 It also implies that India was known for producing various commodities that were sought after by other nations.
@@
 3.
-**Boundaries and Borders**: The collocates "boundary," "set" and "part" indicate the existence of defined boundaries or borders related to India.
+**Boundaries and Borders**: The collocates *boundary*, *set* and *part* indicate the existence of defined boundaries or borders related to India.
 This suggests that there were recognized territorial demarcations associated with India during the referenced period.

### 2023-08-18 freqlist_location.R

@@ -10,8 +10,6 @@ library('tidyverse')
 library('mclm')
 library('here')
 library('kableExtra')
-library('ggplot2')
-library('dplyr')
 library('leaflet')
 
 data <- read.csv("geotext_whole.csv")
@@ -29,9 +27,8 @@ top_20_summary_data <- summary_data %>%
   ungroup()
 
 ggplot(top_20_summary_data, aes(x = reorder(Place_Name, -Count), y = Count)) +
-  geom_bar(stat = "identity") +
-  labs(x = "Place Name", y = "Count") +
-  ggtitle("Top 20 Place Names Mentioned") +
+  geom_col() +
+  labs(x = "Place name", y = "Number of occurrences") +
   theme(axis.text.x = element_text(angle = 45, hjust = 1))
 
 
@@ -40,15 +37,15 @@ ggplot(top_20_summary_data, aes(x = reorder(Place_Name, -Count), y = Count)) +
 mapping <- leaflet() %>%
   addTiles() %>%
   addCircleMarkers(
-    data = top_20_summary_data,
+    data = summary_data,
     lat = ~Lat,
     lng = ~Long,
-    radius = sqrt(top_20_summary_data$Count) * 0.8,  # Adjust the scaling factor as needed
+    radius = sqrt(summary_data$Count) * 0.8,  # Adjust the scaling factor as needed
     color = "blue",
     fill = TRUE,
     fillOpacity = 0.6,
-    popup = paste("Place Name:", top_20_summary_data$Place_Name, "<br>",
-                  "Count:", top_20_summary_data$Count)
+    popup = paste("Place name:", summary_data$Place_Name, "<br>",
+                  "Number of occurences:", summary_data$Count)
   )
 
 
@@ -67,23 +64,14 @@ print(fnames_indiatext, 10, hide_path = corpus_folder_in)
 
 # build frequency list for reference corpus
 flist_ref <- fnames_wholetext %>%
-  freqlist(re_token_transf_in = "[[:punct:]]", # Match punctuation marks
-           token_transf_out = "")
+  freqlist
 
 # build frequency list for target corpus
-flist_target_all <- fnames_indiatext %>%
-  freqlist(re_token_transf_in = "[[:punct:]]", # Match punctuation marks
-           token_transf_out = ""
-    ) 
-
-flist_target <- fnames_indiatext %>%
-  freqlist(re_token_transf_in = "[[:punct:]]", # Match punctuation marks
[…]

### 2023-08-18 freqlist_location.R
indian-related text update

@@ -71,7 +71,7 @@ flist_target <- fnames_indiatext %>%
   freqlist
 
 # calculate scores
-scores_kw <- assoc_scores(flist_target_all, flist_ref)
+scores_kw <- assoc_scores(flist_target, flist_ref)
 
 top_scores_kw <- scores_kw %>% 
   filter(PMI >= 2 & G_signed >= 2)
@@ -80,7 +80,7 @@ top_scores_kw %>%
   as_tibble() %>%
   select(type, a, PMI, G_signed) %>% 
   arrange(desc(PMI)) %>%             
-  slice_max(order_by = PMI, n = 20, with_ties = TRUE) %>%                       
+  slice_max(order_by = G_signed, n = 20, with_ties = TRUE) %>%                       
   kbl(col.names = c("Type", "Frequency", "PMI", r"(Signed $G^2$)")) %>% 
   kable_minimal() %>% 
   scroll_box(height = "400px") %>%  print()

### 2023-08-19 paper_quarto.qmd
0819 research question and corpus description update

@@
 engine: knitr
-title: "Keyword and Collocation analysis on India-related text of Natural History"
+title: "Keyword and Collocation analysis on India-related text of *Natural History*"
 author: "Dawn, Lizao Zhuang (r0914937)"
@@
 echo: false
-code-link: true
 bibliography:
@@
 library('leaflet')
+library('downlit')
 options(digits = 3)
@@
 knitr::write_bib(
-  c("base", "mclm", "ggplot2", "tidyverse", "leaflet"),
+  c("base", "mclm", "ggplot2", "tidyverse", "leaflet", "downlit"),
   here("packages.bib")
@@
 
-# Research Question
+# Research Question[^1]
 
-Pliny the Elder's *Natural History* stands as a seminal work in the history of encyclopedias, serving as a gateway to understanding the knowledge and worldview of ancient Rome.
-Beyond its role as a compendium of diverse subjects, the text provides a captivating glimpse into the actual merchant exchanges [@dodd2021] of the Roman Empire while shedding a light on the spatial imagination of Pliny and the scholarly references of his time [@plinyth2011].
+[^1]: This study is a pilot study of my master thesis, so the description of the research question is connected with that of this [paper](https://raw.githack.com/lizaodawn/NH_thesis/main/NHthesis_structure.html#sec-introduction).
 
-The text of the whole book has been digitized and annotated with people's name, places' name and coordinates by [TOPOSText](https://topostext.org/the-project) project since 2012.
-This invaluable resource allows for the creation of a dataset that includes both the textual contents and geographical annotations, which can be utilized to investigate the distribution of place names in the entire text and examine the frequencies and patterns of geographically-related content.
+Pliny the Elder's *Natural History* is widely recognized as the earliest encyclopedia in the world.
+Written around AD 77, the work is thematically divided into 37 books, covering a diverse range of subjects including astronomy, geography, zoology, botany, medicine, and more.
+Driven by a pioneering attempt to catalogue human knowledge from his era, Pliny made a comprehensive reference to a wide range of Greek and Roman scholarships, and interwove his own literary interpretation or comments to the narratives in *Natural Hisrory*.
+
+*Natural History* stands as a seminal work in the history of encyclopedias, serving as a gateway to understanding the knowledge and worldview of ancient Rome.
+Beyond its role as a compendium of diverse subjects, the text provides a captivating glimpse into the knowledge, cultural, and merchandise exchange [@dodd2021] between the Roman Empire and other regions while shedding a light on the spatial perception and imagination of Pliny and the scholarly references of his time [@plinyth2011].
+
+As pointed out by @beagon2011, differentiating from his predecessors, Pliny showed a "terrestrial curiosity" in Natural History, emphasising recognition of the physical, material world.
+Drawing from the long-established topographical and ethnographic traditions, Pliny connects volumes dedicated to geography (books 3-6) with broader elements, activities, and cultural, historical, and societal contexts [@roller2022], exemplified in his portrayal of exotic plants, communities' habitats, imperial expeditions, and trade products.
+In this regard, geographical names mentioned in the text plays a pivotal role in distributing information, knowledge, and discussions throughout *Natural History*.
+
+*Natural History* is originally in Latin.
+For this study, an English translation by Henry T.
+Riley (1816-1878) and John Bostock (1773-1846), first published in 1855, is utilized.
+The translated text is obtained in a digitised version from the [TOPOSText project](https://topostext.org/the-project), having been sourced from the Perseus Project and governed by a Creative Commons Attribution-Share-Alike 3.0 U.S.
+License.
+
+In addition to the digitised textual content of *Natural History*, the place names mentioned in the text are annotated with their corresponding coordinates on TOPOXText.
+The annotations are available in an HTML format, which were sparsed and restructured into a dataset of geographical-related text in *Natural History* with [Beautiful Soup](https://www.crummy.com/software/BeautifulSoup/bs4/doc/) library in Python[^2].
+The dataset structure, corpus scraping procedure and and corpus extention will be further elaborated in Corpus Description section (@sec-corpus).
+
+[^2]: The sparsing [code](https://github.com/lizaodawn/zhuang/blob/papertry/Natural%20History_corpus.ipynb) is uploaded to the same repository of the project.
 
@@
 
-An intriguing observation from this analysis, as depicted in @fig-map, is the prominence of India---a region outside the Mediterranean---despite its high frequency of mentions.
+An intriguing observation from this analysis, as depicted in @fig-map, is that India seems prominently mentioned in the work despite being outside the Mediterranean.
 
@@
 
-Building upon this observation, this paper aims to delve deeper into the themes associated with the India region referred in the text by employing keyword analysis and collocation analysis methods within the framework of corpus linguistics.
+Building upon this observation, the study focus is narrowed down to India-related text in *Natural History*, aiming to delve deeper into the themes associated with the Indian region referred in the text by employing keyword analysis and collocation analysis methods within the framework of corpus linguistics.
 
@@
 
-# Corpus Description
+# Corpus Description {#sec-corpus}
 
-As mentioned earlier, the digitized text of *Natural History* with geographical annotations is readily accessible through the [TOPOSText](https://topostext.org/work/148 "Check Natural History on ToposText") project.
-In order to facilitate the analysis, I conducted a scraping of the full text, exporting it as a **reference corpus** in .txt format.
-Furthermore, I extracted the texts specifically associated with the India, utilizing the annotated coordinates, creating a **target corpus** of geographically related texts focused on India.
-The scraping was conducted with [Beautiful Soup](https://www.crummy.com/software/BeautifulSoup/bs4/doc/) library in Python, and the [code](https://github.com/lizaodawn/zhuang/blob/papertry/Natural%20History_corpus.ipynb) is uploaded to the same repository of the project.[^1]
+As mentioned, an English translation by Henry T. Riley (1816-1878) and John Bostock (1773-1846) of the original Latin text of *Natural History* is employed in the study.
 
-[^1]: As this paper represents a preliminary investigation for my master's thesis, I utilized the corpus that had already been scraped using Python.
+The digitised text is avalible in paragraphs with geographical annotations on TOPOSText website as two parts, [book 1-11](https://topostext.org/work/148) and [book 12-37](https://topostext.org/work/153), both of which are in HTML format.
+Extracting all the "place" class in the HTML files, a dataset containing all annotated place names in the work, the URI and corresponding coordinates of the place, the book/chapter/paragraph number where it is mentioned, as well as the coordinating textual content are structured as a dataset of geographic-related text in *Natural History*.
+This dataset is used for an initial exploration of the prominent mentioned places in the text.
+
+Since the research focus is narrowed down to India-related text after the initial exploration, a dataset including all Indian place names mentioned in the text is extracted from the geographical-related text dataset.
+With a reference to *Barrington Atlas of the Greek and Roman World* (@talbert2000a, @talbert2000b), the approximate coordinates defining the Indian region during the time of *Natural Hisoty* are as follows^[As indicated in the map-by-map directory, the range spans territories of “modern states of India (minus the Punjab), Bangladesh, Bhutan, Burma, Nepal, and Sri Lanka”.]:
+
+>Latitude: 5-35 degrees North
+
+>Longitude: 65-95 degrees East
+
+The records in geographical-related text dataset with corresponding coordinates falling within the specified range are extracted as the India-related text dataset.
+
+Each distinct paragraph in the India-related text dataset is extracted and stored in TXT format as separate files within a corpus folder, comprising a total of 146 files as the **target corpus** for India-related text in *Natural History*.
+The file names contain information about the book, chapter, and paragraph numbers.
+
+And the full text of the entire work, segregrating in paragraphs, are scraped and stored in TXT format as a **reference corpus**.
+
+The text are set into lower case in the corpus file extraction process.
 
@@
 flist_ref <- fnames_wholetext %>%
-  freqlist(re_token_transf_in = "[[:punct:]]", # Match punctuation marks
-           token_transf_out = "")
+  freqlist()
 
@@
 flist_target_all <- fnames_indiatext %>%
-  freqlist(re_token_transf_in = "[[:punct:]]", # Match punctuation marks
-           token_transf_out = ""
-    ) 
+  freqlist() 
 ```
 
-The **target corpus** consists of all text related to India (with coordinates in range of *8°4'N-37°6'N and 68°7'E-97°25'E*), segregated by paragraphs, containing `r prettyNum(n_tokens(flist_target_all))` tokens and `r n_types(flist_target_all)` types, with the type-token ratio of `r round(n_types(flist_target_all)/n_tokens(flist_target_all), 2)`.
-[^2]
+The **target corpus** consists of all text related to India in paragraphs, containing `r prettyNum(n_tokens(flist_target_all))` tokens and `r n_types(flist_target_all)` types, with the type-token ratio of `r round(n_types(flist_target_all)/n_tokens(flist_target_all), 2)`.
 
-[^2]: Given the challenges in precisely determining the coordinate range during the 1st century AD, the coordinate range of modern India is applied as a rough approximation.
+And the **reference corpus** consists of all texts in *Natural History* in paragraphs, consisting of `r prettyNum(n_tokens(flist_ref))` tokens and `r n_types(flist_ref)` types, with the type-token ratio of `r round(n_types(flist_ref)/n_tokens(flist_ref), 2)`.
 
-And the **reference corpus** consists of all texts in *Natural History*, segregated by paragraphs, consisting of `r prettyNum(n_tokens(flist_ref))` tokens and `r n_types(flist_ref)` types, with the type-token ratio of `r round(n_types(flist_ref)/n_tokens(flist_ref), 2)`.
+# Methodology
 
-The punctuation marks are removed in the tokenization process.
+## Keyword Analysis
 
-# Keyword analysis on India-related texts
+## Collocation Analysis
+
+# Data Analysis
+
+## Keyword in India-related text in *Natural History*
 
@@
 ::: panel-tabset
-## Sorted by PMI
+### Sorted by absolute frequencies
+
+```{r}
+#| warning: false
+#| echo: false
+#| label: tbl-kwtable_absolute_freqencies
+#| tbl-cap-location: top
+#| tbl-cap: Top 20 Keywords on Indian Related Text in Natural History (sorted by PMI)
+
+top_scores_kw %>% 
+  as_tibble() %>%
+  select(type, a, PMI, G_signed) %>% 
+  slice_max(order_by = a, n = 20, with_ties = TRUE) %>%                       
+  kbl(col.names = c("Type", "Frequency", "PMI", r"(Signed $G^2$)")) %>% 
+  kable_minimal() %>% 
+  scroll_box(height = "400px")
+```
+
+### Sorted by PMI
 
@@
 
-## Sorted by G_signed
+### Sorted by G_signed
 
@@
 
-# Collocation analysis on "India" in the whole corpus
+## Collocating word to "India" in *Natural History*
 
@@
 ::: panel-tabset
-## Sorted by G_singed
+### Sorted by absolute frequencies
+
+```{r}
+#| label: tbl-coltable_absolute_freqencies
+#| tbl-cap-location: top
+#| tbl-cap: Top 20 collocates to the word "india" in Natural History (sorted by G_signed)
+#| warning: false
+#| echo: false
+top_scores_colloc %>% 
+  as_tibble() %>%
+  select(type, a, PMI, G_signed) %>% 
+  slice_max(order_by = a, n = 20, with_ties = TRUE) %>%
+  kbl(col.names = c("Type", "Frequency", "PMI", r"(Signed $G^2$)"), escape = FALSE) %>%
+  kable_minimal() %>% 
+  scroll_box(height = "400px")
+
+```
+
+### Sorted by G_singed
 
@@
 
-## Sorted by PMI
+### Sorted by PMI
 

### 2023-08-20 freqlist_location.R
0819 library update

@@ -4,6 +4,7 @@ install.packages('here')
 install.packages('kableExtra')
 install.packages("leaflet")
 install.packages("quarto")
+install.packages("downlit")
 
 
 library('tidyverse')
@@ -11,6 +12,7 @@ library('mclm')
 library('here')
 library('kableExtra')
 library('leaflet')
+library('downlit')
 
 data <- read.csv("geotext_whole.csv")
 

### 2023-08-21 paper_quarto.qmd
0821 methodology update

@@
 
+# Methodology
+
+To investigate the prominent themes in the India-related content discussed in *Natural History*, methods of keyword analysis and collocation analysis are employed for this study.
+Both of the analyses rely on the `mclm::assoc_scores` objects of the [mclm](https://github.com/masterclm/mclm) package, which return frequencies and association scores of a certain event in a target context and in a reference context.
+
+Both of the methods will be examined by three association measurements, namely absolute frequency, PMI and $G^2$ signed, to discuss with the context in *Natural History* and the potential theme it indicates.
+
+PMI measures the association strength between two words by comparing their observed co-occurrence frequency with their expected co-occurrence frequency by chance.
+It highlights words that appear together more frequently than expected.
+High PMI values indicates strong associations.
+High $G^2$ values suggest that the co-occurrence is unlikely to occur by chance.
+
+$G^2$ is a statistical test that measures the independence or association between two categorical variables (words in this case).
+It compares the observed co-occurrence frequencies with the expected frequencies under the assumption of independence.
+Higher $G^2$ values suggest a stronger association.
+
+## Keyword Analysis
+
+Keyword analysis is a statistical method used in corpus linguistics to identify words that occur more frequently in a target corpus than in a reference corpus.
+Defined with different associate measurements, the "keyness" of words are calculated and indicated which words are statistically more frequent appeared in the target corpus comparing to that of the reference corpus.
+
+In this study, the *target corpus* includes all paragraphs in *Natural History* mentioning Indian regions, and the **reference corpus** contains all other paragraphs in the work.
+Lists of 20 words with the highest score in different association measurements are discussed with the textual context.
+As indicated by the measurements, the listed words tend to be more frequently occur in the context pertaining India than other parts of the work, hence they seem to be the potential keywords about India in *Natural History*.
+
+## Collocation Analysis
+
+Collocation analysis is a technique employed in corpus linguistics to identify words that often appear together in a language.
+This technique is rooted in the notion that particular words tend to appear together more often than would occur by chance.
+In the context of this study, lists of the highly possible co-occuring word with "India" in the text of *Natural History* can shed a light on the potential themes and topics about India discussed in the work.
+
+Combining the two methods, and integrating with a close reading of the text, this study aims to discuss what about "India" is discussed in *Natural History*.
+
 # Corpus Description {#sec-corpus}
@@
 Since the research focus is narrowed down to India-related text after the initial exploration, a dataset including all Indian place names mentioned in the text is extracted from the geographical-related text dataset.
-With a reference to *Barrington Atlas of the Greek and Roman World* (@talbert2000a, @talbert2000b), the approximate coordinates defining the Indian region during the time of *Natural Hisoty* are as follows^[As indicated in the map-by-map directory, the range spans territories of “modern states of India (minus the Punjab), Bangladesh, Bhutan, Burma, Nepal, and Sri Lanka”.]:
+With a reference to *Barrington Atlas of the Greek and Roman World* (@talbert2000a, @talbert2000b), the approximate coordinates defining the Indian region during the time of *Natural Hisoty* are as follows[^3]:
 
->Latitude: 5-35 degrees North
+[^3]: As indicated in the map-by-map directory, the range spans territories of "modern states of India (minus the Punjab), Bangladesh, Bhutan, Burma, Nepal, and Sri Lanka".
 
->Longitude: 65-95 degrees East
+> Latitude: 5-35 degrees North
+>
+> Longitude: 65-95 degrees East
 
@@
 
-And the full text of the entire work, segregrating in paragraphs, are scraped and stored in TXT format as a **reference corpus**.
+And the full text of the entire work, segregating in paragraphs, are scraped and stored in TXT format and excluded the files in **target corpus** to serve as a **reference corpus**.
 
@@
 
+fnames_wholetext_short <- basename(fnames_wholetext)
+fnames_indiatext_short <- basename(fnames_indiatext)
+
+# Exclude short file names with the same name from target corpus in the reference corpus
+fnames_wholetext_short_filtered <- fnames_wholetext_short %>%
+  setdiff(fnames_indiatext_short)
+
+# Filter full file names based on filtered short names
+fnames_wholetext_filtered <- fnames_wholetext[fnames_wholetext_short %in% fnames_wholetext_short_filtered]
+
 # build frequency list for reference corpus
-flist_ref <- fnames_wholetext %>%
-  freqlist()
+flist_ref <- fnames_wholetext_filtered %>%
+  freqlist(re_token_transf_in = "'", 
+           token_transf_out = "")
 
 # build frequency list for target corpus
-flist_target_all <- fnames_indiatext %>%
-  freqlist() 
+flist_target <- fnames_indiatext %>%
+  freqlist(re_token_transf_in = "'", 
+           token_transf_out = "") 
 ```
 
-The **target corpus** consists of all text related to India in paragraphs, containing `r prettyNum(n_tokens(flist_target_all))` tokens and `r n_types(flist_target_all)` types, with the type-token ratio of `r round(n_types(flist_target_all)/n_tokens(flist_target_all), 2)`.
+The **target corpus** consists of all text related to India in paragraphs, containing `r prettyNum(n_tokens(flist_target))` tokens and `r n_types(flist_target)` types, with the type-token ratio of `r round(n_types(flist_target)/n_tokens(flist_target), 2)`.
 
 And the **reference corpus** consists of all texts in *Natural History* in paragraphs, consisting of `r prettyNum(n_tokens(flist_ref))` tokens and `r n_types(flist_ref)` types, with the type-token ratio of `r round(n_types(flist_ref)/n_tokens(flist_ref), 2)`.
-
-# Methodology
-
-## Keyword Analysis
-
-## Collocation Analysis
 
@@
 #| warning: false
-
-# build frequency list for target corpus
-flist_target <- fnames_indiatext %>%
-  freqlist(
-    re_token_transf_in = "[[:punct:]]", # Match punctuation marks
-    token_transf_out = "", # Replace punctuation marks with an empty string
-    re_drop_token = "india"
-  )
-
-# build frequency list for reference corpus
-flist_ref <- fnames_wholetext %>%
-  freqlist(
-    re_token_transf_in = "[[:punct:]]", # Match punctuation marks
-    token_transf_out = ""
-  )
 
@@
 
+1.  $G^2$ signed highly overlapped with that of absolute frequency. (plot of corelation)
+2.  list the overlapped keywords
+3.  PMI sorting provides more information
+
 From these keywords, a manual examination was performed to determine their meaning and assign appropriate tags as based on their category.
@@
 
-To analyse the co-text surrounding the term "India," the `mclm::surf_cooc()` function was employed, with "india" designated as the target item for the analysis.
+To analyse the textual collocating bi-gram of word "India", the `mclm::text_cooc()` function was employed, with "india" designated as the target item for the analysis.
 And following the same criteria as the previous keyword analysis, the collocation scores were filtered of having both PMI and G_signed scores of 2 or higher.
@@
 coocs <- fnames_wholetext %>% 
-  surf_cooc("(?xi)  ^ india $", 
-            re_token_transf_in = "[[:punct:]]", # Match punctuation marks
-            token_transf_out = "")
+  text_cooc("(?xi)  ^ india $")
 
@@
 
+1.  $G^2$ signed highly overlapped with that of absolute frequency. (plot of corelation)
+2.  list the overlapped keywords
+3.  PMI sorting provides more information
+
 Within the context of Pliny the Elder's *Natural History* is a book with an encyclopedia scope written in Roman Empire, these collocates suggest the interconnecting role India played in the network of interactions, trade, or cultural exchanges between India and the Mediterranean regions during 1st century AD.
 They highlight India's significance as a trading partner, its geographical positioning, and the recognition of its territorial boundaries.
-
-Furthermore, the concordance table of the word "india" as displayed in @tbl-concordance, presents a comprehensive overview of the instances where "india" appears throughout the text, showcasing the specific contexts as well as providing additional information regarding the references to "India." It serves as a valuable resource for understanding the various perspectives, descriptions, and associations attributed to India within the context of *Natural History*.
-
-```{r}
-#| label: tbl-concordance
-#| tbl-cap-location: top
-#| tbl-cap: Concordance table of word "india" in Natural History
-#| warning: false
-#| echo: false
-
-conc_data <- conc(fnames_wholetext, '\\bindia\\b')
-
-conc_data %>%
-  as_tibble() %>%
-  select(source, left, match, right) %>%
-  mutate(
-    source = short_names(source),
-    book = as.integer(gsub("^(\\d+).*", "\\1", source)),
-    chapter = as.numeric(gsub("^\\d+\\.(\\d+)\\.\\d+_text$", "\\1", source)),
-    paragraph = as.numeric(gsub("^\\d+\\.\\d+\\.(\\d+)_text$", "\\1", source))
-  ) %>%
-  arrange(book, chapter, paragraph) %>%
-  select(book, chapter, paragraph, left, match, right) %>%
-  kbl(align = c("r", "r", "r", "c", "l", "l", "l")) %>%
-  kable_paper(font_size = 15) %>%
-  scroll_box(height = "400px")
-```
 

### 2023-08-21 freqlist_location.R

@@ -59,18 +59,29 @@ print(fnames_wholetext, 10, hide_path = corpus_folder_whole)
 
 corpus_folder_in <- here("NH_geotext_india")
 fnames_indiatext <- get_fnames(corpus_folder_in) %>% 
-  keep_re("[.]txt")
+  keep_re("[.]txt") 
 
 print(fnames_indiatext, 10, hide_path = corpus_folder_in)
 
+fnames_wholetext_short <- basename(fnames_wholetext)
+fnames_indiatext_short <- basename(fnames_indiatext)
+
+# Exclude short file names with the same name from target corpus in the reference corpus
+fnames_wholetext_short_filtered <- fnames_wholetext_short %>%
+  setdiff(fnames_indiatext_short)
+
+# Filter full file names based on filtered short names
+fnames_wholetext_filtered <- fnames_wholetext[fnames_wholetext_short %in% fnames_wholetext_short_filtered]
 
 # build frequency list for reference corpus
-flist_ref <- fnames_wholetext %>%
-  freqlist
+flist_ref <- fnames_wholetext_filtered %>%
+  freqlist(re_token_transf_in = "'", 
+           token_transf_out = "")
 
 # build frequency list for target corpus
 flist_target <- fnames_indiatext %>% 
-  freqlist
+  freqlist(re_token_transf_in = "'", 
+           token_transf_out = "")
 
 # calculate scores
 scores_kw <- assoc_scores(flist_target, flist_ref)
@@ -82,7 +93,7 @@ top_scores_kw %>%
   as_tibble() %>%
   select(type, a, PMI, G_signed) %>% 
   arrange(desc(PMI)) %>%             
-  slice_max(order_by = G_signed, n = 20, with_ties = TRUE) %>%                       
+  slice_max(order_by = PMI, n = 20, with_ties = TRUE) %>%                       
   kbl(col.names = c("Type", "Frequency", "PMI", r"(Signed $G^2$)")) %>% 
   kable_minimal() %>% 
   scroll_box(height = "400px") %>%  print()
@@ -114,9 +125,7 @@ ggplot(tag_counts, aes(x = n, y = reorder(Tag, -n), fill = Tag)) +
 
 
 coocs <- fnames_wholetext %>% 
-  surf_cooc("(?xi)  ^ india $",
-            re_token_transf_in = "[[:punct:]]", # Match punctuation marks
-            token_transf_out = "")
[…]

### 2023-08-21 freqlist_location.R
0821 code update

@@ -76,7 +76,7 @@ fnames_wholetext_filtered <- fnames_wholetext[fnames_wholetext_short %in% fnames
 # build frequency list for reference corpus
 flist_ref <- fnames_wholetext_filtered %>%
   freqlist(re_token_transf_in = "'", 
-           token_transf_out = "")
+           token_transf_out = "") %>% print(20)
 
 # build frequency list for target corpus
 flist_target <- fnames_indiatext %>% 

### 2023-08-22 paper_quarto.qmd
0822 keyword analysis update

@@
 echo: false
+warning: false
+tbl-cap-location: top
 bibliography:
@@
 The following tables present the top 20 keywords in India-related texts as compared to the entire texts in *Natural History*.
-They are sorted based on their PMI (@tbl-kwtable_PMI) and G_signed scores (@tbl-kwtable_Gsigned), respectively.
+They are sorted based on their PMI (@tbl-kwtable_PMI), Absolute frequencies(@tbl-kwtable_absolute_freqencies) and G_signed scores (@tbl-kwtable_Gsigned), respectively.
 The initial sorting was carried out based on the PMI scores (@tbl-kwtable_PMI), since the it serves as a crucial indicator for measuring the keyness of words.
@@
   select(type, a, PMI, G_signed) %>%         # sort by PMI (descending) 
-  slice_max(order_by = G_signed, n = 20, with_ties = TRUE) %>%   # select top 30 rows
+  slice_max(order_by = G_signed, n = 20, with_ties = TRUE) %>%   
   kbl(col.names = c("Type", "Frequency", "PMI", r"(Signed $G^2$)")) %>% 
@@
 
-1.  $G^2$ signed highly overlapped with that of absolute frequency. (plot of corelation)
-2.  list the overlapped keywords
-3.  PMI sorting provides more information
+In the list of three measurements, 16/20 of absolute frequency overlaps with that of $G^2$ Signed.
+As shown in the @fig-col_keyword, the $G^2$ score has a positive correlation with the absolute frequency.
+
+```{r}
+#| label: fig-col_keyword
+#| tbl-cap:  Scatterplot of G_signed by absolute frequency
+
+top_scores_kw_df <- as_tibble(top_scores_kw)
+
+theme_set(theme_minimal(base_size = 15))
+g <- top_scores_kw_df %>%
+  ggplot(aes(x = G_signed, y = a)) +
+  labs(x = "Signed G", y = "Absolute frequency")
+g + geom_point()
+```
+
+Combing the lists sorted by absolute frequency and signed G, it can be categorized as follows (those without specified are the overlapped words):
+
+**Geographical/Ethnic Group**: india, arabia, indian, ganges, indus, ethiopia, taprobane(G), thence, sail(A)
+
+**People**: alexander, indians, tribe(A), ichthyophagi(G), megasthenes(G)
+
+**Numeric**: hundred, thousand, fifty(A)
+
+**Precious Stone/Gem**: stones, amber, beryls, rock-crystal, glass, beryls(G)
+
+**Animal/Plant**: elephants, pepper(A)
+
+The categories partly highlights the potential themes in the target corpus, i.e.
+India-related text in *Natural History*, that a lot of geographical details, including land marks, locations and spatial transportation, as well as precious stones and introduction about tribes, historical figures and animal and plants.
+
+It aligns with the general structure of the work, that catelouging the natural, material world in to chapters of geography, anthropology, natural creatures and mineralogy.
+
+And the high ranking words even have more appearences in the reference corpus, as shown in @tbl-kw_frequency_compare.
+
+```{r}
+#| label: tbl-kw_frequency_compare
+#| tbl-cap:  Comparison of overlapping keywords sorted by absolute frequency and G signed with that of reference corpus
+flist_ref_df <- as_tibble(flist_ref)
+words_to_check <- c("india", "hundred", "stones", "arabia", "indian", "alexander",
+                    "amber", "thousand", "elephants", "indus", "glass", "thence",
+                    "ganges", "rock-crystal", "ethiopia", "indians")
+
+filtered_top_scores <- top_scores_kw_df %>%
+  filter(type %in% words_to_check)
+
+abs_freq_lookup <- setNames(flist_ref_df$abs_freq, flist_ref_df$type)
+nrm_freq_lookup <- setNames(flist_ref_df$nrm_freq, flist_ref_df$type)
+
+results <- tibble(
+  Word = filtered_top_scores$type,
+  Target_Frequency = filtered_top_scores$a,
+  Reference_Abs_Frequency = abs_freq_lookup[filtered_top_scores$type],
+  Reference_Nrm_Frequency = nrm_freq_lookup[filtered_top_scores$type]
+) %>% 
+  kbl(col.names = c("Type", "Target_Frequency", "Reference_Abs_Frequency", "Reference_Nrm_Frequency")) %>% 
+  kable_minimal() %>% 
+  scroll_box(height = "400px")
+
+results
+
+```
+
+As PMI score indicates times of probability of the keyword in the target context higher than its probability in all the data taken together, it could serve as a more convincing indicator for the analysis of keywords.
+And in fact, in the sorted top 20 list of PMI, it does showed more detailed information about the context.
+Moreover, almost all of them shown none frequency in the reference corpus, which reinforces the indication that they are distinctly key to the target corpus comparing to that of the other context of the work, as shown in @tbl-kw_frequency_pmi.
+
+```{r}
+#| label: tbl-kw_frequency_pmi
+#| tbl-cap:  Comparison of overlapping keywords sorted by absolute frequency and G signed with that of reference corpus
+
+words_to_check_pmi <- c("india", "ganges", "beryls", "indus", "taprobane",
+                    "ichthyophagi", "megasthenes", "obsidian", "bdellium",
+                    "agates", "callaina", "condensation", "expeditions",
+                    "gerra", "jomanes", "nonius", "patala", "prasii", "alia",
+                    "bactra", "carnelian", "ceylon", "cophes", "hypasis",
+                    "merchandize", "pepper-tree", "sacae", "sandastros",
+                    "thorn-bush")
+
+filtered_top_scores1 <- top_scores_kw_df %>%
+  filter(type %in% words_to_check_pmi)
+
+abs_freq_lookup1 <- setNames(flist_ref_df$abs_freq, flist_ref_df$type)
+nrm_freq_lookup1 <- setNames(flist_ref_df$nrm_freq, flist_ref_df$type)
+
+results1 <- tibble(
+  Word = filtered_top_scores1$type,
+  Target_Frequency = filtered_top_scores1$a,
+  Reference_Abs_Frequency = abs_freq_lookup1[filtered_top_scores1$type],
+  Reference_Nrm_Frequency = nrm_freq_lookup1[filtered_top_scores1$type]
+)%>% 
+  kbl(col.names = c("Type", "Target_Frequency", "Reference_Abs_Frequency", "Reference_Nrm_Frequency")) %>% 
+  kable_minimal() %>% 
+  scroll_box(height = "400px")
+
+results1
+
+```
 
@@
 
-1.  $G^2$ signed highly overlapped with that of absolute frequency. (plot of corelation)
-2.  list the overlapped keywords
-3.  PMI sorting provides more information
+4.  $G^2$ signed highly overlapped with that of absolute frequency. (plot of corelation)
+
+5.  list the overlapped keywords
+
+6.  PMI sorting provides more information
 

### 2023-08-22 freqlist_location.R

@@ -7,12 +7,14 @@ install.packages("quarto")
 install.packages("downlit")
 
 
+
 library('tidyverse')
 library('mclm')
 library('here')
 library('kableExtra')
 library('leaflet')
 library('downlit')
+
 
 data <- read.csv("geotext_whole.csv")
 
@@ -87,7 +89,7 @@ flist_target <- fnames_indiatext %>%
 scores_kw <- assoc_scores(flist_target, flist_ref)
 
 top_scores_kw <- scores_kw %>% 
-  filter(PMI >= 2 & G_signed >= 2)
+  filter(PMI >= 2 & G_signed >= 3.84)
 
 top_scores_kw %>% 
   as_tibble() %>%
@@ -97,6 +99,14 @@ top_scores_kw %>%
   kbl(col.names = c("Type", "Frequency", "PMI", r"(Signed $G^2$)")) %>% 
   kable_minimal() %>% 
   scroll_box(height = "400px") %>%  print()
+
+top_scores_kw_df <- as_tibble(top_scores_kw)
+
+theme_set(theme_minimal(base_size = 15))
+g <- top_scores_kw_df %>%
+  ggplot(aes(x = G_signed, y = a)) +
+  labs(x = "G", y = "afr")
+g + geom_point()
 
 
 keyword_PMI_list <- data.frame(
@@ -122,6 +132,21 @@ ggplot(tag_counts, aes(x = n, y = reorder(Tag, -n), fill = Tag)) +
   labs(x = "Count", y = "Tag", fill = "Tag") +
   theme_minimal() +
   coord_flip()
+
+flist_ref_df <- as_tibble(flist_ref)
+words_to_check <- c("ganges", "beryls", "ichthyophagi", "megasthenes", "obsidian", "bdellium", "agates", "callaina", "condensation", "gerra", "jomanes", "nonius", "prasii", "alia", "carnelian", "cophes", "hypasis", "merchandize", "peppertree", "sacae", "sandastros", "thornbush")
+words_to_check1<- c("india", "hundred", "stones", "arabia", "indian", "alexander",
+                    "amber", "thousand", "elephants", "indus", "glass", "thence",
+                    "ganges", "rock-crystal", "ethiopia", "indians")
+for (word_to_check in words_to_check1){
+  freq <- NA  # Initialize with NA in case the word is not found
+  if (word_to_check %in% names(flist_ref_df)) {
[…]

### 2023-08-22 paper_quarto.qmd
0822 sequence adjust

@@
 Since the research focus is narrowed down to India-related text after the initial exploration, a dataset including all Indian place names mentioned in the text is extracted from the geographical-related text dataset.
-With a reference to *Barrington Atlas of the Greek and Roman World* (@talbert2000a, @talbert2000b), the approximate coordinates defining the Indian region during the time of *Natural Hisoty* are as follows[^3]:
+With a reference to *Barrington Atlas of the Greek and Roman World* (@talbert2000, @talbert2000-1), the approximate coordinates defining the Indian region during the time of *Natural Hisoty* are as follows[^3]:
 
@@
 # Data Analysis
+
+## Collocating word to "India" in *Natural History*
+
+In addition to examining the keywords in the India-related texts, it is also valuable to explore the collocates that appear alongside the word "India" when mentioned in the book.
+
+To analyse the textual collocating bi-gram of word "India", the `mclm::text_cooc()` function was employed, with "india" designated as the target item for the analysis.
+Since the texual collocation of "India" is examinated, the span of the target word is set as the "textual units", to take the broader context into consideration.
+
+And following the same criteria as the previous keyword analysis, the collocation scores were filtered of having both PMI and G_signed scores of 2 or higher.
+By employing this approach, the prominent collocates of "india" were identified, providing a tangible understanding of the prevailing discourse and potentially reflecting Pliny the Elder's perspective on the region.
+
+```{r}
+#| label: collocation
+#| warning: false
+
+coocs <- fnames_wholetext %>% 
+  text_cooc("(?xi)  ^ india $")
+
+# calculate scores
+scores_colloc <- assoc_scores(coocs)
+
+top_scores_colloc <- scores_colloc %>% 
+  filter(PMI >= 2 & G_signed >= 2)
+```
+
+@tbl-coltable_Gsigned and @tbl-coltable_PMI display the top 20 collocates associated with the word "india" in the entire text, respectively sorted by G_signed and PMI scores.
+As the returned $G^2$ score helps gauge the strength of evidence regarding the independence between the two words [@methods], thereby facilitating the initial sorting.
+
+::: panel-tabset
+### Sorted by absolute frequencies
+
+```{r}
+#| label: tbl-coltable_absolute_freqencies
+#| tbl-cap-location: top
+#| tbl-cap: Top 20 collocates to the word "india" in Natural History (sorted by G_signed)
+#| warning: false
+#| echo: false
+top_scores_colloc %>% 
+  as_tibble() %>%
+  select(type, a, PMI, G_signed) %>% 
+  slice_max(order_by = a, n = 20, with_ties = TRUE) %>%
+  kbl(col.names = c("Type", "Frequency", "PMI", r"(Signed $G^2$)"), escape = FALSE) %>%
+  kable_minimal() %>% 
+  scroll_box(height = "400px")
+
+```
+
+### Sorted by G_singed
+
+```{r}
+#| label: tbl-coltable_Gsigned
+#| tbl-cap-location: top
+#| tbl-cap: Top 20 collocates to the word "india" in Natural History (sorted by G_signed)
+#| warning: false
+#| echo: false
+top_scores_colloc %>% 
+  as_tibble() %>%
+  select(type, a, PMI, G_signed) %>% 
+  slice_max(order_by = G_signed, n = 20, with_ties = TRUE) %>%
+  kbl(col.names = c("Type", "Frequency", "PMI", r"(Signed $G^2$)"), escape = FALSE) %>%
+  kable_minimal() %>% 
+  scroll_box(height = "400px")
+
+```
+
+### Sorted by PMI
+
+```{r}
+#| label: tbl-coltable_PMI
+#| tbl-cap-location: top
+#| tbl-cap: Top 20 collocates to the word "india" in Natural History (sorted by PMI)
+
+top_scores_colloc %>% 
+  as_tibble() %>%
+  select(type, a, PMI, G_signed) %>%
+  slice_max(order_by = PMI, n = 20, with_ties = TRUE) %>% 
+  kbl(col.names = c("Type", "Frequency", "PMI", r"(Signed $G^2$)"), escape = FALSE) %>% 
+  kable_minimal() %>% 
+  scroll_box(height = "400px")
+
+```
+:::
+
+Similar to the results of keyword analysis, the top 20 sorted list of absolute frequency and G singed have a 11/20 overlapped outputs.
+As shown in @fig-col_colloc, the signed G score and absolute frequency in textual collocation has a positibe correlation.
+
+```{r}
+#| label: fig-col_colloc
+#| fig-cap: Correlation of signed G and absolute frequency in textual collocation
+
+top_scores_colloc_df <- as_tibble(top_scores_colloc)
+
+g1 <- top_scores_colloc_df %>%
+  ggplot(aes(x = G_signed, y = a)) +
+  labs(x = "signed G", y = "Absolute frequency") +
+  geom_point() +
+  geom_smooth(method = "lm", se = FALSE)
+
+g1
+```
+
+The high-ranking words of textual collocation with "India" in the work are cateforized as follows, those without specifying the association measurement are the overlapped ones:
+
+**Geographical**: arabia, indian, ethiopia, ganges, indus(G)
+
+**Numeric**: hundred, thousand(A), whole(A)
+
+**Time**: year (A)
+
+**Merchandise exchange**: mart(G)
+
+**Precious Stone/Gem**: stones, rock-crystal, gems, pearls, gem(G), gemstone(G)
+
+**Animal/Plant**: elephants, gum(A), lustre(G)
+
+**Historical Figure**: alexander(A), megasthenes(G), onesicritus(G)
+
+**Descriptive expression**: numerous(A), luxury(A), closely(A), valuable(A), bright(A), identical(G), smaragdus(G)
+
+**Others**: shadow(A)
+
+The top 20 collocates associated with the word "India," sorted by their $G^2$ scores, reveal three key dimensions:
+
+1.
+**Geographical Connections**: The collocates such as *arabia*, *ethiopia*, *east*, *south*, *opposite*, and *beyond* indicate the geographical relationships and proximity between India and these regions.
+
+2.
+**Trading and Imports**: The presence of collocates like *imported*, *produces*, *produce* and *nations* suggests that India had a significant role in trade and the importation of goods.
+It also implies that India was known for producing various commodities that were sought after by other nations.
+
+3.
+**Boundaries and Borders**: The collocates *boundary*, *set* and *part* indicate the existence of defined boundaries or borders related to India.
+This suggests that there were recognized territorial demarcations associated with India during the referenced period.
+
+```{r}
+coocs_ref_df <- as_tibble(coocs$ref_freqlist)
+words_to_check_colloc <- c("arabia", "indian", "ethiopia", "ganges", "rock-crystal", "hundred", "elephants", "megasthenes", "indians", "gem", "lustre", "stones", "identical", "'smaragdus", "indus", "gems", "gemstone", "pearls", "onesicritus", "mart")
+filtered_top_scores_colloc <- top_scores_colloc_df %>%
+  filter(type %in% words_to_check_colloc)
+
+abs_freq_lookup1 <- setNames(coocs_ref_df$abs_freq, coocs_ref_df$type)
+nrm_freq_lookup1 <- setNames(coocs_ref_df$nrm_freq, coocs_ref_df$type)
+
+results_colloc <- tibble(
+  Word = filtered_top_scores_colloc$type,
+  Target_Frequency = filtered_top_scores_colloc$a,
+  Reference_Abs_Frequency = abs_freq_lookup1[filtered_top_scores_colloc$type],
+  Reference_Nrm_Frequency = nrm_freq_lookup1[filtered_top_scores_colloc$type]
+) %>% 
+  kbl(col.names = c("Type", "Target_Frequency", "Reference_Abs_Frequency", "Reference_Nrm_Frequency")) %>% 
+  kable_minimal() %>% 
+  scroll_box(height = "400px")
+
+results_colloc
+
+```
+```{r}
+
+words_to_check_colloc_pmi <- c(
+  "megasthenes",
+  "thorn-bush",
+  "carnelian",
+  "obsidian",
+  "cophes",
+  "merchandize",
+  "mart",
+  "expeditions",
+  "patala",
+  "arii",
+  "ichthyophagi",
+  "pursuits",
+  "vermilion",
+  "biggest",
+  "onesicritus",
+  "identical",
+  "ganges",
+  "engrave",
+  "'smaragdus",
+  "honey-coloured",
+  "reflects"
+)
+
+filtered_top_scores_colloc <- top_scores_colloc_df %>%
+  filter(type %in% words_to_check_colloc_pmi)
+
+abs_freq_lookup1 <- setNames(coocs_ref_df$abs_freq, coocs_ref_df$type)
+nrm_freq_lookup1 <- setNames(coocs_ref_df$nrm_freq, coocs_ref_df$type)
+
+results_colloc_pmi <- tibble(
+  Word = filtered_top_scores_colloc$type,
+  Target_Frequency = filtered_top_scores_colloc$a,
+  Reference_Abs_Frequency = abs_freq_lookup1[filtered_top_scores_colloc$type],
+  Reference_Nrm_Frequency = nrm_freq_lookup1[filtered_top_scores_colloc$type]
+) %>% 
+  kbl(col.names = c("Type", "Target_Frequency", "Reference_Abs_Frequency", "Reference_Nrm_Frequency")) %>% 
+  kable_minimal() %>% 
+  scroll_box(height = "400px")
+
+results_colloc_pmi
+```
+
+Within the context of Pliny the Elder's *Natural History* is a book with an encyclopedia scope written in Roman Empire, these collocates suggest the interconnecting role India played in the network of interactions, trade, or cultural exchanges between India and the Mediterranean regions during 1st century AD.
+They highlight India's significance as a trading partner, its geographical positioning, and the recognition of its territorial boundaries.
 
@@
 #| label: fig-col_keyword
-#| tbl-cap:  Scatterplot of G_signed by absolute frequency
+#| fig-cap: Scatterplot of G_signed by absolute frequency
 
@@
 
-**Geographical/Ethnic Group**: india, arabia, indian, ganges, indus, ethiopia, taprobane(G), thence, sail(A)
+**Geographical**: india, arabia, indian, ganges, indus, ethiopia, taprobane(G), thence, sail(A)
 
@@
 
-**Precious Stone/Gem**: stones, amber, beryls, rock-crystal, glass, beryls(G)
+**Precious Stone/Gem**: stones, amber, rock-crystal, glass, beryls(G)
 
@@
 keyword_PMI_list <- data.frame(
-  Word = c("ganges", "beryls", "ichthyophagi", "megasthenes", "obsidian", "bdellium", "agates", "callaina", "condensation", "gerra", "jomanes", "nonius", "prasii", "alia", "carnelian", "cophes", "hypasis", "merchandize", "peppertree", "sacae", "sandastros", "thornbush"),
-  Exp = c("a major river in India", "a type of gemstone", "a group of people who primarily subsist on fish", "a Greek historian and diplomat", "a type of volcanic glass", "a fragrant resin obtained from certain trees", "a type of semiprecious gemstone", "pale green precious stone (lat)", "the process of vapor turning into a liquid state", "war (lat)", "a Roman nomen gentile, gens or \"family name\"", "a Roman nomen gentile, gens or \"family name\"", "prase, green coloured gem", "by another / different way / route (lat)", "a reddish-brown variety of chalcedony", "a river that rises in the ancient Paropamise range, eventually falling into the Indus river near its confluence with the Cophes river", "a river in north India", "goods or commodities", "a tree that produces peppercorns", "the easternmost nation of Elibe, situated to the south of Ilia and the north of Bern", "a precious stone found in India and Arabia", "any of many thorny or spiny shrubs and bushes"),
-  Tag = c("river", "goods", "people", "people", "goods", "goods", "goods", "goods", "activity", "activity", "people", "people", "goods", "route", "goods", "river", "river", "goods", "tree", "river", "goods", "tree"),
-  Sub_tag = c("N/A", "stone", "group of people", "famous people", "others", "others", "stone", "stone", "producing activity", "N/A", "human name", "human name", "stone", "N/A", "stone", "N/A", "N/A", "general", "origin of goods", "N/A", "stone", "N/A")
+  Word = c("india", "ganges", "beryls", "indus", "taprobane", "ichthyophagi", "megasthenes", "obsidian", "bdellium", "agates", "callaina", "condensation", "expeditions", "gerra", "jomanes", "nonius", "patala", "prasii", "alia", "bactra", "carnelian", "ceylon", "cophes", "hypasis", "merchandize", "peppertree", "sacae", "sandastros", "thornbush"),
+  Exp = c("name of the focused region of this study", "a major river in India", "a type of gemstone", "a major river in India", "Island in Sri Lanka", "a group of people who primarily subsist on fish", "a Greek historian and diplomat", "a type of volcanic glass", "a fragrant resin obtained from certain trees", "a type of semiprecious gemstone", "pale green precious stone (lat)", "the process of vapor turning into a liquid state", "referring to the expedition of Alexander the Great", "war (lat)", "name of a river", "a Roman nomen gentile, gens or \"family name\"", "refer to a city in Indian region", "prase, green coloured gem", "by another / different way / route (lat)", "name of a city in Asia Minor", "a reddish-brown variety of chalcedony", "name of an Island in Indian subcontinent", "a river that rises in the ancient Paropamise range, eventually falling into the Indus river near its confluence with the Cophes river", "a river in north India", "goods or commodities", "a tree that produces peppercorns", "the easternmost nation of Elibe, situated to the south of Ilia and the north of Bern", "a precious stone found in India and Arabia", "any of many thorny or spiny shrubs and bushes"),
+  Category = c("region", "river", "goods", "river", "region", "people", "people", "goods", "goods", "goods", "goods", "activity", "activity", "activity", "river", "people", "region", "goods", "route", "region", "goods", "region", "river", "river", "goods", "plant", "river", "goods", "plant"),
+  Remark = c("N/A", "N/A", "gemstone", "N/A", "N/A", "tribe", "referencing scholar", "other goods", "other goods", "gemstone", "gemstone", "producing activity", "N/A", "N/A", "N/A", "human name", "N/A", "gemstone", "N/A", "N/A", "gemstone", "N/A", "N/A", "N/A", "general goods", "origin of goods", "N/A", "gemstone", "N/A")
 )
@@
   as_tibble() %>%
-  select(Word, Exp, Tag, Sub_tag) %>%                        
-  kbl(col.names = c("Word", "Exp", "Category", "Sub_category")) %>% 
+  select(Word, Exp, Category, Remark) %>%                        
+  kbl(col.names = c("Word", "Exp", "Category", "Remark")) %>% 
   kable_minimal()
@@
 tag_counts <- keyword_PMI_list %>%
-  count(Tag) %>%
+  count(Category) %>%
   arrange(desc(n))
@@
 # Plot the tag distribution
-ggplot(tag_counts, aes(x = n, y = reorder(Tag, -n), fill = Tag)) +
+ggplot(tag_counts, aes(x = n, y = reorder(Category, -n), fill = Category)) +
   geom_bar(stat = "identity") +
-  labs(x = "Count", y = "Tag", fill = "Tag") +
+  labs(x = "Count", y = "Category", fill = "Category") +
   theme_minimal() +
@@
 
-## Collocating word to "India" in *Natural History*
-
-In addition to examining the keywords in the India-related texts, it is also valuable to explore the collocates that appear alongside the word "India" when mentioned in the book.
-
-To analyse the textual collocating bi-gram of word "India", the `mclm::text_cooc()` function was employed, with "india" designated as the target item for the analysis.
-And following the same criteria as the previous keyword analysis, the collocation scores were filtered of having both PMI and G_signed scores of 2 or higher.
-By employing this approach, the prominent collocates of "india" were identified, providing a tangible understanding of the prevailing discourse and potentially reflecting Pliny the Elder's perspective on the region.
-
-```{r}
-#| label: collocation
-#| warning: false
-
-coocs <- fnames_wholetext %>% 
-  text_cooc("(?xi)  ^ india $")
-
-# calculate scores
-scores_colloc <- assoc_scores(coocs)
-
-top_scores_colloc <- scores_colloc %>% 
-  filter(PMI >= 2 & G_signed >= 2)
-```
-
-@tbl-coltable_Gsigned and @tbl-coltable_PMI display the top 20 collocates associated with the word "india" in the entire text, respectively sorted by G_signed and PMI scores.
-As the returned $G^2$ score helps gauge the strength of evidence regarding the independence between the two words [@methods], thereby facilitating the initial sorting.
-
-::: panel-tabset
-### Sorted by absolute frequencies
-
-```{r}
-#| label: tbl-coltable_absolute_freqencies
-#| tbl-cap-location: top
-#| tbl-cap: Top 20 collocates to the word "india" in Natural History (sorted by G_signed)
-#| warning: false
-#| echo: false
-top_scores_colloc %>% 
-  as_tibble() %>%
-  select(type, a, PMI, G_signed) %>% 
-  slice_max(order_by = a, n = 20, with_ties = TRUE) %>%
-  kbl(col.names = c("Type", "Frequency", "PMI", r"(Signed $G^2$)"), escape = FALSE) %>%
-  kable_minimal() %>% 
-  scroll_box(height = "400px")
-
-```
-
-### Sorted by G_singed
-
-```{r}
-#| label: tbl-coltable_Gsigned
-#| tbl-cap-location: top
-#| tbl-cap: Top 20 collocates to the word "india" in Natural History (sorted by G_signed)
-#| warning: false
-#| echo: false
-top_scores_colloc %>% 
-  as_tibble() %>%
-  select(type, a, PMI, G_signed) %>% 
-  slice_max(order_by = G_signed, n = 20, with_ties = TRUE) %>%
-  kbl(col.names = c("Type", "Frequency", "PMI", r"(Signed $G^2$)"), escape = FALSE) %>%
-  kable_minimal() %>% 
-  scroll_box(height = "400px")
-
-```
-
-### Sorted by PMI
-
-```{r}
-#| label: tbl-coltable_PMI
-#| tbl-cap-location: top
-#| tbl-cap: Top 20 collocates to the word "india" in Natural History (sorted by PMI)
-#| warning: false
-#| echo: false
-
-top_scores_colloc %>% 
-  as_tibble() %>%
-  select(type, a, PMI, G_signed) %>%
-  slice_max(order_by = PMI, n = 20, with_ties = TRUE) %>% 
-  kbl(col.names = c("Type", "Frequency", "PMI", r"(Signed $G^2$)"), escape = FALSE) %>% 
-  kable_minimal() %>% 
-  scroll_box(height = "400px")
-
-```
-:::
-
-The top 20 collocates associated with the word "India," sorted by their $G^2$ scores, reveal three key dimensions:
-
-1.
-**Geographical Connections**: The collocates such as *arabia*, *ethiopia*, *east*, *south*, *opposite*, and *beyond* indicate the geographical relationships and proximity between India and these regions.
-
-2.
-**Trading and Imports**: The presence of collocates like *imported*, *produces*, *produce* and *nations* suggests that India had a significant role in trade and the importation of goods.
-It also implies that India was known for producing various commodities that were sought after by other nations.
-
-3.
-**Boundaries and Borders**: The collocates *boundary*, *set* and *part* indicate the existence of defined boundaries or borders related to India.
-This suggests that there were recognized territorial demarcations associated with India during the referenced period.
-
-4.  $G^2$ signed highly overlapped with that of absolute frequency. (plot of corelation)
-
-5.  list the overlapped keywords
-
-6.  PMI sorting provides more information
-
-Within the context of Pliny the Elder's *Natural History* is a book with an encyclopedia scope written in Roman Empire, these collocates suggest the interconnecting role India played in the network of interactions, trade, or cultural exchanges between India and the Mediterranean regions during 1st century AD.
-They highlight India's significance as a trading partner, its geographical positioning, and the recognition of its territorial boundaries.
-
 # Conclusion

### 2023-08-22 freqlist_location.R

@@ -141,12 +141,11 @@ words_to_check1<- c("india", "hundred", "stones", "arabia", "indian", "alexander
 for (word_to_check in words_to_check1){
   freq <- NA  # Initialize with NA in case the word is not found
   if (word_to_check %in% names(flist_ref_df)) {
-    freq <- flist_ref$[[word_to_check]]  # Adjust this based on your data structure
+    freq <- flist_ref_df$[[word_to_check]]  # Adjust this based on your data structure
   }
   cat("Frequency of '", word_to_check, "':", freq, "\n")
 }
 
-flist_ref_df$abs_freq[flist_ref_df$type == 'elephants']
 
 
 coocs <- fnames_wholetext %>% 
@@ -165,6 +164,80 @@ top_scores_colloc %>%
   kbl(col.names = c("Type", "Frequency", "PMI", r"(Signed $G^2$)"), escape = FALSE) %>%
   kable_minimal() %>% 
   scroll_box(height = "400px") %>% print()
+
+top_scores_colloc_df <- as_tibble(top_scores_colloc)
+g1 <- top_scores_colloc_df %>%
+  ggplot(aes(x = G_signed, y = a)) +
+  labs(x = "signed G", y = "Absolute frequency") +
+  geom_point() +
+  geom_smooth(method = "lm", se = FALSE) 
+
+
+
+coocs_ref_df <- as_tibble(coocs$ref_freqlist)
+words_to_check_colloc <- c("arabia", "indian", "ethiopia", "ganges", "rock-crystal", "hundred", "elephants", "megasthenes", "indians", "gem", "lustre", "stones", "identical", "'smaragdus", "indus", "gems", "gemstone", "pearls", "onesicritus", "mart")
+filtered_top_scores_colloc <- top_scores_colloc_df %>%
+  filter(type %in% words_to_check_colloc)
+
+abs_freq_lookup1 <- setNames(coocs_ref_df$abs_freq, coocs_ref_df$type)
+nrm_freq_lookup1 <- setNames(coocs_ref_df$nrm_freq, coocs_ref_df$type)
+
+results_colloc <- tibble(
+  Word = filtered_top_scores_colloc$type,
+  Target_Frequency = filtered_top_scores_colloc$a,
+  Reference_Abs_Frequency = abs_freq_lookup1[filtered_top_scores_colloc$type],
[…]

### 2023-08-22 paper_quarto.qmd
0822 structure modification

@@
 The study focuses on uncovering prominent themes and topics associated with India in the context of the book.
-The research employs keyword analysis and collocate examination techniques to reveal significant insights into the perception and imagination of India, as a competent counterpart to the Roman Empire, by Pliny the Elder and the scholars of his time.'
+The research employs collocate examination techniques and keyword analysis to reveal significant insights into the perception and imagination of India, as a competent counterpart to the Roman Empire, by Pliny the Elder and the scholars of his time.'
 ---
@@
 
-Building upon this observation, the study focus is narrowed down to India-related text in *Natural History*, aiming to delve deeper into the themes associated with the Indian region referred in the text by employing keyword analysis and collocation analysis methods within the framework of corpus linguistics.
+Building upon this observation, the study focus is narrowed down to India-related text in *Natural History*, aiming to delve deeper into the themes associated with the Indian region referred in the text by employing collocation analysis and keyword analysis methods within the framework of corpus linguistics.
 
@@
 
-To investigate the prominent themes in the India-related content discussed in *Natural History*, methods of keyword analysis and collocation analysis are employed for this study.
+To investigate the prominent themes in the India-related content discussed in *Natural History*, methods of collocation analysis and keyword analysis are employed for this study.
 Both of the analyses rely on the `mclm::assoc_scores` objects of the [mclm](https://github.com/masterclm/mclm) package, which return frequencies and association scores of a certain event in a target context and in a reference context.
@@
 
+## Collocation Analysis
+
+Collocation analysis is a technique employed in corpus linguistics to identify words that often appear together in a language.
+This technique is rooted in the notion that particular words tend to appear together more often than would occur by chance.
+In the context of this study, lists of the highly possible co-occuring word with "India" in the text of *Natural History* can shed a light on the potential themes and topics about India discussed in the work.
+
+Combining the two methods, and integrating with a close reading of the text, this study aims to discuss what about "India" is discussed in *Natural History*.
+
 ## Keyword Analysis
@@
 As indicated by the measurements, the listed words tend to be more frequently occur in the context pertaining India than other parts of the work, hence they seem to be the potential keywords about India in *Natural History*.
-
-## Collocation Analysis
-
-Collocation analysis is a technique employed in corpus linguistics to identify words that often appear together in a language.
-This technique is rooted in the notion that particular words tend to appear together more often than would occur by chance.
-In the context of this study, lists of the highly possible co-occuring word with "India" in the text of *Natural History* can shed a light on the potential themes and topics about India discussed in the work.
-
-Combining the two methods, and integrating with a close reading of the text, this study aims to discuss what about "India" is discussed in *Natural History*.
 
@@
 In conclusion, this paper located the research question on potential theme and topics in texts about India in Pliny the Elder's *Natural History* based on the prominent distribution of "India" in the entire text comparing to other place names.
-The analysis was conducted with the keyword analysis and collocation analysis in a framework of corpus linguistics.
+The analysis was conducted with the collocation analysis and keyword analysis in a framework of corpus linguistics.
 

### 2023-08-24 paper_quarto.qmd
0824 wording refine

@@
 knitr::write_bib(
-  c("base", "mclm", "ggplot2", "tidyverse", "leaflet", "downlit"),
+  c("base", "mclm", "tidyverse", "leaflet", "kableExtra", "downlit"),
   here("packages.bib")
@@
 
-[^1]: This study is a pilot study of my master thesis, so the description of the research question is connected with that of this [paper](https://raw.githack.com/lizaodawn/NH_thesis/main/NHthesis_structure.html#sec-introduction).
+[^1]: The present paper is a pilot study of my master thesis, *Mapping India in Pliny the Elder's Natural History*, thus the description of the research question is connected with the content in this [thesis](https://raw.githack.com/lizaodawn/NH_thesis/main/NHthesis_structure.html#sec-introduction).
 
@@
 Written around AD 77, the work is thematically divided into 37 books, covering a diverse range of subjects including astronomy, geography, zoology, botany, medicine, and more.
-Driven by a pioneering attempt to catalogue human knowledge from his era, Pliny made a comprehensive reference to a wide range of Greek and Roman scholarships, and interwove his own literary interpretation or comments to the narratives in *Natural Hisrory*.
+Driven by a pioneering attempt to catalog human knowledge from his era, Pliny made a comprehensive reference to a wide range of Greek and Roman scholarships, and interwove his own literary interpretation or comments to the narratives in *Natural History*.
 
 *Natural History* stands as a seminal work in the history of encyclopedias, serving as a gateway to understanding the knowledge and worldview of ancient Rome.
-Beyond its role as a compendium of diverse subjects, the text provides a captivating glimpse into the knowledge, cultural, and merchandise exchange [@dodd2021] between the Roman Empire and other regions while shedding a light on the spatial perception and imagination of Pliny and the scholarly references of his time [@plinyth2011].
+Beyond its role as a compendium of diverse subjects, the text provides a captivating glimpse into the knowledge, cultural, and merchandise exchange [@dodd2021] between the Roman Empire and other regions [@plinyth2011].
 
-As pointed out by @beagon2011, differentiating from his predecessors, Pliny showed a "terrestrial curiosity" in Natural History, emphasising recognition of the physical, material world.
-Drawing from the long-established topographical and ethnographic traditions, Pliny connects volumes dedicated to geography (books 3-6) with broader elements, activities, and cultural, historical, and societal contexts [@roller2022], exemplified in his portrayal of exotic plants, communities' habitats, imperial expeditions, and trade products.
-In this regard, geographical names mentioned in the text plays a pivotal role in distributing information, knowledge, and discussions throughout *Natural History*.
+As pointed out by @beagon2011, differentiating from his predecessors, Pliny showed a "terrestrial curiosity" in *Natural History*, emphasizing recognition of the physical, material world.
+Drawing from the long-established topographical and ethnographic traditions, Pliny connects volumes dedicated to geography (books 3-6) with broader natural elements, human activities, and cultural, historical, and societal contexts [@roller2022], exemplified in his description of plants, tribe habitats, imperial expeditions, and trade products.
+In this regard, this study aims to analyse the text of *Natural History* in a spatial scope, as geographical names mentioned in the text plays a pivotal role in distributing information, knowledge, and discussions throughout the work.
 
 *Natural History* is originally in Latin.
-For this study, an English translation by Henry T.
-Riley (1816-1878) and John Bostock (1773-1846), first published in 1855, is utilized.
-The translated text is obtained in a digitised version from the [TOPOSText project](https://topostext.org/the-project), having been sourced from the Perseus Project and governed by a Creative Commons Attribution-Share-Alike 3.0 U.S.
+An English translation by Henry T.
+Riley (1816-1878) and John Bostock (1773-1846), first published in 1855, is utilized for this study.
+The translated text is obtained in a digitized version from the [TOPOSText project](https://topostext.org/the-project), having been sourced from the Perseus Project and governed by a Creative Commons Attribution-Share-Alike 3.0 U.S.
 License.
 
-In addition to the digitised textual content of *Natural History*, the place names mentioned in the text are annotated with their corresponding coordinates on TOPOXText.
-The annotations are available in an HTML format, which were sparsed and restructured into a dataset of geographical-related text in *Natural History* with [Beautiful Soup](https://www.crummy.com/software/BeautifulSoup/bs4/doc/) library in Python[^2].
-The dataset structure, corpus scraping procedure and and corpus extention will be further elaborated in Corpus Description section (@sec-corpus).
+In addition to the digitized textual content of *Natural History*, the place names mentioned in the text are annotated with their corresponding coordinates on TOPOXText.
+Since the annotations are available in an HTML format, they are scraped and restructured into a dataset of geographical-related text in *Natural History* with [Beautiful Soup](https://www.crummy.com/software/BeautifulSoup/bs4/doc/) library in Python[^2].
+The dataset structure, corpus scraping procedure and and corpus extension will be further explained in Corpus Description section (@sec-corpus).
 
-[^2]: The sparsing [code](https://github.com/lizaodawn/zhuang/blob/papertry/Natural%20History_corpus.ipynb) is uploaded to the same repository of the project.
+[^2]: The scraping [code](https://github.com/lizaodawn/zhuang/blob/papertry/Natural%20History_corpus.ipynb) is uploaded to the same repository of the project.
 
-As a starting point, @fig-geoname reveals the Top 20 distinct geographical names mentioned within the text.
+As a starting point of this study, @fig-top20geoname reveals the 20 most frequently mentioned geographical names within the text.
 
 ```{r}
-#| label: fig-geoname
-#| fig-cap: Bar chart for top 20 distinct place names mentioned in *Natural History*
-#| fig-cap-location: top
-#| warning: false
-#| echo: false
+#| label: fig-top20geoname
+#| fig-cap: Top 20 most frequently mentioned place names in *Natural History*
 
@@
 
-# Create a bar chart using ggplot2
 top_20_summary_data <- summary_data %>%
@@
 
-An intriguing observation from this analysis, as depicted in @fig-map, is that India seems prominently mentioned in the work despite being outside the Mediterranean.
+Additionally, @fig-geonamemap depicted the times of each place name found mentioned in the work on a map.
+The individual places are represented by distinct dots, and its occurring times in the text are represented by the size of the dots.
+The larger the dot size, the more frequent it is appeared in the context.
 
 ```{r}
-#| label: fig-map
-#| fig-cap: Mapping of geographical names mentioned in Natural History
+#| label: fig-geonamemap
+#| fig-cap: Mapping of geographical names mentioned in *Natural History*
 #| fig-cap-location: top
@@
 
-Building upon this observation, the study focus is narrowed down to India-related text in *Natural History*, aiming to delve deeper into the themes associated with the Indian region referred in the text by employing collocation analysis and keyword analysis methods within the framework of corpus linguistics.
+An intriguing observation from these figures is that India seems being prominently mentioned in the work despite locating outside the Mediterranean.
 
-The analysis is conducted in R environment [@R-base], and the main anlysing methods are applied through functions from [mclm](https://masterclm.github.io/mclm/) [@R-mclm] package.
-In addition, [tidyverse](https://www.tidyverse.org/) [@R-tidyverse] and [leaflet](https://rstudio.github.io/leaflet/) [@R-leaflet] are used for data manipulation and visualisation.
+Building upon this observation, the study focus is narrowed down to India-related text in *Natural History*.
+By delving deeper into the themes associated with the Indian region referred in the text, this study aims to examine the portrayal of India by Pliny the Elder, which potentially shed a light on the spatial perception and imagination of the representative writers and scholars of ancient Rome.
 
-# Methodology
+# Methodology {#sec-method}
 
-To investigate the prominent themes in the India-related content discussed in *Natural History*, methods of collocation analysis and keyword analysis are employed for this study.
-Both of the analyses rely on the `mclm::assoc_scores` objects of the [mclm](https://github.com/masterclm/mclm) package, which return frequencies and association scores of a certain event in a target context and in a reference context.
+To investigate the prominent themes in the India-related content discussed in *Natural History*, the study generally employs methods of collocation analysis and keyword analysis in corpus linguistics, and is conducted in R environment [@R-base].
+The discussions are based on the `mclm::assoc_scores` objects returned from [mclm](https://masterclm.github.io/mclm/) [@R-mclm] package.
+In addition, [tidyverse](https://www.tidyverse.org/) [@R-tidyverse] and [leaflet](https://rstudio.github.io/leaflet/) [@R-leaflet] packages are used for data manipulation and visualization.
 
-Both of the methods will be examined by three association measurements, namely absolute frequency, PMI and $G^2$ signed, to discuss with the context in *Natural History* and the potential theme it indicates.
+In the Data Analysis section (@sec-data_analysis), both of the collocation and keyword analysis are examined by three association measures, namely absolute frequency, PMI and signed $G^2$ for discussing the potential theme it inferred integrating with a close reading of the context.
 
-PMI measures the association strength between two words by comparing their observed co-occurrence frequency with their expected co-occurrence frequency by chance.
-It highlights words that appear together more frequently than expected.
+Absolute frequency refers to the simple count of each single type (distinct word) observed in the text.
+In the case of collocation analysis, it shows the time a type collocates with the target word.
+While in the case of keyword analysis, it shows the time a type occurs in the target corpus.
+As a basic counting measure, absolute frequency provide an overview of the word distribution with limited insights.
+
+PMI (Pointwise Mutual Information) is one of effect size measures for association.
+It compares the observed co-occurring frequency of two outcomes to the probability of either of them occurring independently.
+It can be applied to observe word association, and the association between words and context categories as well [@bestvater2022].
+As the PMI value increases by one, the probability becomes twice as high.
 High PMI values indicates strong associations.
-High $G^2$ values suggest that the co-occurrence is unlikely to occur by chance.
 
-$G^2$ is a statistical test that measures the independence or association between two categorical variables (words in this case).
-It compares the observed co-occurrence frequencies with the expected frequencies under the assumption of independence.
-Higher $G^2$ values suggest a stronger association.
+$G^2$ refers to the log-likelihood ratio for measuring the strength of statistical evidence of the observasion [@blume2017].
+In the context of this study, it indicates how significant the association between the two factors (either for two words or for keywords associating with a target corpus) is.
+Specificly, the signed $G^2$ score returned by `mclm::assoc_scores` shows the strength of evidence for attraction, i.e.
+co-occurrence.
+High signed $G^2$ values suggest that the co-occurrence is unlikely to occur by chance.
+
+Since a PMI score higher than two indicates a four times higher probability of association, and a signed $G^2$ score higher than 3.84 indicates a significant association at a 95% confidence level [@montes2022], a filter of "PMI \>= 2 & G_signed \>= 3.84" is applied for the returned objects of `mclm::assoc_scores` for both of the methods, in order to gain strong and significant association outputs for further discussion.
 
@@
 
-Collocation analysis is a technique employed in corpus linguistics to identify words that often appear together in a language.
-This technique is rooted in the notion that particular words tend to appear together more often than would occur by chance.
-In the context of this study, lists of the highly possible co-occuring word with "India" in the text of *Natural History* can shed a light on the potential themes and topics about India discussed in the work.
+Collocation analysis is a technique employed in corpus linguistics to identify words that often appear together in a given text.
+This technique is rooted in the notion that particular words tend to appear together more often than they would occur by chance.
 
-Combining the two methods, and integrating with a close reading of the text, this study aims to discuss what about "India" is discussed in *Natural History*.
+In this study, the textual collocating word with "India" in *Natural History* is examined.
+Lists of highly frequent co-occurring word with "India" in the context are obtained and sorted by scores of different measurements.
+The potential theme of India-related content in the work can be discussed based on the output of textual collocation of word "India".
 
@@
 Keyword analysis is a statistical method used in corpus linguistics to identify words that occur more frequently in a target corpus than in a reference corpus.
-Defined with different associate measurements, the "keyness" of words are calculated and indicated which words are statistically more frequent appeared in the target corpus comparing to that of the reference corpus.
+The words showing higher association with the target corpus comparing to its frequency in the reference corpus are seen as the "keyword" of the target corpus.
 
-In this study, the *target corpus* includes all paragraphs in *Natural History* mentioning Indian regions, and the **reference corpus** contains all other paragraphs in the work.
-Lists of 20 words with the highest score in different association measurements are discussed with the textual context.
-As indicated by the measurements, the listed words tend to be more frequently occur in the context pertaining India than other parts of the work, hence they seem to be the potential keywords about India in *Natural History*.
+In this study, the **target corpus** includes all paragraphs in *Natural History* mentioning place names in Indian regions, and the **reference corpus** contains all other paragraphs in the work.
+Lists of words with relatively higher frequency in the target corpus are obtained and sorted by scores of different measurements.
+The "keywords" found in India-related text in *Natural History* provides more descriptive information about the topics and elements related to "India" in Pliny's narrative.
+
+Combining the two methods, and integrating with a close reading of the text, this study aims to gain insights about how "India" is discussed and portrayed in *Natural History*.
 
@@
 
-The digitised text is avalible in paragraphs with geographical annotations on TOPOSText website as two parts, [book 1-11](https://topostext.org/work/148) and [book 12-37](https://topostext.org/work/153), both of which are in HTML format.
-Extracting all the "place" class in the HTML files, a dataset containing all annotated place names in the work, the URI and corresponding coordinates of the place, the book/chapter/paragraph number where it is mentioned, as well as the coordinating textual content are structured as a dataset of geographic-related text in *Natural History*.
+The digitized text is available in paragraphs with geographical annotations on TOPOSText website as two parts, [book 1-11](https://topostext.org/work/148) and [book 12-37](https://topostext.org/work/153), both of which are in HTML format.
+Extracting all "place" class in the HTML files, information of all annotated place names in the work, the URI and corresponding coordinates of the place, the book/chapter/paragraph number where it is mentioned, as well as the coordinating textual content is structured as a dataset of geographical-related text in *Natural History*.
 This dataset is used for an initial exploration of the prominent mentioned places in the text.
 
-Since the research focus is narrowed down to India-related text after the initial exploration, a dataset including all Indian place names mentioned in the text is extracted from the geographical-related text dataset.
-With a reference to *Barrington Atlas of the Greek and Roman World* (@talbert2000, @talbert2000-1), the approximate coordinates defining the Indian region during the time of *Natural Hisoty* are as follows[^3]:
+The initial obeservation shown in @fig-top20geoname and @fig-geonamemap leads to a focus to the India-related text for this study.
+With a reference to *Barrington Atlas of the Greek and Roman World* (@talbert2000; @talbert2000-1), the approximate geographical coordinates defining the Indian region during the time of *Natural Hisoty* are as follows[^3]:
 
@@
 The records in geographical-related text dataset with corresponding coordinates falling within the specified range are extracted as the India-related text dataset.
-
-Each distinct paragraph in the India-related text dataset is extracted and stored in TXT format as separate files within a corpus folder, comprising a total of 146 files as the **target corpus** for India-related text in *Natural History*.
-The file names contain information about the book, chapter, and paragraph numbers.
-
-And the full text of the entire work, segregating in paragraphs, are scraped and stored in TXT format and excluded the files in **target corpus** to serve as a **reference corpus**.
-
-The text are set into lower case in the corpus file extraction process.
 
@@
 
+Each distinct paragraph in the India-related text dataset is extracted and stored in TXT format as separate files within a corpus folder, comprising a total of `length(fname_indiatext)` files as the **target corpus**.
+The file names contain information about the book, chapter, and paragraph number of the text.
+
+And the full text of the entire work, separated in paragraphs, are also scraped and stored in TXT format.
+Excluding those in **target corpus**, the other part of the work, containing `length(fname_wholetext_filtered)` files, serve as a **reference corpus**.
+
+The text are set into lower case in the corpus file extraction process.
+
 The **target corpus** consists of all text related to India in paragraphs, containing `r prettyNum(n_tokens(flist_target))` tokens and `r n_types(flist_target)` types, with the type-token ratio of `r round(n_types(flist_target)/n_tokens(flist_target), 2)`.
@@
 
-# Data Analysis
+# Data Analysis {#sec-data_analysis}
 
-## Collocating word to "India" in *Natural History*
+## Textual collocating word with "India" in *Natural History*
 
-In addition to examining the keywords in the India-related texts, it is also valuable to explore the collocates that appear alongside the word "India" when mentioned in the book.
+To analyse the textual collocating word with "India", the `mclm::text_cooc()` function was employed, with "India" designated as the target item for the analysis.
+Since the textual collocation of "India" is examined, the span of the target word is set as the "textual units", to take the broader context into consideration.
 
-To analyse the textual collocating bi-gram of word "India", the `mclm::text_cooc()` function was employed, with "india" designated as the target item for the analysis.
-Since the texual collocation of "India" is examinated, the span of the target word is set as the "textual units", to take the broader context into consideration.
-
-And following the same criteria as the previous keyword analysis, the collocation scores were filtered of having both PMI and G_signed scores of 2 or higher.
-By employing this approach, the prominent collocates of "india" were identified, providing a tangible understanding of the prevailing discourse and potentially reflecting Pliny the Elder's perspective on the region.
+As mentioned in the Methodology Section (@sec-method), the collocation scores were filtered for those having PMI scores higher than 2 and signed $G^2$ scores higher than 3.84.
+By employing this approach, the prominent collocates of "India" were identified, providing a tangible understanding of the prevailing discourse and potentially reflecting Pliny the Elder's perspective on the region.
 
@@
 top_scores_colloc <- scores_colloc %>% 
-  filter(PMI >= 2 & G_signed >= 2)
+  filter(PMI >= 2 & G_signed >= 3.84)
 ```
@@
 @tbl-coltable_Gsigned and @tbl-coltable_PMI display the top 20 collocates associated with the word "india" in the entire text, respectively sorted by G_signed and PMI scores.
-As the returned $G^2$ score helps gauge the strength of evidence regarding the independence between the two words [@methods], thereby facilitating the initial sorting.
+As the returned $G^2$ score helps gauge the strength of evidence regarding the independence between the two words [@montes2022], thereby facilitating the initial sorting.
 
@@
 ```
+
 ```{r}
@@
 The association score is filtered based on the criteria of both PMI and $G^2$ scores, requiring a minimum score of 2.
-This criterion ensures that the selected words have a probability at least four times higher than the overall data, along with statistically significant supporting evidence [@methods], allowing to identify the most statistically significant keywords in India-related texts when compared to the reference corpus.
+This criterion ensures that the selected words have a probability at least four times higher than the overall data, along with statistically significant supporting evidence [@montes2022], allowing to identify the most statistically significant keywords in India-related texts when compared to the reference corpus.
 
@@
 top_scores_kw <- scores_kw %>% 
-  filter(PMI >= 2 & G_signed >= 2)
+  filter(PMI >= 2 & G_signed >= 3.84)
 
@@
 The following tables present the top 20 keywords in India-related texts as compared to the entire texts in *Natural History*.
-They are sorted based on their PMI (@tbl-kwtable_PMI), Absolute frequencies(@tbl-kwtable_absolute_freqencies) and G_signed scores (@tbl-kwtable_Gsigned), respectively.
+They are sorted based on their PMI (@tbl-kwtable_PMI), Absolute frequencies (@tbl-kwtable_absolute_freqencies) and G_signed scores (@tbl-kwtable_Gsigned), respectively.
 The initial sorting was carried out based on the PMI scores (@tbl-kwtable_PMI), since the it serves as a crucial indicator for measuring the keyness of words.

### 2023-08-24 freqlist_location.R

@@ -78,7 +78,7 @@ fnames_wholetext_filtered <- fnames_wholetext[fnames_wholetext_short %in% fnames
 # build frequency list for reference corpus
 flist_ref <- fnames_wholetext_filtered %>%
   freqlist(re_token_transf_in = "'", 
-           token_transf_out = "") %>% print(20)
+           token_transf_out = "") 
 
 # build frequency list for target corpus
 flist_target <- fnames_indiatext %>% 
@@ -155,7 +155,7 @@ coocs <- fnames_wholetext %>%
 scores_colloc <- assoc_scores(coocs)
 
 top_scores_colloc <- scores_colloc %>% 
-  filter(PMI >= 2 & G_signed >= 2)
+  filter(PMI >= 2 & G_signed >= 3.84)
 
 top_scores_colloc %>% 
   as_tibble() %>%

### 2023-08-24 paper_quarto.qmd
0824 minor update

@@
 
-Each distinct paragraph in the India-related text dataset is extracted and stored in TXT format as separate files within a corpus folder, comprising a total of `length(fname_indiatext)` files as the **target corpus**.
+Each distinct paragraph in the India-related text dataset is extracted and stored in TXT format as separate files within a corpus folder, comprising a total of `r length(fnames_indiatext)` files as the **target corpus**.
 The file names contain information about the book, chapter, and paragraph number of the text.
@@
 And the full text of the entire work, separated in paragraphs, are also scraped and stored in TXT format.
-Excluding those in **target corpus**, the other part of the work, containing `length(fname_wholetext_filtered)` files, serve as a **reference corpus**.
+Excluding those in **target corpus**, the other part of the work, containing `r length(fnames_wholetext_filtered)` files, serve as a **reference corpus**.
 
@@
 
-To analyse the textual collocating word with "India", the `mclm::text_cooc()` function was employed, with "India" designated as the target item for the analysis.
-Since the textual collocation of "India" is examined, the span of the target word is set as the "textual units", to take the broader context into consideration.
+Textual collocation refers to the frequently occurring word with the target word in the context.
+Different from the surface collocation, which only taking the word left and right to the target word, the word span in this case refers to the "textual units" around the target word.
+Setting "India" as the target word in the corpus of all paragraphs in *Natural History*, the `mclm::text_cooc()` function returns the frequency of words observed in the context of "India".
+As mentioned in the Methodology Section (@sec-method), the returned scores were filtered for those having PMI scores higher than 2 and signed $G^2$ scores higher than 3.84, in order to gain a strong and significant word list co-occurring with word "India" in the context.
 
-As mentioned in the Methodology Section (@sec-method), the collocation scores were filtered for those having PMI scores higher than 2 and signed $G^2$ scores higher than 3.84.
-By employing this approach, the prominent collocates of "India" were identified, providing a tangible understanding of the prevailing discourse and potentially reflecting Pliny the Elder's perspective on the region.
+The prominent textual collocates of "India" identified with this approach suggests the potential themes about Indian region in the narrative of Pliny.
 

### 2023-08-24 paper_quarto.qmd
0824 collocation part update

@@
 tbl-cap-location: top
+fig-cap-location: top
 bibliography:
@@
 The initial obeservation shown in @fig-top20geoname and @fig-geonamemap leads to a focus to the India-related text for this study.
-With a reference to *Barrington Atlas of the Greek and Roman World* (@talbert2000; @talbert2000-1), the approximate geographical coordinates defining the Indian region during the time of *Natural Hisoty* are as follows[^3]:
+With a reference to *Barrington Atlas of the Greek and Roman World* [@talbert2000; @talbert2000-1], the approximate geographical coordinates defining the Indian region during the time of *Natural Hisoty* are as follows[^3]:
 
@@
 
-Textual collocation refers to the frequently occurring word with the target word in the context.
-Different from the surface collocation, which only taking the word left and right to the target word, the word span in this case refers to the "textual units" around the target word.
-Setting "India" as the target word in the corpus of all paragraphs in *Natural History*, the `mclm::text_cooc()` function returns the frequency of words observed in the context of "India".
-As mentioned in the Methodology Section (@sec-method), the returned scores were filtered for those having PMI scores higher than 2 and signed $G^2$ scores higher than 3.84, in order to gain a strong and significant word list co-occurring with word "India" in the context.
+Textual collocation refers to the observation of some words frequently occurring with the target word in the context.
+Different from the surface collocation, which taking the collocating span, i.e.
+the certain words left and right to the target word into consideration [@evert2009], the word span in this case refers to the textual unit around the target word.
+Setting "India" as the target word in the corpus of all paragraphs in *Natural History*, the `mclm::text_cooc()` function returns the frequency of words appeared in the context of "India".
+As mentioned in the Methodology Section (@sec-method), the returned scores are filtered with a statistical criteria for gaining a list of the most frequently observed words in the context of word "India" with strong significance.
 
@@
 
-@tbl-coltable_Gsigned and @tbl-coltable_PMI display the top 20 collocates associated with the word "india" in the entire text, respectively sorted by G_signed and PMI scores.
-As the returned $G^2$ score helps gauge the strength of evidence regarding the independence between the two words [@montes2022], thereby facilitating the initial sorting.
+@tbl-coltable_absolute_freqencies, @tbl-coltable_Gsigned and @tbl-coltable_PMI display the top 20 contextual collocates associated with the word "india", respectively sorted by PMI, absolute frequency signed $G^2$ scores.
 
 ::: panel-tabset
+
 ### Sorted by absolute frequencies
@@
 
-### Sorted by G_singed
+### Sorted by Signed $G^2$
 
@@
 ```
+
 :::
 
-Similar to the results of keyword analysis, the top 20 sorted list of absolute frequency and G singed have a 11/20 overlapped outputs.
-As shown in @fig-col_colloc, the signed G score and absolute frequency in textual collocation has a positibe correlation.
+The top 20 ranking lists of absolute frequency and signed $G^2$ scores have a 11/20 overlapped outputs.
+As shown in @fig-col_colloc, the signed $G^2$ score and absolute frequency in textual collocation analysis shows a positive correlation.
 
@@
 #| label: fig-col_colloc
-#| fig-cap: Correlation of signed G and absolute frequency in textual collocation
+#| fig-cap: Scatter plot of signed $G^2$ scores and absolute frequency in textual collocation analysis
 
@@
 
-The high-ranking words of textual collocation with "India" in the work are cateforized as follows, those without specifying the association measurement are the overlapped ones:
+The high-ranking words in textual collocation with "India" sorted by absolute frequency and signed $G^2$ scores are categorized as follows, those without specifying the association measures ("A" stands for "absolute frequency" and "G" stands for "signed $G^2$ scores") are the overlapped ones.
+These words listed out comprises the strongest evidence of collocating with "India" in the context.
 
-**Geographical**: arabia, indian, ethiopia, ganges, indus(G)
+**Geographical connections**: *arabia*, *indian*, *ethiopia*, *ganges*, *indus*(G)
 
-**Numeric**: hundred, thousand(A), whole(A)
+**Animal/Plant**: *elephants*, *gum*(A), *lustre*(G)
 
-**Time**: year (A)
+**Precious Stone**: *stones*, *rock-crystal*, *gems*, *gem*(G), *gemstone*(G), *pearls*
 
-**Merchandise exchange**: mart(G)
+**Historical Figure**: *alexander*(A), *megasthenes*(G), *onesicritus*(G)
 
-**Precious Stone/Gem**: stones, rock-crystal, gems, pearls, gem(G), gemstone(G)
+**Merchandise exchange**: *mart*(G)
 
-**Animal/Plant**: elephants, gum(A), lustre(G)
+**Descriptive expression**: *hundred*, *thousand*(A), *whole*(A), *numerous*(A), *luxury*(A), *closely*(A), *valuable*(A), *bright*(A), *identical*(G), *smaragdus*(G)
 
-**Historical Figure**: alexander(A), megasthenes(G), onesicritus(G)
+**Others**: *shadow*(A), *year*(A)
 
-**Descriptive expression**: numerous(A), luxury(A), closely(A), valuable(A), bright(A), identical(G), smaragdus(G)
+These categories indicates that the narrative about "India" in *Natural History* covers three major dimensions.
+The first dimension is its geographical situation, including its connection to other places (mainly Arabia and Ethiopia), the two major rivers, Ganges and Indus within the region, and the animals, plants and precious stones originated in it.
+And it is often mentioned with historical figures, some related to the conquest history of the Roman Empire (in the case of *alexander*, referring to Alexander the Great, who had conducted several expeditions to Indian subcontinent), and some related to the referencing scholarship Pliny made his dialogue with.
+Moreover, the collocating word *mart* and the descriptive expressions highlights the merchandise exchanges introduced and discussed in the India-related content in the work.
 
-**Others**: shadow(A)
-
-The top 20 collocates associated with the word "India," sorted by their $G^2$ scores, reveal three key dimensions:
-
-1.
-**Geographical Connections**: The collocates such as *arabia*, *ethiopia*, *east*, *south*, *opposite*, and *beyond* indicate the geographical relationships and proximity between India and these regions.
-
-2.
-**Trading and Imports**: The presence of collocates like *imported*, *produces*, *produce* and *nations* suggests that India had a significant role in trade and the importation of goods.
-It also implies that India was known for producing various commodities that were sought after by other nations.
-
-3.
-**Boundaries and Borders**: The collocates *boundary*, *set* and *part* indicate the existence of defined boundaries or borders related to India.
-This suggests that there were recognized territorial demarcations associated with India during the referenced period.
+In the `mclm::text_cooc()` function, the given text will be separated as target context (text surrounding the target node) and reference context (text not surrounding the target node).
+As checked in the @tbl-colloc_freq_compare_AFG, not all words with both high absolute frequency and signed $G^2$ scores showing more frequency than that in the reference context.
 
 ```{r}
+#| label: tbl-colloc_freq_compare_AFG
+#| tbl-cap:  Frequency comparison of overlapping textual collocating words sorted by absolute frequency and signed $G^2$ score in the top 20 ranking in target and reference context
+
 coocs_ref_df <- as_tibble(coocs$ref_freqlist)
@@
 ) %>% 
+  arrange(desc(Target_Frequency)) %>% 
   kbl(col.names = c("Type", "Target_Frequency", "Reference_Abs_Frequency", "Reference_Nrm_Frequency")) %>% 
@@
 
+While in the top 20 list sorted with PMI scores, as shown in @tbl-colloc_frequency_compare_PMI, all of the results shows higher frequency than that in the reference context.
 ```{r}
+#| label: tbl-colloc_frequency_compare_PMI
+#| tbl-cap:  Frequency comparison of top 20 textual collocating words sorted by PMI score in target and reference context
 
@@
 ) %>% 
+  arrange(desc(Target_Frequency)) %>%
   kbl(col.names = c("Type", "Target_Frequency", "Reference_Abs_Frequency", "Reference_Nrm_Frequency")) %>% 
@@
 ```
+
+The PMI word list shows more descriptive information about the theme related to India in *Natural History*.
 

### 2023-08-25 paper_quarto.qmd
0825 keyword part update

@@
 engine: knitr
-title: "Keyword and Collocation analysis on India-related text of *Natural History*"
+title: "Collocation and keyword analysis on India-related text of *Natural History*"
 author: "Dawn, Lizao Zhuang (r0914937)"
@@
 *Natural History* stands as a seminal work in the history of encyclopedias, serving as a gateway to understanding the knowledge and worldview of ancient Rome.
-Beyond its role as a compendium of diverse subjects, the text provides a captivating glimpse into the knowledge, cultural, and merchandise exchange [@dodd2021] between the Roman Empire and other regions [@plinyth2011].
+Beyond its role as a compendium of diverse subjects, the text provides a captivating glimpse into the knowledge, cultural, and merchandize exchange [@dodd2021] between the Roman Empire and other regions [@plinyth2011].
 
@@
 
-Since a PMI score higher than two indicates a four times higher probability of association, and a signed $G^2$ score higher than 3.84 indicates a significant association at a 95% confidence level [@montes2022], a filter of "PMI \>= 2 & G_signed \>= 3.84" is applied for the returned objects of `mclm::assoc_scores` for both of the methods, in order to gain strong and significant association outputs for further discussion.
+Since a PMI score higher than two indicates a four times higher probability of association, and a signed $G^2$ score higher than 3.84 indicates a significant association at a 95% confidence level [@montes2022], a filter of "PMI \>= 2 & signed $G^2$ \>= 3.84" is applied for the returned objects of `mclm::assoc_scores` for both of the methods, in order to gain strong and significant association outputs for further discussion.
 
@@
 
-@tbl-coltable_absolute_freqencies, @tbl-coltable_Gsigned and @tbl-coltable_PMI display the top 20 contextual collocates associated with the word "india", respectively sorted by PMI, absolute frequency signed $G^2$ scores.
+@tbl-coltable_absolute_freqencies, @tbl-coltable_Gsigned and @tbl-coltable_PMI display the top 20 contextual collocates associated with the word "india", respectively sorted by absolute frequency, signed $G^2$ scores and PMI scores.
 
@@
 #| tbl-cap-location: top
-#| tbl-cap: Top 20 collocates to the word "india" in Natural History (sorted by G_signed)
+#| tbl-cap: Top 20 collocates to the word "india" in Natural History (sorted by absolute freqencies)
 #| warning: false
@@
 #| tbl-cap-location: top
-#| tbl-cap: Top 20 collocates to the word "india" in Natural History (sorted by G_signed)
+#| tbl-cap: Top 20 collocates to the word "india" in Natural History (sorted by signed $G^2$)
 #| warning: false
@@
 #| label: fig-col_colloc
-#| fig-cap: Scatter plot of signed $G^2$ scores and absolute frequency in textual collocation analysis
+#| fig-cap: Scatter plot of signed $G^2$ scores by absolute frequency in textual collocation analysis
 
@@
 
+theme_set(theme_minimal(base_size = 15))
 g1 <- top_scores_colloc_df %>%
   ggplot(aes(x = G_signed, y = a)) +
-  labs(x = "signed G", y = "Absolute frequency") +
+  labs(x = "signed $G^2$", y = "Absolute frequency") +
   geom_point() +
@@
 
-**Precious Stone**: *stones*, *rock-crystal*, *gems*, *gem*(G), *gemstone*(G), *pearls*
+**Precious stone**: *stones*, *rock-crystal*, *gems*, *gem*(G), *gemstone*(G), *pearls*
 
-**Historical Figure**: *alexander*(A), *megasthenes*(G), *onesicritus*(G)
+**Historical figure**: *alexander*(A), *megasthenes*(G), *onesicritus*(G)
 
-**Merchandise exchange**: *mart*(G)
+**Merchandize exchange**: *mart*(G)
 
@@
 And it is often mentioned with historical figures, some related to the conquest history of the Roman Empire (in the case of *alexander*, referring to Alexander the Great, who had conducted several expeditions to Indian subcontinent), and some related to the referencing scholarship Pliny made his dialogue with.
-Moreover, the collocating word *mart* and the descriptive expressions highlights the merchandise exchanges introduced and discussed in the India-related content in the work.
+Moreover, the collocating word *mart* and the descriptive expressions highlights the merchandize exchanges introduced and discussed in the India-related content in the work.
 
 In the `mclm::text_cooc()` function, the given text will be separated as target context (text surrounding the target node) and reference context (text not surrounding the target node).
-As checked in the @tbl-colloc_freq_compare_AFG, not all words with both high absolute frequency and signed $G^2$ scores showing more frequency than that in the reference context.
+The normalized frequency of the top ranking words with the highest frequency and strongest evidence in the target context are at least 20 times higher than that of the reference context, as shown in @tbl-colloc_freq_compare_AFG.
 
@@
 coocs_ref_df <- as_tibble(coocs$ref_freqlist)
+coocs_tar_df <- as_tibble(coocs$target_freqlist)
+
 words_to_check_colloc <- c("arabia", "indian", "ethiopia", "ganges", "rock-crystal", "hundred", "elephants", "megasthenes", "indians", "gem", "lustre", "stones", "identical", "'smaragdus", "indus", "gems", "gemstone", "pearls", "onesicritus", "mart")
-filtered_top_scores_colloc <- top_scores_colloc_df %>%
+
+filtered_top_scores_colloc <- coocs_tar_df %>%
   filter(type %in% words_to_check_colloc)
 
-abs_freq_lookup1 <- setNames(coocs_ref_df$abs_freq, coocs_ref_df$type)
+tar_nrm_freq_lookup1 <- setNames(coocs_tar_df$nrm_freq, coocs_tar_df$type)
 nrm_freq_lookup1 <- setNames(coocs_ref_df$nrm_freq, coocs_ref_df$type)
@@
   Word = filtered_top_scores_colloc$type,
-  Target_Frequency = filtered_top_scores_colloc$a,
-  Reference_Abs_Frequency = abs_freq_lookup1[filtered_top_scores_colloc$type],
+  Target_Nrm_Frequency = tar_nrm_freq_lookup1[filtered_top_scores_colloc$type],
   Reference_Nrm_Frequency = nrm_freq_lookup1[filtered_top_scores_colloc$type]
 ) %>% 
-  arrange(desc(Target_Frequency)) %>% 
-  kbl(col.names = c("Type", "Target_Frequency", "Reference_Abs_Frequency", "Reference_Nrm_Frequency")) %>% 
+  arrange(desc(Target_Nrm_Frequency)) %>% 
+  kbl(col.names = c("Type", "Target_Nrm_Frequency", "Reference_Nrm_Frequency")) %>% 
   kable_minimal() %>% 
@@
 
-While in the top 20 list sorted with PMI scores, as shown in @tbl-colloc_frequency_compare_PMI, all of the results shows higher frequency than that in the reference context.
+When checking about the normalized frequency of the top 20 list sorted with PMI scores, as shown in @tbl-colloc_frequency_compare_PMI, all of the results show higher frequency than that in the reference context as well.
 ```{r}
@@
 
-words_to_check_colloc_pmi <- c(
-  "megasthenes",
-  "thorn-bush",
-  "carnelian",
-  "obsidian",
-  "cophes",
-  "merchandize",
-  "mart",
-  "expeditions",
-  "patala",
-  "arii",
-  "ichthyophagi",
-  "pursuits",
-  "vermilion",
-  "biggest",
-  "onesicritus",
-  "identical",
-  "ganges",
-  "engrave",
-  "'smaragdus",
-  "honey-coloured",
-  "reflects"
+words_to_check_colloc_pmi <- c("megasthenes", "thorn-bush", "carnelian", "obsidian", "cophes", "merchandize", "mart", "expeditions", "patala",   "arii", "ichthyophagi", "pursuits", "vermilion", "biggest", "onesicritus", "identical", "ganges", "engrave", "'smaragdus", "honey-coloured",   "reflects"
 )
 
-filtered_top_scores_colloc <- top_scores_colloc_df %>%
+filtered_top_scores_colloc_pmi <- coocs_tar_df %>%
   filter(type %in% words_to_check_colloc_pmi)
 
-abs_freq_lookup1 <- setNames(coocs_ref_df$abs_freq, coocs_ref_df$type)
-nrm_freq_lookup1 <- setNames(coocs_ref_df$nrm_freq, coocs_ref_df$type)
-
 results_colloc_pmi <- tibble(
-  Word = filtered_top_scores_colloc$type,
-  Target_Frequency = filtered_top_scores_colloc$a,
-  Reference_Abs_Frequency = abs_freq_lookup1[filtered_top_scores_colloc$type],
-  Reference_Nrm_Frequency = nrm_freq_lookup1[filtered_top_scores_colloc$type]
+  Word = filtered_top_scores_colloc_pmi$type,
+  Target_Nrm_Frequency = tar_nrm_freq_lookup1[filtered_top_scores_colloc_pmi$type],
+  Reference_Nrm_Frequency = nrm_freq_lookup1[filtered_top_scores_colloc_pmi$type]
 ) %>% 
-  arrange(desc(Target_Frequency)) %>%
-  kbl(col.names = c("Type", "Target_Frequency", "Reference_Abs_Frequency", "Reference_Nrm_Frequency")) %>% 
+  arrange(desc(Target_Nrm_Frequency)) %>%
+  kbl(col.names = c("Type", "Target_Nrm_Frequency", "Reference_Nrm_Frequency")) %>% 
   kable_minimal() %>% 
@@
 results_colloc_pmi
+
 ```
 
-The PMI word list shows more descriptive information about the theme related to India in *Natural History*.
+The PMI word list, indicating the words with relatively strongest attraction to the word "India" in the context, shows more descriptive information about the theme related to India in *Natural History*.
+Most of them can be classified to the categories set for the overlapping high ranking absolute frequency and signed $G^2$ scores, and some words contribute to a new category relating to the exsisting categories, as shown in the classification as follows:
 
-Within the context of Pliny the Elder's *Natural History* is a book with an encyclopedia scope written in Roman Empire, these collocates suggest the interconnecting role India played in the network of interactions, trade, or cultural exchanges between India and the Mediterranean regions during 1st century AD.
-They highlight India's significance as a trading partner, its geographical positioning, and the recognition of its territorial boundaries.
+**Geographical connections**: *cophes*, *patala*, *ganges*
+
+**Animal/Plant**: *thorn-bush*
+
+**Precious stone**: *carnelian*, *obsidian*, *'smaragdus*
+
+**Historical figure**: *megasthenes*, *onesicritus*
+
+**Merchandize exchange**: *merchandize*, *mart*
+
+**Descriptive expression**: *vermilion*, *biggest*, *identical*, *honey-coloured*
+
+**Others**: *reflects*
+
+**Activity (new category)**: *expeditions*, *pursuits*, *engrave*
+
+**Ethnic group (new category)**: *arii*, *ichthyophagi*
+
+Except for showing more specified geographical connections, plants and gemstone names, the descriptive expressions in the list relates to the description of stones, and the special traits of natural creatures originated in India in *Natural History*.
+The words of the new categories relates to the existing categories.
+For example, the words of activity relates to the Indian-subcontinent expedition of Alexander the Great, the need for merchandize exchange, and the product processing of gemstones, and the words of ethnic group relates to the geographical introduction about Indian and its connected regions, which reinforced the previous conclusion, that the context of "India" in the work shows focuses on the geographical introduction about India and the trade relation between it and the Roman Empire.
+
+Combining the observation of the three top ranking word lists of textual collocation to word "Inida" in *Natural History*, these collocates suggest the interconnecting role India played in the network of interactions, trade, and cultural exchanges in the narrative.
 
@@
 
-As mentioned, the method of keyword analysis could help with a further discuss about the prominent theme and topic in the India-related texts.
+Additionally, in order to examine the significant phrases, i.e.
+"keyword", in the India-related content in the work, as a comparison and supplement to the conclusion of textual collocation analysis, a keyword analysis is employed for the India-related text.
 
 The frequency lists for the **target corpus** (India-related texts) and **reference corpus** (whole text) are generated respectively, and the association scores are calculated through the `mclm::assoc_scores()` function.
-The association score is filtered based on the criteria of both PMI and $G^2$ scores, requiring a minimum score of 2.
-This criterion ensures that the selected words have a probability at least four times higher than the overall data, along with statistically significant supporting evidence [@montes2022], allowing to identify the most statistically significant keywords in India-related texts when compared to the reference corpus.
-
-During the calculation of word frequencies in the **target corpus**, the specific word "India" itself was excluded from the analysis.
-This exclusion was intentional, aiming to focus on more descriptive words within the corpus and efficiently identify potential thematic keywords in the **target corpus**.
+Similar to the collocation analysis, the returned scores are filtered with a criterion of PMI >= 2 and signed $G^2$ >= 3.84, to ensure the selected words for further discussion have a strong attraction to the target corpus with statistical significance [@montes2022].
 
@@
 The following tables present the top 20 keywords in India-related texts as compared to the entire texts in *Natural History*.
-They are sorted based on their PMI (@tbl-kwtable_PMI), Absolute frequencies (@tbl-kwtable_absolute_freqencies) and G_signed scores (@tbl-kwtable_Gsigned), respectively.
-The initial sorting was carried out based on the PMI scores (@tbl-kwtable_PMI), since the it serves as a crucial indicator for measuring the keyness of words.
+They are sorted based on their absolute frequencies (@tbl-kwtable_absolute_freqencies), signed $G^2$ scores (@tbl-kwtable_Gsigned) and PMI scores (@tbl-kwtable_PMI) respectively.
 
@@
 ```{r}
-#| warning: false
-#| echo: false
 #| label: tbl-kwtable_absolute_freqencies
-#| tbl-cap-location: top
 #| tbl-cap: Top 20 Keywords on Indian Related Text in Natural History (sorted by PMI)
@@
 
-### Sorted by PMI
+### Sorted by signed $G^2$
 
@@
 #| echo: false
+#| label: tbl-kwtable_Gsigned
+#| tbl-cap-location: top
+#| tbl-cap: Top 20 Keywords on Indian Related Text in Natural History (sorted by signed $G^2$)
+
+top_scores_kw %>% # also valid for top_scores_colloc
+  as_tibble() %>%
+  select(type, a, PMI, G_signed) %>%         # sort by PMI (descending) 
+  slice_max(order_by = G_signed, n = 20, with_ties = TRUE) %>%   
+  kbl(col.names = c("Type", "Frequency", "PMI", r"(Signed $G^2$)")) %>% 
+  kable_minimal() %>% 
+  scroll_box(height = "400px")
+```
+
+### Sorted by PMI
+
+```{r}
 #| label: tbl-kwtable_PMI
-#| tbl-cap-location: top
 #| tbl-cap: Top 20 Keywords on Indian Related Text in Natural History (sorted by PMI)
@@
 ```
-
-### Sorted by G_signed
-
-```{r}
-#| warning: false
-#| echo: false
-#| label: tbl-kwtable_Gsigned
-#| tbl-cap-location: top
-#| tbl-cap: Top 20 Keywords on Indian Related Text in Natural History (sorted by G_Signed)
-
-top_scores_kw %>% # also valid for top_scores_colloc
-  as_tibble() %>%
-  select(type, a, PMI, G_signed) %>%         # sort by PMI (descending) 
-  slice_max(order_by = G_signed, n = 20, with_ties = TRUE) %>%   
-  kbl(col.names = c("Type", "Frequency", "PMI", r"(Signed $G^2$)")) %>% 
-  kable_minimal() %>% 
-  scroll_box(height = "400px")
-```
 :::
 
-In the list of three measurements, 16/20 of absolute frequency overlaps with that of $G^2$ Signed.
-As shown in the @fig-col_keyword, the $G^2$ score has a positive correlation with the absolute frequency.
+Among the three lists sorting by different measurements, 16/20 words of absolute frequency top ranking list overlaps with that of the signed $G^2$ scores.
+As shown in the @fig-col_keyword, the signed $G^2$ score has a positive correlation with the absolute frequency in this case.
 
@@
 #| label: fig-col_keyword
-#| fig-cap: Scatterplot of G_signed by absolute frequency
+#| fig-cap: Scatter plot of signed $G^2$ scores by absolute frequency in keyword analysis
 
@@
   ggplot(aes(x = G_signed, y = a)) +
-  labs(x = "Signed G", y = "Absolute frequency")
-g + geom_point()
+  labs(x = "signed $G^2$", y = "Absolute frequency") +
+  geom_point() +
+  geom_smooth(method = "lm", se = FALSE)
+
+g 
 ```
 
-Combing the lists sorted by absolute frequency and signed G, it can be categorized as follows (those without specified are the overlapped words):
+Combing the top ranking keyword lists sorted by absolute frequency and signed $G^2$ scores, it can be classified into categories similar to that in the previous collocation analysis.
+In the categorized groups below, those without specifying the association measures ("A" stands for "absolute frequency" and "G" stands for "signed $G^2$ scores") are the overlapped ones.
 
-**Geographical**: india, arabia, indian, ganges, indus, ethiopia, taprobane(G), thence, sail(A)
-
-**People**: alexander, indians, tribe(A), ichthyophagi(G), megasthenes(G)
-
-**Numeric**: hundred, thousand, fifty(A)
-
-**Precious Stone/Gem**: stones, amber, rock-crystal, glass, beryls(G)
+**Geographical connections**: india, arabia, indian, ganges, indus, ethiopia, taprobane(G), thence, sail(A)
 
@@
 
-The categories partly highlights the potential themes in the target corpus, i.e.
-India-related text in *Natural History*, that a lot of geographical details, including land marks, locations and spatial transportation, as well as precious stones and introduction about tribes, historical figures and animal and plants.
+**Precious stone**: stones, amber, rock-crystal, glass, beryls(G)
 
-It aligns with the general structure of the work, that catelouging the natural, material world in to chapters of geography, anthropology, natural creatures and mineralogy.
+**Historical figure**: alexander, ichthyophagi(G), megasthenes(G)
 
-And the high ranking words even have more appearences in the reference corpus, as shown in @tbl-kw_frequency_compare.
+**Ethnic group**: indians, tribe(A)
+
+**Descriptive expression (numeric)**: hundred, thousand, fifty(A)
+
+The words in each group partly overlaps with the results in collocation analysis, which on the one hand confirms the potential themes in the India-related content as concluded previously, and on the other hand, suggests that the high evidence ranking textual collocates of "India" also possibly serve as the keywords in the target corpus.
+
+In the comparison of normalized frequency of these words in the target and reference corpra, they all show notably higer frequencies in the target corpus, as shown in @tbl-kw_frequency_compare.
 
@@
 flist_ref_df <- as_tibble(flist_ref)
+flist_target_df <- as_tibble(flist_target)
+
 words_to_check <- c("india", "hundred", "stones", "arabia", "indian", "alexander",
@@
 
-filtered_top_scores <- top_scores_kw_df %>%
+filtered_top_scores <- flist_target_df %>%
   filter(type %in% words_to_check)
 
-abs_freq_lookup <- setNames(flist_ref_df$abs_freq, flist_ref_df$type)
+tar_nrm_freq_lookup <- setNames(flist_target_df$nrm_freq, flist_target_df$type)
+
 nrm_freq_lookup <- setNames(flist_ref_df$nrm_freq, flist_ref_df$type)
@@
   Word = filtered_top_scores$type,
-  Target_Frequency = filtered_top_scores$a,
-  Reference_Abs_Frequency = abs_freq_lookup[filtered_top_scores$type],
+  Target_Nrm_Frequency = tar_nrm_freq_lookup[filtered_top_scores$type],
   Reference_Nrm_Frequency = nrm_freq_lookup[filtered_top_scores$type]
 ) %>% 
-  kbl(col.names = c("Type", "Target_Frequency", "Reference_Abs_Frequency", "Reference_Nrm_Frequency")) %>% 
+  arrange(desc(Target_Nrm_Frequency)) %>%
+  kbl(col.names = c("Type", "Target_Nrm_Frequency", "Reference_Nrm_Frequency")) %>% 
   kable_minimal() %>% 
@@
 
-As PMI score indicates times of probability of the keyword in the target context higher than its probability in all the data taken together, it could serve as a more convincing indicator for the analysis of keywords.
-And in fact, in the sorted top 20 list of PMI, it does showed more detailed information about the context.
-Moreover, almost all of them shown none frequency in the reference corpus, which reinforces the indication that they are distinctly key to the target corpus comparing to that of the other context of the work, as shown in @tbl-kw_frequency_pmi.
+Furthermore, as PMI score indicates the times of probability of the selected keyword occur in the target corpus higher than that in the reference corpus, it could serve as a more convincing indicator for the analysis of keywords.
+
+When checking about the normalized frequency of the top 20 keywords with the most PMI score, as shown in @tbl-kw_frequency_pmi, almost all of them are seem distinct in the India-related text, which reinforces the indication that they are especially key to the target corpus comparing to the other parts of the work.
 
@@
 
-filtered_top_scores1 <- top_scores_kw_df %>%
+filtered_top_scores_pmi <- top_scores_kw_df %>%
   filter(type %in% words_to_check_pmi)
 
-abs_freq_lookup1 <- setNames(flist_ref_df$abs_freq, flist_ref_df$type)
-nrm_freq_lookup1 <- setNames(flist_ref_df$nrm_freq, flist_ref_df$type)
-
 results1 <- tibble(
-  Word = filtered_top_scores1$type,
-  Target_Frequency = filtered_top_scores1$a,
-  Reference_Abs_Frequency = abs_freq_lookup1[filtered_top_scores1$type],
-  Reference_Nrm_Frequency = nrm_freq_lookup1[filtered_top_scores1$type]
+  Word = filtered_top_scores_pmi$type,
+  Target_Nrm_Frequency = tar_nrm_freq_lookup[filtered_top_scores_pmi$type],
+  Reference_Nrm_Frequency = nrm_freq_lookup[filtered_top_scores_pmi$type]
 )%>% 
-  kbl(col.names = c("Type", "Target_Frequency", "Reference_Abs_Frequency", "Reference_Nrm_Frequency")) %>% 
+  arrange(desc(Target_Nrm_Frequency)) %>%
+  kbl(col.names = c("Type", "Target_Nrm_Frequency", "Reference_Nrm_Frequency")) %>% 
   kable_minimal() %>% 
@@
 
-From these keywords, a manual examination was performed to determine their meaning and assign appropriate tags as based on their category.
-The resulting explanations for the top 20 keywords, sorted by PMI, can be found in @tbl-kwlist below.
+For these keywords, a manual examination was performed to determine their meaning and assign classification tags based on their category.
+The explanations for the top 20 keywords with the highest PMI scores is displayed in @tbl-kwlist below.
 
 ```{r}
-#| warning: false
-#| echo: false
 #| label: tbl-kwlist
 #| tbl-cap: Top 20 keywords with meaning sorted by PMI
-#| tbl-cap-location: top
 
@@
 The presence of keywords such as *beryls*, *obsidian*, *bdellium*, *agates*, *callaina*, *prasii*, *carnelian* and *sandastros* indicates the involvement of various gemstones and goods associated with India.
-These findings are complemented by the presence of keywords like *condensation*, *merchandize* and *peppertree* which suggest the production and trade of goods between the Roman Empire and the Indian regions during that era.
+These findings are complemented by the presence of keywords like *condensation*, *merchandize* and *pepper tree* which suggest the production and trade of goods between the Roman Empire and the Indian regions during that era.
 

### 2023-08-25 freqlist_location.R
0825 minor fix

@@ -134,6 +134,7 @@ ggplot(tag_counts, aes(x = n, y = reorder(Tag, -n), fill = Tag)) +
   coord_flip()
 
 flist_ref_df <- as_tibble(flist_ref)
+flist_target_df <- as_tibble(flist_target)
 words_to_check <- c("ganges", "beryls", "ichthyophagi", "megasthenes", "obsidian", "bdellium", "agates", "callaina", "condensation", "gerra", "jomanes", "nonius", "prasii", "alia", "carnelian", "cophes", "hypasis", "merchandize", "peppertree", "sacae", "sandastros", "thornbush")
 words_to_check1<- c("india", "hundred", "stones", "arabia", "indian", "alexander",
                     "amber", "thousand", "elephants", "indus", "glass", "thence",

### 2023-08-26 paper_quarto.qmd
0826 update introduction

@@
 
-# Research Question[^1]
+# Introduction[^1]
 
@@
 
-Building upon this observation, the study focus is narrowed down to India-related text in *Natural History*.
-By delving deeper into the themes associated with the Indian region referred in the text, this study aims to examine the portrayal of India by Pliny the Elder, which potentially shed a light on the spatial perception and imagination of the representative writers and scholars of ancient Rome.
+Building upon this observation, the study focus is narrowed down to India-related text in *Natural History* to investigate what and how is India described in the work.
+By delving into the themes associated with Indian region with the methods of collocation and keyword analysis, this study aims to examine the portrayal of India by Pliny the Elder, which potentially shed a light on the spatial perception and imagination of the representative writers and scholars of ancient Rome.
+
+The subsequent sections provide detailed explanation of the methodology and corpus employed, interpretation and discussion of the results of the collocation and keyword analysis, and an overall conclusion responding to the captioned research questions.
 

### 2023-08-27 paper_quarto.qmd
0827 proofread

--- 2023-08-25 paper_quarto.qmd
@@
 csl: unified-style-sheet-for-linguistics.csl
-abstract: 'This paper presents a comprehensive analysis of keywords and collocates related to India in a corpus of Natural History by Pliny the Elder.
-The study focuses on uncovering prominent themes and topics associated with India in the context of the book.
-The research employs collocate examination techniques and keyword analysis to reveal significant insights into the perception and imagination of India, as a competent counterpart to the Roman Empire, by Pliny the Elder and the scholars of his time.'
+abstract: 'This paper presents a comprehensive analysis of textual collocations and keywords related to "India" in a corpus of *Natural History*, the earliest known encyclopedia written by Pliny the Elder in the 1st century AD.
+By analyzing these word associations and significant terms, this study seeks to identify the main themes and topics related to the Indian region within the text.
+This will shed light on how Pliny depicts and imagines this geographical area, providing insights into the spatial representation and imagination in the work.'
 ---
@@
 Written around AD 77, the work is thematically divided into 37 books, covering a diverse range of subjects including astronomy, geography, zoology, botany, medicine, and more.
-Driven by a pioneering attempt to catalog human knowledge from his era, Pliny made a comprehensive reference to a wide range of Greek and Roman scholarships, and interwove his own literary interpretation or comments to the narratives in *Natural History*.
+Driven by a pioneering attempt to catalog all human knowledge from his era, Pliny made a comprehensive reference to a wide range of Greek and Roman scholarships, and interwove his own literary interpretation or comments to the narratives in the work.
 
@@
 
-[^2]: The scraping [code](https://github.com/lizaodawn/zhuang/blob/papertry/Natural%20History_corpus.ipynb) is uploaded to the same repository of the project.
+[^2]: The scraping code is uploaded to the same repository of the paper.
 
@@
 #| fig-cap: Mapping of geographical names mentioned in *Natural History*
-#| fig-cap-location: top
-#| warning: false
-#| echo: false
 
@@
 
-Building upon this observation, the study focus is narrowed down to India-related text in *Natural History*.
-By delving deeper into the themes associated with the Indian region referred in the text, this study aims to examine the portrayal of India by Pliny the Elder, which potentially shed a light on the spatial perception and imagination of the representative writers and scholars of ancient Rome.
+Based on this observation, the focus of the study is narrowed down to India-related texts in the *Natural History* to investigate what and how India is described in the work.
+By delving into the themes associated with the Indian region using the methods of collocation and keyword analysis, this study aims to examine Pliny the Elder's portrayal of India, which may shed light on the spatial perception and imagination of the representative writers and scholars of ancient Rome.
+
+The following sections provide a detailed explanation of the methodology and corpus used, an interpretation and discussion of the results of the collocation and keyword analysis, and an overall conclusion in response to the research questions.
 
@@
 To investigate the prominent themes in the India-related content discussed in *Natural History*, the study generally employs methods of collocation analysis and keyword analysis in corpus linguistics, and is conducted in R environment [@R-base].
-The discussions are based on the `mclm::assoc_scores` objects returned from [mclm](https://masterclm.github.io/mclm/) [@R-mclm] package.
-In addition, [tidyverse](https://www.tidyverse.org/) [@R-tidyverse] and [leaflet](https://rstudio.github.io/leaflet/) [@R-leaflet] packages are used for data manipulation and visualization.
+The discussions are based on the `mclm::assoc_scores` objects returned with [mclm](https://masterclm.github.io/mclm/) [@R-mclm] package.
+In addition, [tidyverse](https://www.tidyverse.org/) [@R-tidyverse], [leaflet](https://rstudio.github.io/leaflet/) [@R-leaflet] and [kableExtra](http://haozhu233.github.io/kableExtra/) [@R-kableExtra] packages are used for data manipulation and visualization.
 
-In the Data Analysis section (@sec-data_analysis), both of the collocation and keyword analysis are examined by three association measures, namely absolute frequency, PMI and signed $G^2$ for discussing the potential theme it inferred integrating with a close reading of the context.
+In the Data Analysis section (@sec-data_analysis), both of the collocation and keyword analysis are examined using three measures of association, namely absolute frequency, PMI and signed $G^2$ to discuss the potential theme it inferred with an integration of a close reading of the text.
 
 Absolute frequency refers to the simple count of each single type (distinct word) observed in the text.
-In the case of collocation analysis, it shows the time a type collocates with the target word.
-While in the case of keyword analysis, it shows the time a type occurs in the target corpus.
-As a basic counting measure, absolute frequency provide an overview of the word distribution with limited insights.
+In the case of collocation analysis, it shows how often a type collocates with the target word.
+While in the case of keyword analysis, it shows how often a type occurs in the target corpus.
+As a basic counting measure, absolute frequency provide an general view of the word distribution.
 
@@
 
-Since a PMI score higher than two indicates a four times higher probability of association, and a signed $G^2$ score higher than 3.84 indicates a significant association at a 95% confidence level [@montes2022], a filter of "PMI \>= 2 & signed $G^2$ \>= 3.84" is applied for the returned objects of `mclm::assoc_scores` for both of the methods, in order to gain strong and significant association outputs for further discussion.
+Since a PMI score higher than two indicates a four times higher probability of association, and a signed $G^2$ score higher than 3.84 indicates a significant association at a 95% confidence level [@montes2022], a filter of "PMI \>= 2 & signed $G^2$ \>= 3.84" is applied to the returned objects of `mclm::assoc_scores` for both methods to obtain strong and significant association results for further discussion.
 
@@
 
-Collocation analysis is a technique employed in corpus linguistics to identify words that often appear together in a given text.
-This technique is rooted in the notion that particular words tend to appear together more often than they would occur by chance.
+Collocation analysis is a technique used in corpus linguistics to identify words that frequently occur together in a given text.
+This technique is based on the idea that certain words tend to occur together more often than they would by chance.
 
-In this study, the textual collocating word with "India" in *Natural History* is examined.
-Lists of highly frequent co-occurring word with "India" in the context are obtained and sorted by scores of different measurements.
-The potential theme of India-related content in the work can be discussed based on the output of textual collocation of word "India".
+This study examines the textual co-occurrence of the word "India" in *Natural History*.
+Lists of highly frequent words co-occurring with "India" in context are obtained and sorted by scores of different measures.
+The potential themes of India-related content in the work can be discussed based on the outputs of textual collocation of word "India".
 
@@
 Keyword analysis is a statistical method used in corpus linguistics to identify words that occur more frequently in a target corpus than in a reference corpus.
-The words showing higher association with the target corpus comparing to its frequency in the reference corpus are seen as the "keyword" of the target corpus.
+The words that have a higher association with the target corpus compared to their frequency in the reference corpus are considered to be the "keyword" of the target corpus.
 
-In this study, the **target corpus** includes all paragraphs in *Natural History* mentioning place names in Indian regions, and the **reference corpus** contains all other paragraphs in the work.
-Lists of words with relatively higher frequency in the target corpus are obtained and sorted by scores of different measurements.
-The "keywords" found in India-related text in *Natural History* provides more descriptive information about the topics and elements related to "India" in Pliny's narrative.
+In this study, the **target corpus** includes all paragraphs in *Natural History* that mention place names in Indian regions, and the **reference corpus** includes all other paragraphs in the work.
+Lists of words with relatively higher frequency in the target corpus are obtained and sorted by the results of different measurements.
+The "keywords" found in the India-related text in *Natural History* provide more descriptive information about the topics and elements related to "India" in Pliny's narrative.
 
-Combining the two methods, and integrating with a close reading of the text, this study aims to gain insights about how "India" is discussed and portrayed in *Natural History*.
+By combining the two methods and integrating them with a close reading of the text, this study aims to gain insights into how "India" is discussed and represented in *Natural History*.
 
@@
 The digitized text is available in paragraphs with geographical annotations on TOPOSText website as two parts, [book 1-11](https://topostext.org/work/148) and [book 12-37](https://topostext.org/work/153), both of which are in HTML format.
-Extracting all "place" class in the HTML files, information of all annotated place names in the work, the URI and corresponding coordinates of the place, the book/chapter/paragraph number where it is mentioned, as well as the coordinating textual content is structured as a dataset of geographical-related text in *Natural History*.
-This dataset is used for an initial exploration of the prominent mentioned places in the text.
+Extracting all "place" classes in the HTML files, information of all annotated place names in the work, the URI and corresponding coordinates of the place, the book/chapter/paragraph number where it is mentioned, as well as the coordinating textual content is structured as a dataset of geographical-related text in *Natural History*.
+This dataset is used for an initial exploration of the prominent places mentioned in the text.
 
-The initial obeservation shown in @fig-top20geoname and @fig-geonamemap leads to a focus to the India-related text for this study.
+The initial observation shown in @fig-top20geoname and @fig-geonamemap leads to a focus on the India-related text for this study.
 With a reference to *Barrington Atlas of the Greek and Roman World* [@talbert2000; @talbert2000-1], the approximate geographical coordinates defining the Indian region during the time of *Natural Hisoty* are as follows[^3]:
@@
 
-The records in geographical-related text dataset with corresponding coordinates falling within the specified range are extracted as the India-related text dataset.
+The records in geographical-related text dataset with corresponding coordinates that fall within the specified range are extracted as the India-related text dataset.
 
@@
 #| label: prepare-corpus
-#| warning: false
 
@@
 The file names contain information about the book, chapter, and paragraph number of the text.
+This **target corpus** contains `r prettyNum(n_tokens(flist_target))` tokens and `r n_types(flist_target)` types, with the type-token ratio of `r round(n_types(flist_target)/n_tokens(flist_target), 2)`.
 
 And the full text of the entire work, separated in paragraphs, are also scraped and stored in TXT format.
-Excluding those in **target corpus**, the other part of the work, containing `r length(fnames_wholetext_filtered)` files, serve as a **reference corpus**.
+Excluding those in target corpus, the other part of the work, containing `r length(fnames_wholetext_filtered)` files, serve as a **reference corpus**.
+The **reference corpus** contains `r prettyNum(n_tokens(flist_ref))` tokens and `r n_types(flist_ref)` types, with the type-token ratio of `r round(n_types(flist_ref)/n_tokens(flist_ref), 2)`.
 
-The text are set into lower case in the corpus file extraction process.
-
-The **target corpus** consists of all text related to India in paragraphs, containing `r prettyNum(n_tokens(flist_target))` tokens and `r n_types(flist_target)` types, with the type-token ratio of `r round(n_types(flist_target)/n_tokens(flist_target), 2)`.
-
-And the **reference corpus** consists of all texts in *Natural History* in paragraphs, consisting of `r prettyNum(n_tokens(flist_ref))` tokens and `r n_types(flist_ref)` types, with the type-token ratio of `r round(n_types(flist_ref)/n_tokens(flist_ref), 2)`.
+During the extraction process of the corpus files, the texts are already converted to lower case.
 
@@
 
+Collocation analysis traces the frequent occurrence of certain words or phrases in close proximity to each other within a given context.
+Unlike surface collocation, which considers the collocating span, i.e., the specific words to the left and right of the target word [@evert2009], the span in textual collocation refers to the textual unit around the target word.
+Setting "India" as the target word for tracing in the corpus of all paragraphs in *Natural History*, the `mclm::text_cooc()` function returns the frequency of words appearing in the context of "India".
+As mentioned in the Methodology section (@sec-method), the returned results are filtered with a statistical criterion to obtain a list of the most frequently collocated words with the word "India" with strong evidence.
+
+The prominent textual collocates of "India" identified with this approach suggest the potential themes about the Indian region in the narrative of Pliny.
+
 ```{r}
-#| label: collocation
-#| warning: false
-
 coocs <- fnames_wholetext %>% 
@@
 
-# calculate scores
 scores_colloc <- assoc_scores(coocs)
@@
 
-@tbl-coltable_absolute_freqencies, @tbl-coltable_Gsigned and @tbl-coltable_PMI display the top 20 contextual collocates associated with the word "india", respectively sorted by absolute frequency, signed $G^2$ scores and PMI scores.
+@tbl-coltable_absolute_freqency, @tbl-coltable_Gsigned and @tbl-coltable_PMI show the top 20 textual collocates associated with the word "India", sorted by absolute frequency, signed $G^2$ and PMI scores in decsending order.
 
 ::: panel-tabset
-
-### Sorted by absolute frequencies
+### Sorted by absolute frequency
 
 ```{r}
-#| label: tbl-coltable_absolute_freqencies
-#| tbl-cap-location: top
-#| tbl-cap: Top 20 collocates to the word "india" in Natural History (sorted by absolute freqencies)
-#| warning: false
-#| echo: false
+#| label: tbl-coltable_absolute_freqency
+#| tbl-cap: Top 20 collocates to the word "India" in *Natural History* (sorted by absolute freqency)
+
 top_scores_colloc %>% 
@@
 #| label: tbl-coltable_Gsigned
-#| tbl-cap-location: top
-#| tbl-cap: Top 20 collocates to the word "india" in Natural History (sorted by signed $G^2$)
-#| warning: false
-#| echo: false
+#| tbl-cap: Top 20 collocates to the word "India" in *Natural History* (sorted by signed $G^2$)
+
 top_scores_colloc %>% 
@@
 #| label: tbl-coltable_PMI
-#| tbl-cap-location: top
-#| tbl-cap: Top 20 collocates to the word "india" in Natural History (sorted by PMI)
+#| tbl-cap: Top 20 collocates to the word "India" in *Natural History* (sorted by PMI)
 
@@
 ```
-
 :::
 
-The top 20 ranking lists of absolute frequency and signed $G^2$ scores have a 11/20 overlapped outputs.
-As shown in @fig-col_colloc, the signed $G^2$ score and absolute frequency in textual collocation analysis shows a positive correlation.
+The top 20 ranking word lists of absolute frequency and signed $G^2$ score have a 11/20 overlapping outputs.
+As shown in @fig-col_colloc, there is a positive correlation between the signed $G^2$ score and absolute frequency in textual collocation analysis.
 
@@
 
-The high-ranking words in textual collocation with "India" sorted by absolute frequency and signed $G^2$ scores are categorized as follows, those without specifying the association measures ("A" stands for "absolute frequency" and "G" stands for "signed $G^2$ scores") are the overlapped ones.
-These words listed out comprises the strongest evidence of collocating with "India" in the context.
+The high-ranking words collocating with "India", sorted by their absolute frequency and signed $G^2$ score, are categorized as follows.
+Those without specifying the association measures ("A" stands for "absolute frequency" and "G" stands for "signed $G^2$ score") are the overlapped ones.
+The overlapped words are considered having the strongest evidence of frequently collocating with "India" in the context.
 
@@
 
-**Precious stone**: *stones*, *rock-crystal*, *gems*, *gem*(G), *gemstone*(G), *pearls*
+**Precious stone**: *stones*, *rock-crystal*, *gems*, *gem*(G), *gemstone*(G), *pearls*, *smaragdus*(G)
 
@@
 
-**Merchandize exchange**: *mart*(G)
+**Merchandise exchange**: *mart*(G)
 
-**Descriptive expression**: *hundred*, *thousand*(A), *whole*(A), *numerous*(A), *luxury*(A), *closely*(A), *valuable*(A), *bright*(A), *identical*(G), *smaragdus*(G)
+**Descriptive expression**: *hundred*, *thousand*(A), *whole*(A), *numerous*(A), *luxury*(A), *closely*(A), *valuable*(A), *bright*(A), *identical*(G)
 
@@
 
-These categories indicates that the narrative about "India" in *Natural History* covers three major dimensions.
-The first dimension is its geographical situation, including its connection to other places (mainly Arabia and Ethiopia), the two major rivers, Ganges and Indus within the region, and the animals, plants and precious stones originated in it.
-And it is often mentioned with historical figures, some related to the conquest history of the Roman Empire (in the case of *alexander*, referring to Alexander the Great, who had conducted several expeditions to Indian subcontinent), and some related to the referencing scholarship Pliny made his dialogue with.
-Moreover, the collocating word *mart* and the descriptive expressions highlights the merchandize exchanges introduced and discussed in the India-related content in the work.
+These categories indicate that the "India" narrative in *Natural History* covers three major dimensions.
+The first dimension is its geographical information, including its connection to other places (primarily Arabia and Ethiopia), the two major rivers in the region, Ganges and Indus, and the animals, plants and precious stones originating from it.
+And it is frequently mentioned with historical figures, some related to the conquest history of the Roman Empire (in the case of *alexander*, referring to Alexander the Great, who conducted several expeditions to Indian subcontinent), and some related to the referencing scholarship Pliny consulted in the work.
+Moreover, the term *mart* and the descriptive phrases such as *luxury* and *valuable*, highlights the merchandise exchanges introduced in the discussion of India.
 
@@
 #| label: tbl-colloc_freq_compare_AFG
-#| tbl-cap:  Frequency comparison of overlapping textual collocating words sorted by absolute frequency and signed $G^2$ score in the top 20 ranking in target and reference context
+#| tbl-cap:  Normalized frequency comparison of overlapping top 20 ranking textual "Inida"-collocating words sorted by absolute frequency and signed $G^2$ score in target and reference context
 
@@
 
-When checking about the normalized frequency of the top 20 list sorted with PMI scores, as shown in @tbl-colloc_frequency_compare_PMI, all of the results show higher frequency than that in the reference context as well.
+When examining the normalized frequency of the top 20 list sorted by PMI score, as presented in @tbl-colloc_frequency_compare_PMI, all of the results exhibit a higher frequency than that of the reference context as well.
+
 ```{r}
 #| label: tbl-colloc_frequency_compare_PMI
-#| tbl-cap:  Frequency comparison of top 20 textual collocating words sorted by PMI score in target and reference context
+#| tbl-cap: Normalized frequency comparison of top 20 textual "India"-collocating words sorted by PMI score in target and reference context
 
@@
 
-The PMI word list, indicating the words with relatively strongest attraction to the word "India" in the context, shows more descriptive information about the theme related to India in *Natural History*.
-Most of them can be classified to the categories set for the overlapping high ranking absolute frequency and signed $G^2$ scores, and some words contribute to a new category relating to the exsisting categories, as shown in the classification as follows:
+As the PMI sorting identifies the words of the strongest attraction with the word "India" in the context, the listed words provides additional descriptive information about the themes relating to India in the work.
+Most of them can be classified into the aforementioned categories set for the results of absolute frequency and signed $G^2$ score, some of the words contribute to a new category relating to the existing ones.
+The top ranking words sorted by PMI are grouped as follows:
 
@@
 
-**Merchandize exchange**: *merchandize*, *mart*
+**Merchandise exchange**: *merchandize*, *mart*
 
@@
 
-Except for showing more specified geographical connections, plants and gemstone names, the descriptive expressions in the list relates to the description of stones, and the special traits of natural creatures originated in India in *Natural History*.
-The words of the new categories relates to the existing categories.
-For example, the words of activity relates to the Indian-subcontinent expedition of Alexander the Great, the need for merchandize exchange, and the product processing of gemstones, and the words of ethnic group relates to the geographical introduction about Indian and its connected regions, which reinforced the previous conclusion, that the context of "India" in the work shows focuses on the geographical introduction about India and the trade relation between it and the Roman Empire.
+Except for displaying more specific geographic connections, plant and gemstone names, the descriptive expressions in the list pertain to the description of stones (such as *vermilion* and *honey-coloured*) and the special traits of natural creatures originating in India (such as *biggest* and *identical*) in *Natural History*.
+The words in the new categories relate to the existing categories.
+For example, the terms in "Activity" refer to Alexander the Great's *expedition* to the Indian subcontinent, the necessity for exchange of merchandise (*pursuits*), and the processing of gemstones (*engrave*).
+The terms in "Ethnic group" pertain to the human communities living in India and its surrounding regions.
+This additional information reinforces the conclusion that when "India" is mentioned in the work, Pliny tended to focus his discussion on its geographical conditions and trade relations with the Roman Empire.
 
-Combining the observation of the three top ranking word lists of textual collocation to word "Inida" in *Natural History*, these collocates suggest the interconnecting role India played in the network of interactions, trade, and cultural exchanges in the narrative.
+The observations from the top ranking "India"-collocating word lists of the three measures highlight how the narrative of *Natural History* underscores India's geographical interconnection and its important role in merchandise and cultural exchange.
 
@@
 The frequency lists for the **target corpus** (India-related texts) and **reference corpus** (whole text) are generated respectively, and the association scores are calculated through the `mclm::assoc_scores()` function.
-Similar to the collocation analysis, the returned scores are filtered with a criterion of PMI >= 2 and signed $G^2$ >= 3.84, to ensure the selected words for further discussion have a strong attraction to the target corpus with statistical significance [@montes2022].
+Similar to the collocation analysis, the returned scores are filtered with a criterion of PMI \>= 2 and signed $G^2$ \>= 3.84, to ensure the selected words for further discussion have a strong attraction to the target corpus with statistical significance [@montes2022].
+
+Additionally, in order to examine the significant phrases, i.e.
+"keyword", in the India-related content in the work, a keyword analysis for the India-related text is employed as a comparison and complement to the conclusion of the textual collocation analysis.
+
+The word frequency and their association scores in the **target corpus** (India-related texts) and **reference corpus** (other parts of *Natural History* excluding the India-related texts) are obtained with the `mclm::assoc_scores()` function.
+Similar to the collocation analysis, the returned scores are filtered with a criterion of PMI \>= 2 and signed $G^2$ \>= 3.84 to ensure that the words selected for further discussion have a strong attraction to the target corpus with statistical significance [@montes2022].
 
@@
 #| label: keyword
-#| warning: false
 
-# calculate scores
 scores_kw <- assoc_scores(flist_target, flist_ref)
@@
 
-The following tables present the top 20 keywords in India-related texts as compared to the entire texts in *Natural History*.
-They are sorted based on their absolute frequencies (@tbl-kwtable_absolute_freqencies), signed $G^2$ scores (@tbl-kwtable_Gsigned) and PMI scores (@tbl-kwtable_PMI) respectively.
+The following tables show the top 20 keywords in India-related texts as compared to the total texts in *Natural History*.
+They are sorted by their absolute frequency (@tbl-kwtable_absolute_frequency), signed $G^2$ score (@tbl-kwtable_Gsigned) and PMI score (@tbl-kwtable_PMI) in descending order.
 
 ::: panel-tabset
-### Sorted by absolute frequencies
+### Sorted by absolute frequency
 
 ```{r}
-#| label: tbl-kwtable_absolute_freqencies
-#| tbl-cap: Top 20 Keywords on Indian Related Text in Natural History (sorted by PMI)
+#| label: tbl-kwtable_absolute_frequency
+#| tbl-cap: Top 20 keywords of India-related text in *Natural History* (sorted by absolute frequency)
 
@@
 ```{r}
-#| warning: false
-#| echo: false
 #| label: tbl-kwtable_Gsigned
-#| tbl-cap-location: top
-#| tbl-cap: Top 20 Keywords on Indian Related Text in Natural History (sorted by signed $G^2$)
+#| tbl-cap: Top 20 keywords of India-related text in *Natural History* (sorted by signed $G^2$)
 
@@
 #| label: tbl-kwtable_PMI
-#| tbl-cap: Top 20 Keywords on Indian Related Text in Natural History (sorted by PMI)
+#| tbl-cap: Top 20 keywords of India-related text in *Natural History* (sorted by PMI)
 
@@
 
-Among the three lists sorting by different measurements, 16/20 words of absolute frequency top ranking list overlaps with that of the signed $G^2$ scores.
+Among the three lists sorted by different measures, 16/20 words of the absolute frequency top list overlap with that of the signed $G^2$ score.
 As shown in the @fig-col_keyword, the signed $G^2$ score has a positive correlation with the absolute frequency in this case.
@@
 #| label: fig-col_keyword
-#| fig-cap: Scatter plot of signed $G^2$ scores by absolute frequency in keyword analysis
+#| fig-cap: Scatter plot of signed $G^2$ score by absolute frequency in keyword analysis
 
@@
 
-Combing the top ranking keyword lists sorted by absolute frequency and signed $G^2$ scores, it can be classified into categories similar to that in the previous collocation analysis.
-In the categorized groups below, those without specifying the association measures ("A" stands for "absolute frequency" and "G" stands for "signed $G^2$ scores") are the overlapped ones.
+The top 20 keyword lists, sorted by absolute frequency and signed $G^2$ score, can be categorized similarly to the previous collocation analysis.
+In the categorized groups below, those without association measures remarks ("A" stands for "absolute frequency" and "G" for "signed $G^2$ score") are the overlapping ones.
 
@@
 
-The words in each group partly overlaps with the results in collocation analysis, which on the one hand confirms the potential themes in the India-related content as concluded previously, and on the other hand, suggests that the high evidence ranking textual collocates of "India" also possibly serve as the keywords in the target corpus.
+The words in each group partially overlap with the results of the collocation analysis, which on the one hand confirms the potential themes in the India-related content as concluded earlier, and on the other hand suggests that the textual collocates of "India" with a high evidence ranking may also serve as keywords in the target corpus.
 
-In the comparison of normalized frequency of these words in the target and reference corpra, they all show notably higer frequencies in the target corpus, as shown in @tbl-kw_frequency_compare.
+Comparing the normalized frequency of these words in the target and reference corpus, they all show significantly higher frequencies in the target corpus, as shown in @tbl-kw_frequency_compare.
 
@@
 #| label: tbl-kw_frequency_compare
-#| tbl-cap:  Comparison of overlapping keywords sorted by absolute frequency and G signed with that of reference corpus
+#| tbl-cap:  Comparison of overlapping keywords in India-related text sorted by absolute frequency and G signed with that of reference corpus
 flist_ref_df <- as_tibble(flist_ref)
@@
 
-Furthermore, as PMI score indicates the times of probability of the selected keyword occur in the target corpus higher than that in the reference corpus, it could serve as a more convincing indicator for the analysis of keywords.
+Moreover, since the PMI score indicates the degree of probability of the selected keyword's occurrence in the target corpus higher than that in the reference corpus, it could be a more convincing indicator for keyword analysis.
 
-When checking about the normalized frequency of the top 20 keywords with the most PMI score, as shown in @tbl-kw_frequency_pmi, almost all of them are seem distinct in the India-related text, which reinforces the indication that they are especially key to the target corpus comparing to the other parts of the work.
+When checking the normalized frequency of the top 20 keywords with the most PMI score, as shown in @tbl-kw_frequency_pmi, almost all of them seem to be distinct in the India-related text, which reinforces the indication that they are especially key to the target corpus compared to the other parts of the work.
 
@@
 #| label: tbl-kw_frequency_pmi
-#| tbl-cap:  Comparison of overlapping keywords sorted by absolute frequency and G signed with that of reference corpus
+#| tbl-cap:  Comparison of overlapping keywords in India-related text sorted by absolute frequency and G signed with that of reference corpus
 
@@
 
-For these keywords, a manual examination was performed to determine their meaning and assign classification tags based on their category.
-The explanations for the top 20 keywords with the highest PMI scores is displayed in @tbl-kwlist below.
+These keywords were manually reviewed to determine their meaning and assigned classification tags based on their category.
+The explanations for the top 20 keywords with the highest PMI scores are displayed in the @tbl-kwlist below.
 
@@
 #| label: tbl-kwlist
-#| tbl-cap: Top 20 keywords with meaning sorted by PMI
+#| tbl-cap: Explaination and classification of the top 20 keywords in India-related text sorted by PMI
 
 keyword_PMI_list <- data.frame(
-  Word = c("india", "ganges", "beryls", "indus", "taprobane", "ichthyophagi", "megasthenes", "obsidian", "bdellium", "agates", "callaina", "condensation", "expeditions", "gerra", "jomanes", "nonius", "patala", "prasii", "alia", "bactra", "carnelian", "ceylon", "cophes", "hypasis", "merchandize", "peppertree", "sacae", "sandastros", "thornbush"),
-  Exp = c("name of the focused region of this study", "a major river in India", "a type of gemstone", "a major river in India", "Island in Sri Lanka", "a group of people who primarily subsist on fish", "a Greek historian and diplomat", "a type of volcanic glass", "a fragrant resin obtained from certain trees", "a type of semiprecious gemstone", "pale green precious stone (lat)", "the process of vapor turning into a liquid state", "referring to the expedition of Alexander the Great", "war (lat)", "name of a river", "a Roman nomen gentile, gens or \"family name\"", "refer to a city in Indian region", "prase, green coloured gem", "by another / different way / route (lat)", "name of a city in Asia Minor", "a reddish-brown variety of chalcedony", "name of an Island in Indian subcontinent", "a river that rises in the ancient Paropamise range, eventually falling into the Indus river near its confluence with the Cophes river", "a river in north India", "goods or commodities", "a tree that produces peppercorns", "the easternmost nation of Elibe, situated to the south of Ilia and the north of Bern", "a precious stone found in India and Arabia", "any of many thorny or spiny shrubs and bushes"),
-  Category = c("region", "river", "goods", "river", "region", "people", "people", "goods", "goods", "goods", "goods", "activity", "activity", "activity", "river", "people", "region", "goods", "route", "region", "goods", "region", "river", "river", "goods", "plant", "river", "goods", "plant"),
-  Remark = c("N/A", "N/A", "gemstone", "N/A", "N/A", "tribe", "referencing scholar", "other goods", "other goods", "gemstone", "gemstone", "producing activity", "N/A", "N/A", "N/A", "human name", "N/A", "gemstone", "N/A", "N/A", "gemstone", "N/A", "N/A", "N/A", "general goods", "origin of goods", "N/A", "gemstone", "N/A")
+  Word = c("india", "indus", "ganges", "beryls", "taprobane", "ichthyophagi", "megasthenes", "obsidian", "bdellium", "agates", "callaina", "condensation", "expeditions", "gerra", "jomanes", "nonius", "patala", "prasii", "alia", "bactra", "carnelian", "ceylon", "cophes", "hypasis", "merchandize", "pepper-tree", "sacae", "sandastros", "thorn-bush"),
+  Exp = c("name of the focused region of this study", "a major river in India", "a major river in India", "a type of gemstone", "island in Sri Lanka", "a group of people who primarily subsist on fish", "a Greek historian and diplomat", "a type of volcanic glass", "a fragrant resin obtained from certain trees", "a type of semiprecious gemstone", "pale green precious stone (lat)", "the process of vapor turning into a liquid state", "referring to the expedition of Alexander the Great", "war (lat)", "the most important of the affluents of the Ganges", "a Roman nomen gentile, gens or \"family name\"", "name of an ancient city at the mouth of the Indus River", "prase, green coloured gem", "by another / different way / route (lat)", "name of a city in Asia Minor", "a reddish-brown variety of chalcedony", "name of an island in Indian subcontinent", "a river that emerges in Hindu Kush mountains and empties into the Indus River", "a river in north India", "goods or commodities", "a tree that produces peppercorns", "historic Persian ethnic group", "a precious stone found in India and Arabia", "any of many thorny or spiny shrubs and bushes"),
+  Category = c("region", "river", "river", "goods", "region", "people", "people", "goods", "goods", "goods", "goods", "activity", "activity", "activity", "river", "people", "region", "goods", "route", "region", "goods", "region", "river", "river", "goods", "plant", "people", "goods", "plant"),
+  Remark = c("N/A", "N/A", "N/A", "gemstone", "N/A", "tribe", "referencing scholar", "other goods", "other goods", "gemstone", "gemstone", "producing activity", "N/A", "N/A", "N/A", "human name", "N/A", "gemstone", "N/A", "N/A", "gemstone", "N/A", "N/A", "N/A", "general goods", "origin of goods", "N/A", "gemstone", "N/A")
 )
@@
 
-The distribution plot of categories, as demonstrated in @fig-kwtype, reveals the pattern regarding keywords of India-related texts in *Natural History*.
+@fig-kwtype demonstrates the distribution of the classification tags of the top 20 keywords with the highest PMI score.
 
 ```{r}
-#| warning: false
-#| echo: false
 #| label: fig-kwtype
-#| fig-cap: Top 20 keywords type distribution
-#| fig-cap-location: top
+#| fig-cap: Classification distribution of the top 20 keywords in India-related text sorted by PMI
 
@@
 
-Significantly, a substantial number of the keywords in the India-related text revolve around goods, particularly precious stones, suggesting a prominent thematic focus.
-The presence of keywords such as *beryls*, *obsidian*, *bdellium*, *agates*, *callaina*, *prasii*, *carnelian* and *sandastros* indicates the involvement of various gemstones and goods associated with India.
-These findings are complemented by the presence of keywords like *condensation*, *merchandize* and *pepper tree* which suggest the production and trade of goods between the Roman Empire and the Indian regions during that era.
+A significant proportion of the highest PMI-scored keywords in texts related to India center around the concept of "goods", specifically gemstones.
+This emphasis on gemstones indicates a prevailing thematic concentration in this context.
+The inclusion of keywords such as *beryls*, *agates*, *callaina*, *obsidian*, *prasii*, *carnelian*,  *sandastros*, *obsidian* and *bdellium* represents the integration of diverse gemstones and commodities closely linked to India.
+Complemented by the presence of keywords like *condensation*, *merchandize* and *pepper-tree*, which relate to the production and trade of goods, India's role as an central hub in the Indo-Mediterranean commercial network is emphasized in the narrative.
 
-Furthermore, the keywords related to rivers in India, such as *ganges*, *cophes*, *hypasis*, and *sacae* indicate their significance as sources of goods or as integral parts of trading routes.
-Since Pliny the Elder's contextual framework includes critical descriptions of the geographical surroundings like rivers, as evident in his references to the Po River and the Nile River [@pollard2009; @murphy2003], a deeper investigation into the portrayal and role of Indian rivers within this context would provide valuable insights.
+Additionally, many of the keywords are names of rivers that flow through India, such as *indus*, *ganges*, *jomanes*, *cophes*, and *hypasis*.
+These rivers are important for transportation within India and connecting it with neighboring regions.
+Some of them serve as landmarks along trade routes or the origins of traded goods.
+Taking a broader context into consideration, as noted by @roller2022, Pliny shows a particular interest in rivers in *Natural History*, not only in relation to India.
+The highlights on rivers reflect a shift in Roman geographical ideology, which accentuates rivers as symbols of territorial expansion and markers of inland regions, as opposed to the Greek tradition that emphasized coastlines.
 
-Additionally, a notable proportion of the keywords pertain to people, encompassing names, descriptions, and specific historical figures like *megasthenes*.
-This suggests the historical significance of individuals who played a role in trade with India or in documenting and understanding the region.
+Furthermore, a notable proportion of the keywords are place names, encompassing names of cities and islands in Indian subcontinent and neighboring areas.
 
-In conclusion, the keywords extracted from the India-related text in the *Natural History* shed light on India's role in trade, the production of valuable goods, and its association with notable historical figures and geographical features within the perspective of Pliny the Elder during the 1st century AD in the context of the Roman Empire.
-These findings could also contribute to a better understanding of India's historical interactions with the broader ancient world.
+To summarize, aside from echoing the focus on the geographical interconnection and the role as a trading hub related to India in the collocation analysis, the keyword analysis reveals two concrete themes, stones and rivers, in the narrative about India in *Natural History*.
+These themes provide additional information about the trading products and routes while also reflecting the transition of ancient Rome's geographical ideology from Greek.
 
@@
 
-In conclusion, this paper located the research question on potential theme and topics in texts about India in Pliny the Elder's *Natural History* based on the prominent distribution of "India" in the entire text comparing to other place names.
-The analysis was conducted with the collocation analysis and keyword analysis in a framework of corpus linguistics.
+In conclusion, this paper investigates how Pliny the Elder describes India in his work, *Natural History*, by examining the potential themes and topics related to India.
+The research question is motivated by the notable frequency of references to "India" throughout the text.
+The analysis employs methods of collocation and keyword analysis within a corpus linguistics framework.
 
-The analysis of keywords in the India-related text revealed significant themes such as the rivers, gemstones, goods, and historical figures like Megasthenes.
-These findings emphasize the cultural, geographical, and historical importance of India in the scope of scholars in Roman Empire during 1st century AD.
+The exploration of textual collocates to the word "India" reveals the geographical connections, trade networks, historical figures, and scholarly references associated with India in *Natural History*.
+The collocates also emphasize India's close relationship with neighboring regions such as Arabia and Ethiopia.
 
-Moreover, the exploration of collocates uncovered the geographical connections, trading networks, and territorial boundaries linked to India.
-The collocates highlighted the close relationships with neighboring regions such as Arabia and Ethiopia, along with references to trade, imports, and commodity production.
+Furthermore, the examination of keywords in India-related text aligns with the observations of the collocation analysis and highlights potential topics on stones and rivers about India in the work.
+These findings enhance the interpretation of the identified themes, such as geographical connectivity and merchandise trade, and also reflect Pliny's general geographical concern in the historical context of ancient Rome.
 
-Additionally, the study provided information on the specific contexts and usage of the word "India" within Pliny the Elder's *Natural History*, as a resource for further analysis about the discourse and recognition of India during that era.
-
-While this research represents an initial exploration, it paves the way for future investigations.
-Subsequent studies can expand the analysis to encompass a wider range of texts, explore different domains within Indian subcontinent-related literature, and utilize advanced natural language processing techniques to gain deeper semantic insights.
+As this paper serves as a preliminary exploration, it encourages further in-depth investigations of the text.
+A comparative analysis of collocation and keywords centering other neighboring regions, and a closer examination of "stone" or "river" in the context, incorporating additional literature regarding the historical and cultural background may offer greater insights and enrich the discussion.

### 2023-08-27 freqlist_location.R

@@ -102,12 +102,6 @@ top_scores_kw %>%
 
 top_scores_kw_df <- as_tibble(top_scores_kw)
 
-theme_set(theme_minimal(base_size = 15))
-g <- top_scores_kw_df %>%
-  ggplot(aes(x = G_signed, y = a)) +
-  labs(x = "G", y = "afr")
-g + geom_point()
-
 
 keyword_PMI_list <- data.frame(
   Word = c("ganges", "beryls", "ichthyophagi", "megasthenes", "obsidian", "bdellium", "agates", "callaina", "condensation", "gerra", "jomanes", "nonius", "prasii", "alia", "carnelian", "cophes", "hypasis", "merchandize", "peppertree", "sacae", "sandastros", "thornbush"),
@@ -126,12 +120,6 @@ tag_counts <- keyword_PMI_list %>%
   count(Tag) %>%
   arrange(desc(n))
 
-# Plot the tag distribution
-ggplot(tag_counts, aes(x = n, y = reorder(Tag, -n), fill = Tag)) +
-  geom_bar(stat = "identity") +
-  labs(x = "Count", y = "Tag", fill = "Tag") +
-  theme_minimal() +
-  coord_flip()
 
 flist_ref_df <- as_tibble(flist_ref)
 flist_target_df <- as_tibble(flist_target)
@@ -139,13 +127,7 @@ words_to_check <- c("ganges", "beryls", "ichthyophagi", "megasthenes", "obsidian
 words_to_check1<- c("india", "hundred", "stones", "arabia", "indian", "alexander",
                     "amber", "thousand", "elephants", "indus", "glass", "thence",
                     "ganges", "rock-crystal", "ethiopia", "indians")
-for (word_to_check in words_to_check1){
-  freq <- NA  # Initialize with NA in case the word is not found
-  if (word_to_check %in% names(flist_ref_df)) {
-    freq <- flist_ref_df$[[word_to_check]]  # Adjust this based on your data structure
-  }
-  cat("Frequency of '", word_to_check, "':", freq, "\n")
-}
+
 
 
 
@@ -167,15 +149,9 @@ top_scores_colloc %>%
   scroll_box(height = "400px") %>% print()
 
 top_scores_colloc_df <- as_tibble(top_scores_colloc)
-g1 <- top_scores_colloc_df %>%
-  ggplot(aes(x = G_signed, y = a)) +
[…]

### 2023-08-27 paper_quarto.qmd
0827 final refine

@@
 By analyzing these word associations and significant terms, this study seeks to identify the main themes and topics related to the Indian region within the text.
-This will shed light on how Pliny depicts and imagines this geographical area, providing insights into the spatial representation and imagination in the work.'
+The investigation of how Pliny depicts India in *Natural Hisotry* could potentially contribute to the discussion of the spatial representation and imagination in the work.'
 ---
+
+<script type="text/x-mathjax-config">MathJax.Hub.Config({tex2jax: {inlineMath: [["$","$"]]}})</script>
+<script async src="https://mathjax.rstudio.com/latest/MathJax.js?config=TeX-AMS-MML_HTMLorMML"></script>
 
@@
 
+# read file names of the corpra
 refcorpus_folder <- here("NH_wholetext")
@@
 
-# Exclude short file names with the same name from target corpus in the reference corpus
+# exclude short file names with the same name from target corpus in the reference corpus
 fnames_wholetext_short_filtered <- fnames_wholetext_short %>%
@@
 
-# Filter full file names based on filtered short names
+# filter full file names based on filtered short names
 fnames_wholetext_filtered <- fnames_wholetext[fnames_wholetext_short %in% fnames_wholetext_short_filtered]
@@
 During the extraction process of the corpus files, the texts are already converted to lower case.
+In addition, the closing quotation mark "'", which ranks high while provides limited information in the initial observation of the returned frequency lists, is replaced by an empty string for a more informative return for further discussions.
 
@@
 ## Textual collocating word with "India" in *Natural History*
-
-Textual collocation refers to the observation of some words frequently occurring with the target word in the context.
-Different from the surface collocation, which taking the collocating span, i.e.
-the certain words left and right to the target word into consideration [@evert2009], the word span in this case refers to the textual unit around the target word.
-Setting "India" as the target word in the corpus of all paragraphs in *Natural History*, the `mclm::text_cooc()` function returns the frequency of words appeared in the context of "India".
-As mentioned in the Methodology Section (@sec-method), the returned scores are filtered with a statistical criteria for gaining a list of the most frequently observed words in the context of word "India" with strong significance.
-
-The prominent textual collocates of "India" identified with this approach suggests the potential themes about Indian region in the narrative of Pliny.
 
@@
 ```{r}
+#| lable: obtain and filter collocation association scores
+
 coocs <- fnames_wholetext %>% 
@@
   ggplot(aes(x = G_signed, y = a)) +
-  labs(x = "signed $G^2$", y = "Absolute frequency") +
+  labs(x = r"(Signed G)", y = "Absolute frequency") +
   geom_point() +
@@
 Additionally, in order to examine the significant phrases, i.e.
-"keyword", in the India-related content in the work, as a comparison and supplement to the conclusion of textual collocation analysis, a keyword analysis is employed for the India-related text.
-
-The frequency lists for the **target corpus** (India-related texts) and **reference corpus** (whole text) are generated respectively, and the association scores are calculated through the `mclm::assoc_scores()` function.
-Similar to the collocation analysis, the returned scores are filtered with a criterion of PMI \>= 2 and signed $G^2$ \>= 3.84, to ensure the selected words for further discussion have a strong attraction to the target corpus with statistical significance [@montes2022].
-
-Additionally, in order to examine the significant phrases, i.e.
 "keyword", in the India-related content in the work, a keyword analysis for the India-related text is employed as a comparison and complement to the conclusion of the textual collocation analysis.
@@
 ```{r}
-#| label: keyword
+#| label: obtain and filter keywords association scores
 
@@
 
-**Geographical connections**: india, arabia, indian, ganges, indus, ethiopia, taprobane(G), thence, sail(A)
+**Geographical connections**: *india*, *arabia*, *indian*, *ganges*, *indus*, *ethiopia*, *taprobane*(G), *thence*, *sail*(A)
 
-**Animal/Plant**: elephants, pepper(A)
+**Animal/Plant**: *elephants*, *pepper*(A)
 
-**Precious stone**: stones, amber, rock-crystal, glass, beryls(G)
+**Precious stone**: *stones*, *amber*, *rock-crystal*, *glass*, *beryls*(G)
 
-**Historical figure**: alexander, ichthyophagi(G), megasthenes(G)
+**Historical figure**: *alexander*, *ichthyophagi*(G), *megasthenes*(G)
 
-**Ethnic group**: indians, tribe(A)
+**Ethnic group**: *indians*, *tribe*(A)
 
-**Descriptive expression (numeric)**: hundred, thousand, fifty(A)
+**Descriptive expression (numeric)**: *hundred*, *thousand*, *fifty*(A)
 
@@
 #| label: tbl-kw_frequency_compare
-#| tbl-cap:  Comparison of overlapping keywords in India-related text sorted by absolute frequency and G signed with that of reference corpus
+#| tbl-cap:  Normalized frequency comparison of overlapping top 20 ranking keywords in India-related text sorted by absolute frequency and signed $G^2$ score in target and reference corpus
 flist_ref_df <- as_tibble(flist_ref)
@@
 tar_nrm_freq_lookup <- setNames(flist_target_df$nrm_freq, flist_target_df$type)
-
 nrm_freq_lookup <- setNames(flist_ref_df$nrm_freq, flist_ref_df$type)
 
-results <- tibble(
+results_keyword <- tibble(
   Word = filtered_top_scores$type,
@@
 
-results
+results_keyword
 
@@
 #| label: tbl-kw_frequency_pmi
-#| tbl-cap:  Comparison of overlapping keywords in India-related text sorted by absolute frequency and G signed with that of reference corpus
+#| tbl-cap:  Normalized frequency comparison of top 20 ranking keywords in India-related text sorted by PMI in target and reference corpus
 
@@
 
-results1 <- tibble(
+results_keyword_pmi <- tibble(
   Word = filtered_top_scores_pmi$type,
@@
 
-results1
+results_keyword_pmi
 
@@
   select(Word, Exp, Category, Remark) %>%                        
-  kbl(col.names = c("Word", "Exp", "Category", "Remark")) %>% 
+  kbl(col.names = c("Word", "Explaination", "Category", "Remark")) %>% 
   kable_minimal()
@@
 
-# Plot the tag distribution
+# plot the tag distribution
 ggplot(tag_counts, aes(x = n, y = reorder(Category, -n), fill = Category)) +
@@
 
-Furthermore, the examination of keywords in India-related text aligns with the observations of the collocation analysis and highlights potential topics on stones and rivers about India in the work.
+Moreover, the examination of keywords in India-related text aligns with the observations of the collocation analysis and highlights potential topics on stones and rivers about India in the work.
 These findings enhance the interpretation of the identified themes, such as geographical connectivity and merchandise trade, and also reflect Pliny's general geographical concern in the historical context of ancient Rome.
@@
 As this paper serves as a preliminary exploration, it encourages further in-depth investigations of the text.
-A comparative analysis of collocation and keywords centering other neighboring regions, and a closer examination of "stone" or "river" in the context, incorporating additional literature regarding the historical and cultural background may offer greater insights and enrich the discussion.
+A comparative analysis of collocation and keywords centering other neighboring regions to India, and a closer examination of "stone" or "river" in the context, incorporating additional literature regarding the historical and cultural background may offer greater insights and enrich the discussion.

### 2023-08-27 NH_pilot_exploration.R

@@ -1,0 +1,200 @@
+install.packages('tidyverse')
+install.packages('mclm')
+install.packages('here')
+install.packages('kableExtra')
+install.packages("leaflet")
+install.packages("downlit")
+
+
+
+library('tidyverse')
+library('mclm')
+library('here')
+library('kableExtra')
+library('leaflet')
+library('downlit')
+
+# read the geographical-related dataset
+data <- read.csv("geotext_whole.csv")
+
+# sort frequency of place names being mentioned
+# for bar plot and map visualization
+summary_data <- data %>%
+  group_by(ToposText_ID, Place_Name, Lat, Long) %>%
+  summarise(Count = n()) %>%
+  arrange(desc(Count)) %>%
+  ungroup() 
+
+# read the corpus files for whole texts
+refcorpus_folder <- here("NH_wholetext")
+fnames_wholetext <- get_fnames(refcorpus_folder) %>% 
+  keep_re("[.]txt")
+
+# read the corpus files for India-related texts
+tarcorpus_folder <-  here("NH_geotext_india")
+fnames_indiatext <- get_fnames(tarcorpus_folder) %>% 
+  keep_re("[.]txt") 
+
+
+# get the short file name for filtering out India-related texts
+# from the corpus of whole texts
+fnames_wholetext_short <- basename(fnames_wholetext)
+fnames_indiatext_short <- basename(fnames_indiatext)
+
+# exclude short file names with the same name from India-related texts corpus in the whole texts corpus
+fnames_wholetext_short_filtered <- fnames_wholetext_short %>%
+  setdiff(fnames_indiatext_short)
+
+# filter full file names based on filtered short names
+# the filtered corpus will serve as the reference corpus in keyword analysis
+fnames_wholetext_filtered <- fnames_wholetext[fnames_wholetext_short %in% fnames_wholetext_short_filtered]
+
+# textual collocation analysis
+# set "india" as the target word for textual collocation analysis
+coocs <- fnames_wholetext %>% 
+  text_cooc("(?xi)  ^ india $")
+
+# calculate collocation scores
+scores_colloc <- assoc_scores(coocs)
+
+# filter the collocation scores with a statistical criterion
+top_scores_colloc <- scores_colloc %>% 
+  filter(PMI >= 2 & G_signed >= 3.84)
+
+# transfer the filtered collocation objects into dataframe
[…]

### 2023-08-27 freqlist_location.R

@@ -1,218 +1,0 @@
-install.packages('tidyverse')
-install.packages('mclm')
-install.packages('here')
-install.packages('kableExtra')
-install.packages("leaflet")
-install.packages("quarto")
-install.packages("downlit")
-
-
-
-library('tidyverse')
-library('mclm')
-library('here')
-library('kableExtra')
-library('leaflet')
-library('downlit')
-
-
-data <- read.csv("geotext_whole.csv")
-
-summary_data <- data %>%
-  group_by(ToposText_ID, Place_Name, Lat, Long) %>%
-  summarise(Count = n()) %>%
-  arrange(desc(Count)) %>%
-  ungroup() 
-
-
-# Create a bar chart using ggplot2
-top_20_summary_data <- summary_data %>%
-  top_n(20, Count) %>%
-  ungroup()
-
-ggplot(top_20_summary_data, aes(x = reorder(Place_Name, -Count), y = Count)) +
-  geom_col() +
-  labs(x = "Place name", y = "Number of occurrences") +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1))
-
-
-
-# Create a leaflet map
-mapping <- leaflet() %>%
-  addTiles() %>%
-  addCircleMarkers(
-    data = summary_data,
-    lat = ~Lat,
-    lng = ~Long,
-    radius = sqrt(summary_data$Count) * 0.8,  # Adjust the scaling factor as needed
-    color = "blue",
-    fill = TRUE,
-    fillOpacity = 0.6,
-    popup = paste("Place name:", summary_data$Place_Name, "<br>",
-                  "Number of occurences:", summary_data$Count)
-  )
-
-
-corpus_folder_whole <- here("NH_wholetext")
-fnames_wholetext <- get_fnames(corpus_folder_whole) %>% 
-  keep_re("[.]txt")
-
-print(fnames_wholetext, 10, hide_path = corpus_folder_whole)
-
-corpus_folder_in <- here("NH_geotext_india")
-fnames_indiatext <- get_fnames(corpus_folder_in) %>% 
-  keep_re("[.]txt") 
-
-print(fnames_indiatext, 10, hide_path = corpus_folder_in)
-
-fnames_wholetext_short <- basename(fnames_wholetext)
-fnames_indiatext_short <- basename(fnames_indiatext)
-
-# Exclude short file names with the same name from target corpus in the reference corpus
-fnames_wholetext_short_filtered <- fnames_wholetext_short %>%
[…]

### 2023-08-27 paper_quarto.qmd
0827 final revise

@@
 
-In addition to the digitized textual content of *Natural History*, the place names mentioned in the text are annotated with their corresponding coordinates on TOPOXText.
+In addition to the digitized textual content of *Natural History*, the place names mentioned in the text are annotated with their corresponding coordinates on TOPOSText.
 Since the annotations are available in an HTML format, they are scraped and restructured into a dataset of geographical-related text in *Natural History* with [Beautiful Soup](https://www.crummy.com/software/BeautifulSoup/bs4/doc/) library in Python[^2].
@@
 
-Based on this observation, the focus of the study is narrowed down to India-related texts in the *Natural History* to investigate what and how India is described in the work.
+Based on this observation, the focus of the study is narrowed down to India-related texts in the *Natural History* to investigate how India is described in the work.
 By delving into the themes associated with the Indian region using the methods of collocation and keyword analysis, this study aims to examine Pliny the Elder's portrayal of India, which may shed light on the spatial perception and imagination of the representative writers and scholars of ancient Rome.
@@
 In this study, the **target corpus** includes all paragraphs in *Natural History* that mention place names in Indian regions, and the **reference corpus** includes all other paragraphs in the work.
-Lists of words with relatively higher frequency in the target corpus are obtained and sorted by the results of different measurements.
+Lists of words with relatively higher frequency in the target corpus are obtained and sorted by the different measurements.
 The "keywords" found in the India-related text in *Natural History* provide more descriptive information about the topics and elements related to "India" in Pliny's narrative.
@@
 
+# build frequency list for general corpus
+flist_gen <- fnames_wholetext %>%
+  freqlist(re_token_transf_in = "'", 
+           token_transf_out = "")
+
 # build frequency list for reference corpus
@@
 
-And the full text of the entire work, separated in paragraphs, are also scraped and stored in TXT format.
-Excluding those in target corpus, the other part of the work, containing `r length(fnames_wholetext_filtered)` files, serve as a **reference corpus**.
+The full text of the entire work, separated in paragraphs, are also scraped and stored in TXT format as a **general corpus**.
+This **general corpus** of `r length(fnames_wholetext)` files contains `r prettyNum(n_tokens(flist_gen))` tokens and `r n_types(flist_gen)` types, with the type-token ratio of `r round(n_types(flist_gen)/n_tokens(flist_gen), 2)`.
+
+Excluding those in target corpus from the general corpus, the other parts of the work contain `r length(fnames_wholetext_filtered)` files, serve as a **reference corpus**.
 The **reference corpus** contains `r prettyNum(n_tokens(flist_ref))` tokens and `r n_types(flist_ref)` types, with the type-token ratio of `r round(n_types(flist_ref)/n_tokens(flist_ref), 2)`.
+
+The **general corpus** is employed for the collocation analysis and the **target corpus** and **reference corpus** are used in the keywords analysis.
 
@@
 
-## Keyword in India-related text in *Natural History*
+## Keywords in India-related text in *Natural History*
 
 Additionally, in order to examine the significant phrases, i.e.
-"keyword", in the India-related content in the work, a keyword analysis for the India-related text is employed as a comparison and complement to the conclusion of the textual collocation analysis.
+"keywords", in the India-related content in the work, a keyword analysis for the India-related text is employed as a comparison and complement to the conclusion of the textual collocation analysis.
 
@@
 
-Among the three lists sorted by different measures, 16/20 words of the absolute frequency top list overlap with that of the signed $G^2$ score.
+Among the three lists sorted by different measures, 16/20 words of the absolute frequency top ranking list overlap with that of the signed $G^2$ score.
 As shown in the @fig-col_keyword, the signed $G^2$ score has a positive correlation with the absolute frequency in this case.
@@
 
-Moreover, since the PMI score indicates the degree of probability of the selected keyword's occurrence in the target corpus higher than that in the reference corpus, it could be a more convincing indicator for keyword analysis.
+Moreover, since the PMI score indicates the degree of probability of the selected keyword's occurrence in the target corpus higher than that in the reference corpus, it could be adopted as a more convincing indicator for keyword analysis.
 
-When checking the normalized frequency of the top 20 keywords with the most PMI score, as shown in @tbl-kw_frequency_pmi, almost all of them seem to be distinct in the India-related text, which reinforces the indication that they are especially key to the target corpus compared to the other parts of the work.
+When checking the normalized frequency of the top 20 keywords with the highest PMI score, as shown in @tbl-kw_frequency_pmi, almost all of them seem to be distinct in the India-related text, which reinforces the indication that they are especially key to the target corpus compared to the other parts of the work.
 
@@
 
-These keywords were manually reviewed to determine their meaning and assigned classification tags based on their category.
+These keywords are manually reviewed to determine their meaning and assigned classification tags based on their category.
 The explanations for the top 20 keywords with the highest PMI scores are displayed in the @tbl-kwlist below.
@@
 
-Furthermore, a notable proportion of the keywords are place names, encompassing names of cities and islands in Indian subcontinent and neighboring areas.
+Furthermore, a notable proportion of the keywords are place names, encompassing names of cities and islands in Indian subcontinent and its neighboring areas.
 
-To summarize, aside from echoing the focus on the geographical interconnection and the role as a trading hub related to India in the collocation analysis, the keyword analysis reveals two concrete themes, stones and rivers, in the narrative about India in *Natural History*.
-These themes provide additional information about the trading products and routes while also reflecting the transition of ancient Rome's geographical ideology from Greek.
+To summarize, aside from echoing the prominent themes about India found in the collocation analysis, the keyword analysis reveals two more concrete topics, namely stones and rivers, in the India-related narrative in *Natural History*.
+These topics provide additional information about the trading products and routes while also reflecting the transition of ancient Rome's geographical ideology from Greek.
 
@@
 
-Moreover, the examination of keywords in India-related text aligns with the observations of the collocation analysis and highlights potential topics on stones and rivers about India in the work.
+Moreover, the examination of keywords in India-related text aligns with the observations from the collocation analysis and highlights potential topics on stones and rivers about India in the work.
 These findings enhance the interpretation of the identified themes, such as geographical connectivity and merchandise trade, and also reflect Pliny's general geographical concern in the historical context of ancient Rome.
